### 2025-04-25 Project6/Example.tex
added new CAMELS paper

\documentclass[twocolumn]{aastex631}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\usepackage{amsmath}
\usepackage{multirow}

\begin{document}

\title{Mapping Star Formation Quenching Efficiency Across Feedback and Cosmological Parameter Space with CAMELS Simulations}

\author{AstroPilot}
\affiliation{Anthropic, Gemini \& OpenAI servers. Planet Earth.}

\begin{abstract}
Understanding the mechanisms that halt star formation in galaxies, leading to their eventual quenching, is a fundamental problem in astrophysics. The challenge lies in disentangling the complex interplay between internal feedback processes, such as those driven by supernovae (SNe) and active galactic nuclei (AGN), and the influence of the larger cosmological environment. These processes are highly degenerate, making it difficult to isolate the specific drivers responsible for quenching. In this study, we address this challenge by systematically quantifying the impact of feedback and cosmological parameters on star formation quenching at $z=0$. We leverage the CAMELS simulation suite, a unique collection of hydrodynamical simulations designed to vary key astrophysical and cosmological parameters independently. By analyzing the relationships between galaxy properties and these parameters, we disentangle the relative importance of SNe, AGN feedback, and cosmological factors in regulating star formation and determine how they correlate with the quenched fraction of galaxies. Our analysis provides predictive insights for galaxy evolution models and offers a theoretical framework for interpreting future observational surveys aimed at understanding the quenching phenomenon, ultimately providing valuable constraints on the underlying physical processes driving galaxy evolution.
\end{abstract}

\keywords{Galaxy evolution, Galaxy quenching, Cosmological parameters, N-body simulations, Regression}

\section{Introduction}
\label{sec:intro}
Understanding the physical processes that govern the evolution of galaxies remains a central goal of modern astrophysics. Galaxies, as the primary repositories of stars, gas, and dark matter, exhibit a remarkable diversity in their properties, ranging from actively star-forming spirals to quiescent ellipticals with little to no ongoing star formation. A critical phase in the life cycle of a galaxy is the transition from an active star-forming state to a quenched state, where star formation is significantly suppressed or halted altogether. Elucidating the mechanisms that drive this quenching phenomenon is essential for a complete understanding of galaxy evolution and the formation of the diverse galaxy population we observe throughout cosmic history. This endeavor requires a synergistic approach, combining sophisticated theoretical models with detailed observational constraints.

The regulation of star formation in galaxies is a complex process influenced by a multitude of factors operating on different scales. Internal feedback processes, driven by supernovae (SNe) and active galactic nuclei (AGN), play a crucial role in shaping the gas content and star formation activity of galaxies \citep{hopkins2011selfregulatedstarformationgalaxies,carr2022regulationstarformationhot}. Supernovae inject energy and momentum into the interstellar medium (ISM), potentially heating and expelling gas, thereby suppressing star formation \citep{hopkins2011selfregulatedstarformationgalaxies,carr2022regulationstarformationhot}. Similarly, AGN can release vast amounts of energy in the form of radiation and outflows, which can also heat or remove gas from the galaxy, leading to quenching. These internal feedback mechanisms are intricately linked to the properties of the galaxy itself, such as its stellar mass, morphology, and gas content.

Furthermore, the larger cosmological environment in which a galaxy resides also exerts a significant influence on its star formation history \citep{wijesinghe2012galaxymassassemblygama,shi2023naturevsnurturerevisiting,pérezmillán2023relationmorphologystarformation}. Factors such as halo mass, merger history, and the density of the surrounding cosmic web can affect the inflow of fresh gas into galaxies, which fuels star formation \citep{wijesinghe2012galaxymassassemblygama,pérezmillán2023relationmorphologystarformation}. Environmental effects can also trigger morphological transformations, such as the formation of a bulge, which can stabilize gas against collapse and prevent star formation \citep{pérezmillán2023relationmorphologystarformation}. Disentangling the relative importance of these internal and external factors, and understanding how they interact to determine a galaxy's star formation history, presents a formidable challenge \citep{pérezmillán2023relationmorphologystarformation,mucesh2024natureversusnurturegalaxy}.

The observed properties of galaxies, such as their stellar mass, morphology, and star formation rate, represent the integrated outcome of these complex interactions  \citep{das2021galaxyinteractionsdifferentenvironments,li2024effectgalaxyinteractionsstarbursts}. This makes it difficult to isolate the specific drivers responsible for quenching based solely on observational data. Moreover, the theoretical modeling of these processes is computationally intensive, demanding high-resolution simulations that accurately capture the relevant physics on a wide range of scales  \citep{das2023galaxyinteractionsfilamentssheets,subramanian2023effectlowmassgalaxyinteractions}. Such simulations must faithfully reproduce both the internal physics of galaxies and their interaction with the larger cosmological environment.

To address these challenges, we present a systematic study aimed at quantifying the impact of feedback and cosmological parameters on star formation quenching at $z=0$  \citep{piotrowska2021quenchingstarformationobserved}. Our approach leverages the CAMELS (Cosmology and Astrophysics with MachinE Learning Simulations) simulation suite, a unique collection of hydrodynamical simulations specifically designed to independently vary key astrophysical and cosmological parameters. The CAMELS suite encompasses both the IllustrisTNG and SIMBA models, enabling us to explore the effects of different subgrid physics implementations on quenching. By analyzing the relationships between galaxy properties and these parameters, we aim to disentangle the relative importance of SNe, AGN feedback, and cosmological factors in regulating star formation  \citep{bluck2023fundamentalsignaturestarformation,kurinchivendhan2024originstarformationquenching}.

Our methodology involves a comprehensive analysis of the CAMELS simulation data, focusing on the quenched fraction of galaxies as a key indicator of quenching efficiency  \citep{xie2024quenchedgalaxieshow}. We employ a binning strategy to stratify galaxies by stellar mass and then further subdivide them based on the values of the feedback and cosmological parameters  \citep{xie2024quenchedgalaxieshow}. This allows us to isolate the effects of each parameter on the quenched fraction, while controlling for other factors  \citep{xie2024quenchedgalaxieshow}. Furthermore, we utilize statistical modeling techniques, such as multivariate logistic regression, to quantify the dependence of quenching efficiency on these parameters and to identify potential correlations and interactions. We model the quenched status of a galaxy as a binary variable, dependent on the input parameters  \citep{xie2024quenchedgalaxieshow}.

We derive several key metrics from our analysis, including the quenched fraction as a function of stellar mass and feedback/cosmological parameters \citep{xie2024quenchedgalaxieshow,xie2024quenchedgalaxieshow,geha2024sagasurveyivstar}, as well as the median specific star formation rate (sSFR) in each bin. We estimate the uncertainties on these metrics using bootstrap resampling techniques, providing a robust assessment of the statistical significance of our results. Additionally, we perform partial correlation analysis to isolate the direct effects of each parameter on the quenched fraction, controlling for stellar mass and other parameters \citep{porrasvalverde2024signatureblackholesquenched}. This allows us to identify the most influential factors driving quenching.

To validate our findings, we employ k-fold cross-validation techniques to assess the robustness of our regression models  \citep{narkedimilli2024predictingstellarmetallicitycomparative}. This ensures that our results are not driven by overfitting or sample variance. We also perform a series of robustness checks, repeating key analyses with alternative binning schemes and sSFR thresholds to confirm the stability of our conclusions  \citep{martin2024robustbayesianregressionastronomy,martin2024robustbayesianregressionastronomy}. These validation steps provide confidence in the reliability of our results and the generalizability of our findings  \citep{narkedimilli2024predictingstellarmetallicitycomparative,martin2024robustbayesianregressionastronomy,martin2024robustbayesianregressionastronomy}. We explore the parameter space and compare our findings to those of previous works to ensure our results are consistent with the current understanding of galaxy evolution  \citep{stoppa2023consistencytestscomparingastrophysical}.

Our analysis provides predictive insights for galaxy evolution models and offers a theoretical framework for interpreting future observational surveys aimed at understanding the quenching phenomenon  \citep{schawinski2018exploringgalaxyevolutiongenerative}. By quantifying the relative importance of different feedback and cosmological parameters, we can provide valuable constraints on the underlying physical processes driving galaxy evolution  \citep{lapi2025semiempiricalmodelsgalaxyformation}. This will help improve the accuracy and predictive power of galaxy evolution models, allowing them to better reproduce the observed properties of galaxies across cosmic time  \citep{li2024usinggalaxyevolutionsource}. The results can be used to improve the theoretical models which inform the observational surveys, and the observational surveys that improve the theoretical models  \citep{comparat2025crosscorrelationsoftxraysgalaxies}.

In future work, we plan to extend our analysis to higher redshifts, exploring the evolution of quenching efficiency over cosmic time \citep{mao2022revealingimpactsstellarmass,bravo2023galaxyquenchingtimescalesforensic}. This will provide a more complete picture of the quenching process and its dependence on feedback and cosmological parameters \citep{dou2025criticalroledarkmatter}. We also plan to investigate the role of different quenching mechanisms, such as morphological quenching and environmental quenching, in more detail \citep{mao2022revealingimpactsstellarmass,ellison2024galaxyevolutionpostmergerregime}. This will involve analyzing the morphology and environment of galaxies in the CAMELS simulations and correlating these properties with their star formation activity \citep{mao2022revealingimpactsstellarmass,bravo2023galaxyquenchingtimescalesforensic,ellison2024galaxyevolutionpostmergerregime}. Ultimately, this will lead to a more comprehensive understanding of the complex interplay between internal and external factors in regulating galaxy evolution.

\section{Methods}
\label{sec:methods}
\subsection{Data Acquisition and Preparation}
The foundation of this study rests upon the CAMELS (Cosmological and Astrophysical Models for Extremely Luminous Sources) project, a suite of cosmological hydrodynamical simulations. We utilize the publicly available data, specifically the IllustrisTNG and SIMBA simulation sets, each comprising 1000 simulations with varying cosmological and astrophysical parameters. The CAMELS simulations are particularly well-suited for this analysis due to their systematic variation of key parameters, enabling a disentangling of the effects of feedback and cosmology on galaxy evolution.

We begin by acquiring the galaxy-level data from the CAMELS database. This data is stored in \texttt{parquet} format for efficient storage and retrieval. Specifically, we load two primary dataframes: \texttt{galaxies\_full\_optimal.parquet}, containing detailed information on individual galaxies within the simulations, and \texttt{catalog\_params\_optimal.parquet}, providing the corresponding cosmological and feedback parameter values for each simulation. These dataframes are read into memory using the \texttt{pandas} library in Python, leveraging the \texttt{read\_parquet} function for optimized I/O performance.

The \texttt{galaxies\_full\_optimal.parquet} dataframe contains crucial information for each galaxy, including its star formation rate (SFR) and stellar mass (\texttt{M\_star}). The \texttt{catalog\_params\_optimal.parquet} dataframe contains the six parameters that are varied across the CAMELS simulations: two parameters controlling the efficiency of supernova feedback (\texttt{A\_SN1}, \texttt{A\_SN2}), two parameters controlling the efficiency of AGN feedback (\texttt{A\_AGN1}, \texttt{A\_AGN2}), the matter density parameter (\texttt{Omega\_m}), and the amplitude of the matter power spectrum (\texttt{sigma\_8}) \citep{villaescusanavarro2022camelsprojectpublicdata,lee2024zoomingcarpoolgplanenew}. Each simulation is uniquely identified by a \texttt{catalog\_number}.

\subsection{Calculation of Derived Quantities and Data Integration}
Following data loading, we compute the specific star formation rate (sSFR) for each galaxy, defined as the ratio of the SFR to the stellar mass (\texttt{sSFR = SFR / M\_star}) \citep{bauer2005specificstarformationrates}. This quantity serves as a key indicator of a galaxy's star-forming activity. We then define a galaxy as "quenched" if its sSFR falls below a threshold of $10^{-11}$ yr$^{-1}$ \citep{whitaker2017predictingquiescencedependencespecific,katsianis2020specificstarformationrate,leslie2020vlacosmos3ghzlarge}. A boolean column is added to the galaxy dataframe, indicating whether each galaxy meets this quenching criterion.

To link galaxy-level properties with the corresponding simulation parameters, we merge the \texttt{catalog\_params\_optimal.parquet} dataframe onto the \texttt{galaxies\_full\_optimal.parquet} dataframe using the \texttt{catalog\_number} as the common key. This ensures that each galaxy is associated with the correct values of \texttt{A\_SN1}, \texttt{A\_SN2}, \texttt{A\_AGN1}, \texttt{A\_AGN2}, \texttt{Omega\_m}, and \texttt{sigma\_8} from its parent simulation \citep{contardo2025effectsparametersgalaxyproperties}. The merging operation is performed using the \texttt{merge} function in \texttt{pandas} \citep{desanti2025fieldlevelsimulationbasedinferencegalaxy,ivanov2025fullshapeanalysissimulationbasedpriors}.

\subsection{Binning Strategy for Parameter Space Exploration}
To systematically explore the influence of stellar mass, feedback, and cosmological parameters on quenching, we employ a binning strategy. First, galaxies are divided into bins based on their stellar mass. We utilize logarithmic bins, specifically log(\texttt{M\_star}/M$_\odot$) = [8.5–9.5], [9.5–10.5], and [10.5–11.5] \citep{porrasvalverde2024signatureblackholesquenched}. These bins are chosen to ensure sufficient galaxy counts within each bin, providing robust statistical analysis.

Within each stellar mass bin, we further stratify galaxies based on the feedback and cosmological parameters \citep{vaughan2024samigalaxysurveypredicting}. For the feedback parameters (\texttt{A\_SN1}, \texttt{A\_SN2}, \texttt{A\_AGN1}, \texttt{A\_AGN2}) and the cosmological parameters (\texttt{Omega\_m}, \texttt{sigma\_8}), we divide their respective ranges into quantiles \citep{arangotoro2025cosmoswebhistorygalaxymigrations}. This approach ensures a uniform sampling across the parameter space, even if the underlying distributions are non-uniform. We experiment with different numbers of quantiles (e.g., quartiles or quintiles) to optimize the balance between resolution and statistical power.

For higher-order analysis, we explore the use of two-dimensional binning (e.g., \texttt{A\_SN1} vs. \texttt{A\_AGN1}) to capture potential interactions between parameters \citep{cappellari2002adaptivespatialbinning2d,cappellari2003adaptivespatialbinningintegralfield,cappellari2009voronoibinningoptimaladaptive}. In cases where multi-dimensional binning leads to sparse bins, we employ regression techniques to disentangle the effects of individual parameters without excessive binning.

\subsection{Calculation of Quenching Metrics and Uncertainty Estimation}
For each combination of stellar mass bin and parameter bin, we calculate the quenched fraction (\texttt{f\_quenched}), defined as the number of quenched galaxies (\texttt{N\_quenched}) divided by the total number of galaxies (\texttt{N\_total}) within that bin \citep{xie2024quenchedgalaxieshow}.
\begin{equation}
f_{\text{quenched}} = \frac{N_{\text{quenched}}}{N_{\text{total}}}
\end{equation}
In addition to the quenched fraction, we also compute the median sSFR within each bin to provide a continuous measure of star-forming activity \citep{banerjee2023clusteringphysicalpropertiesstarforming,shi2023naturevsnurturerevisiting}.

To quantify the uncertainties associated with the quenched fraction and median sSFR, we employ a bootstrap resampling technique \citep{sanderson2009xraymodellinggalaxycluster,mohammad2022creatingjackknifebootstrapestimates}. Within each bin, we resample galaxies with replacement a large number of times (e.g., 1000 times). For each resampled dataset, we recalculate the quenched fraction and median sSFR. The standard deviation of these resampled values is then used as an estimate of the uncertainty for each metric \citep{sanderson2009xraymodellinggalaxycluster,mohammad2022creatingjackknifebootstrapestimates}.

\subsection{Statistical Modeling and Regression Analysis}
To quantify the dependence of quenching efficiency on feedback and cosmological parameters, we perform multivariate logistic regression \citep{kuschel2023investigatingdominantenvironmentalquenching,xie2024quenchedgalaxieshow,rutkowski2025recentstarformation05z15}. The dependent variable is the quenched status of a galaxy (a binary variable indicating whether a galaxy is quenched or not), and the independent variables are the feedback parameters (\texttt{A\_SN1}, \texttt{A\_SN2}, \texttt{A\_AGN1}, \texttt{A\_AGN2}), the cosmological parameters (\texttt{Omega\_m}, \texttt{sigma\_8}), and the logarithm of the stellar mass (log(\texttt{M\_star})). The logistic regression model takes the form:
\begin{equation}
\text{logit}(p) = \beta_0 + \beta_1 A_{\text{SN1}} + \beta_2 A_{\text{SN2}} + \beta_3 A_{\text{AGN1}} + \beta_4 A_{\text{AGN2}} + \beta_5 \Omega_m + \beta_6 \sigma_8 + \beta_7 \log(M_{\text{star}}) + \dots
\end{equation}
where \( p \) is the probability of a galaxy being quenched, \( \beta_i \) are the regression coefficients, and the ellipsis indicates the potential inclusion of interaction terms \citep{romerogómez2024earlytypegalaxiesquenchedpresentday,zheng2025photometricobjectscosmicwebs}.

We also consider the inclusion of interaction terms (e.g., \texttt{A\_SN1} $\times$ \texttt{A\_AGN1}) in the regression model to capture potential non-linear effects and dependencies between parameters \citep{llorella2025exploringsymbolicregressiongenetic,tian2025interactivesymbolicregressionoffline}.

To isolate the direct effects of each parameter on the quenched fraction, we compute partial correlations between each parameter and the quenched fraction, controlling for stellar mass and the other parameters \citep{porrasvalverde2024signatureblackholesquenched}.

\subsection{Model Validation and Robustness Checks}
To assess the robustness of the regression results, we employ k-fold cross-validation \citep{hammond2024identifyingfittingeclipsemaps,sweet2024predictingexoplanetaryfeaturesresidual}. We divide the data into k folds (e.g., k=5) \citep{sweet2024predictingexoplanetaryfeaturesresidual}. For each fold, we fit the model on the remaining k-1 folds (the training set) and test its performance on the held-out fold (the testing set) \citep{sweet2024predictingexoplanetaryfeaturesresidual}. We repeat this process for each of the k folds, and record performance metrics such as accuracy and area under the receiver operating characteristic curve (AUC) \citep{hammond2024identifyingfittingeclipsemaps,sweet2024predictingexoplanetaryfeaturesresidual}. The cross-validation provides an estimate of the model's generalization performance and helps to prevent overfitting \citep{hammond2024identifyingfittingeclipsemaps,sweet2024predictingexoplanetaryfeaturesresidual}.

We also perform robustness checks by repeating key analyses with alternative binning schemes \citep{leslie2021modebymoderelativebinningfast,dainotti2024newbinningmethodchoose,chen2024evolutionxraygalaxycluster} and sSFR thresholds to confirm the stability of the results.

\subsection{Computational Implementation}
All data processing, analysis, and visualization are performed using Python, leveraging libraries such as \texttt{pandas}, \texttt{numpy}, \texttt{scikit-learn}, \texttt{matplotlib}, and \texttt{seaborn} \citep{giri2025astronomycalcpythontoolkitteaching}. Vectorized operations in \texttt{pandas} and \texttt{numpy} are used extensively to optimize computational efficiency \citep{turk2011highperformanceastrophysicalsimulationsanalysis}. For computationally intensive tasks such as bootstrap resampling and cross-validation, we leverage parallel processing using Python's \texttt{concurrent.futures} module to utilize all available CPU cores \citep{turk2011highperformanceastrophysicalsimulationsanalysis}.

\section{Results}
\label{sec:results}
\subsection{Quenched Fraction Trends}

This section presents a detailed analysis of star formation quenching efficiency across the CAMELS simulation suite, focusing on the impact of supernova (SN) and active galactic nucleus (AGN) feedback parameters, as well as cosmological parameters. We explore trends in quenched fractions, examine the relative importance of each parameter using statistical modeling, and investigate the interplay between these factors in driving galaxy quenching at \(z=0\).

\subsubsection{Stellar Mass Dependence}

We begin by examining the quenched fraction (\(f_{quenched}\)), defined as the fraction of galaxies with specific star formation rate (sSFR) below \(10^{-11} \text{ yr}^{-1}\), as a function of stellar mass and the varied simulation parameters. The distribution of sSFR for quenched and star-forming galaxies is shown in Figure \ref{fig:sSFR_hist}, illustrating a clear separation between the two populations. The stellar mass distributions for quenched and star-forming galaxies are shown in Figure \ref{fig:Mstar_hist}, indicating that star-forming galaxies tend to have lower stellar masses than quenched galaxies. Galaxies are binned into stellar mass ranges of width one dex.

A strong positive correlation exists between stellar mass and quenched fraction. In the highest mass bin considered, \(10.5 \leq \log_{10}(M_{star}/M_\odot) < 11.5\), \(f_{quenched}\) consistently exceeds 0.8 across all feedback parameter values. This indicates that galaxies in this mass range are nearly universally quenched, irrespective of the specific feedback implementation. In contrast, the quenched fraction varies significantly with feedback parameters in lower mass bins.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/sSFR_histogram_1_20250424_133143.png}
    \caption{\label{fig:sSFR_hist} Distribution of specific star formation rates (sSFR) for quenched and star-forming galaxies. A clear separation is observed between the two populations, with quenched galaxies exhibiting significantly lower sSFR values compared to star-forming galaxies. The quenched galaxies have a higher normalized count at lower sSFR values.
}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/Mstar_histogram_2_20250424_133143.png}
    \caption{\label{fig:Mstar_hist} The figure shows the stellar mass distribution, separated by quenching status. The red histogram represents quenched galaxies, while the blue histogram represents star-forming galaxies. The x-axis shows the logarithm of the stellar mass in solar masses, and the y-axis shows the normalized count. There are large differences in the distributions, with star-forming galaxies peaking at lower stellar masses than quenched galaxies.
}
\end{figure}

\subsubsection{Supernova Feedback}

The parameter \(A_{SN1}\), representing the SN wind energy per unit star formation rate, exhibits a notable *negative* correlation with \(f_{quenched}\) in low to intermediate mass galaxies. This trend is illustrated in Figure \ref{fig:fquenched_ASN1}, where the quenched fraction is plotted against \(A_{SN1}\) for different stellar mass bins. Specifically, for galaxies in the lowest mass bin (\(9.5 \leq \log_{10}(M_{star}/M_\odot) < 10.5\)), \(f_{quenched}\) decreases from approximately 0.40 in the lowest quartile of \(A_{SN1}\) values to around 0.24 in the highest quartile. This suggests that enhanced SN feedback can suppress quenching, potentially by maintaining a turbulent interstellar medium (ISM) and preventing the collapse of gas clouds necessary for sustained star formation. The distribution of $A_{SN1}$ for quenched and star-forming galaxies is shown in Figure \ref{fig:ASN1_hist}, further highlighting the differences between the two populations.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/fquenched_vs_A_SN1_20250424_133824.png}
    \caption{\label{fig:fquenched_ASN1} The figure shows the quenched fraction as a function of $A_{SN1}$ for three different stellar mass bins: $8.5 \leq \log_{10}(M_{star}/M_{\odot}) < 9.5$, $9.5 \leq \log_{10}(M_{star}/M_{\odot}) < 10.5$, and $10.5 \leq \log_{10}(M_{star}/M_{\odot}) < 11.5$. The quenched fraction decreases with increasing $A_{SN1}$ for all mass bins. At a given $A_{SN1}$, the quenched fraction is higher for more massive galaxies.
}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/A_SN1_histogram_3_20250424_133143.png}
    \caption{\label{fig:ASN1_hist} Distribution of $A_{SN1}$ for quenched and star-forming galaxies. The plot shows the normalized count of $A_{SN1}$ values, with quenched galaxies indicated in red and star-forming galaxies in blue. The distribution of $A_{SN1}$ exhibits differences between the two types of galaxies.
}
\end{figure}

\subsubsection{AGN Feedback}

Conversely, the AGN feedback parameter \(A_{AGN1}\), representing the AGN feedback energy per unit accretion rate, displays a positive correlation with \(f_{quenched}\) across all mass bins. This trend is visible in Figure \ref{fig:fquenched_AAGN1}, which shows the quenched fraction as a function of $A_{AGN1}$ for different stellar mass bins. For example, in the highest mass bin, \(f_{quenched}\) increases from approximately 0.72 in the lowest quartile of \(A_{AGN1}\) to approximately 0.94 in the highest quartile. Figure \ref{fig:AAGN1_hist} shows the distribution of $A_{AGN1}$ for quenched and star-forming galaxies, illustrating the higher $A_{AGN1}$ values for quenched galaxies. This result supports the established paradigm that AGN feedback plays a critical role in maintaining quenching in massive galaxies, by heating and/or expelling the gas reservoir.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/fquenched_vs_A_AGN1_20250424_133935.png}
    \caption{\label{fig:fquenched_AAGN1} Quenched fraction as a function of A\ensuremath{\_}AGN1 for different stellar mass bins. The quenched fraction increases with increasing A\ensuremath{\_}AGN1, with large differences seen between the different stellar mass bins.
}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/A_AGN1_histogram_5_20250424_133143.png}
    \caption{\label{fig:AAGN1_hist} The distribution of $A\_AGN1$ is shown, separated by quenching status. Star-forming galaxies are shown in blue, while quenched galaxies are shown in red. There are large differences between the two populations with quenched galaxies having higher $A\ensuremath{\_}AGN1$ values.
}
\end{figure}

\subsubsection{Other Feedback Parameters}

The parameters \(A_{SN2}\) (SN wind speed) and \(A_{AGN2}\) (AGN kinetic mode ejection speed) show weaker and less systematic trends compared to \(A_{SN1}\) and \(A_{AGN1}\). Figure \ref{fig:fquenched_ASN2} shows the quenched fraction as a function of $A_{SN2}$ for different stellar mass bins, indicating a weak dependence. Similarly, Figure \ref{fig:fquenched_AAGN2} shows the quenched fraction as a function of $A_{AGN2}$, also showing a weak dependence. The distributions of $A_{SN2}$ and $A_{AGN2}$ for quenched and star-forming galaxies are shown in Figure \ref{fig:ASN2_hist} and Figure \ref{fig:AAGN2_hist}, respectively. This suggests that the overall energy injected by feedback processes is more crucial for regulating quenching than the specific velocity of the outflows, at least within the parameter ranges explored in this study.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/fquenched_vs_A_SN2_20250424_133824.png}
    \caption{\label{fig:fquenched_ASN2} The figure displays the quenched fraction as a function of $A_{SN2}$ for three different stellar mass bins. The quenched fraction increases with stellar mass, with galaxies in the highest mass bin ($10.5 \leq \log_{10}(M_{star}/M_{\odot}) < 11.5$) showing a consistently high quenched fraction across all values of $A_{SN2}$. The quenched fraction shows a weak dependence on $A_{SN2}$ for each mass bin.
}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/A_SN2_histogram_4_20250424_133143.png}
    \caption{\label{fig:ASN2_hist} The distribution of $A_{SN2}$ is shown for both quenched and star-forming galaxies. The distributions show that star-forming galaxies have a higher density at smaller $A_{SN2}$ values than quenched galaxies.
}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/fquenched_vs_A_AGN2_20250424_133935.png}
    \caption{\label{fig:fquenched_AAGN2} The quenched fraction as a function of $A_{AGN2}$ for different stellar mass bins is shown. The quenched fraction is significantly higher for galaxies in the highest mass bin ($10.5 \leq \log_{10}(M_{star}/M_{\odot}) < 11.5$) compared to the lower mass bins. The quenched fraction appears to be relatively constant as a function of $A_{AGN2}$ for each mass bin.
}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/A_AGN2_histogram_6_20250424_133143.png}
    \caption{\label{fig:AAGN2_hist} Distribution of $A\_AGN2$ for quenched and star-forming galaxies. The normalized count is plotted against $A\_AGN2$. Overall, the star-forming galaxies tend to have slightly smaller $A\_AGN2$ values compared to quenched galaxies, but the differences are relatively small with significant overlap in the distributions.
}
\end{figure}

\subsubsection{Cosmological Parameters}

The cosmological parameters \(\Omega_m\) (matter density parameter) and \(\sigma_8\) (power spectrum normalization) also influence the quenched fraction. Higher values of both parameters are associated with an increased \(f_{quenched}\). This is consistent with the idea that denser cosmic environments and enhanced clustering, leading to earlier structure formation, favor quenching processes such as accelerated black hole growth and the formation of more massive halos, which more efficiently host quenching mechanisms.

\subsection{Statistical Modeling and Feature Importance}

To quantify the relative importance of each parameter in predicting galaxy quenching, we employ a logistic regression model. The target variable is a binary flag indicating whether a galaxy is quenched (sSFR \(< 10^{-11} \text{ yr}^{-1}\)). We use permutation feature importance to assess the contribution of each parameter to the model's performance.

\subsubsection{Permutation Feature Importance}

The permutation feature importance analysis reveals that \(\sigma_8\) is the most important parameter (importance mean \(\sim\)0.155), followed by \(A_{AGN1}\) (\(\sim\)0.148), \(\Omega_m\) (\(\sim\)0.128), and the logarithm of stellar mass (\(\log M_{star}\), \(\sim\)0.104). The supernova feedback parameter \(A_{SN1}\) also exhibits significant importance (\(\sim\)0.094). These results are summarized in Figure \ref{fig:permutation_importance}, which shows the permutation feature importances for all parameters. These results underscore the combined influence of cosmological environment, AGN feedback, and stellar mass on galaxy quenching.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/permutation_importance_20250424_133935.png}
    \caption{\label{fig:permutation_importance} The figure displays the permutation feature importances, quantifying the contribution of different features and their combinations to the model's performance. The x-axis represents the permutation importance (mean $\pm$ std), while the y-axis lists the features. The features "sigma\_8", "A\ensuremath{\_}AGN1", "Omega\_m", "logMstar", and "A\ensuremath{\_}SN1" show the largest permutation importance.
}
\end{figure}

\subsubsection{Logistic Regression Coefficients}

The coefficients of the logistic regression model further highlight the key drivers of quenching. The coefficients are shown in Figure \ref{fig:logreg_coefficients}. \(A_{AGN1}\) has a strong positive coefficient (+1.87), indicating a strong positive association with quenching. Similarly, \(\sigma_8\) (+1.66), \(\log M_{star}\) (+1.41), and \(\Omega_m\) (+1.13) also have positive coefficients. In contrast, \(A_{SN1}\) has a negative coefficient (–0.97), reflecting its role in suppressing quenching. The magnitudes of these coefficients emphasize the substantial impact of AGN feedback and cosmological parameters on driving galaxy quenching.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/logreg_coefficients_20250424_133935.png}
    \caption{\label{fig:logreg_coefficients} The figure shows the Logistic Regression Coefficients for the full model. Large differences are seen in the magnitude and sign of the coefficients, indicating varying degrees of influence from different combinations of cosmological parameters (e.g., $\sigma_8$, $\Omega_m$, $logMstar$) and survey parameters (A\ensuremath{\_}SN1, A\ensuremath{\_}SN2, A\ensuremath{\_}AGN1, A\ensuremath{\_}AGN2) on the logistic regression model.
}
\end{figure}

\subsubsection{Partial Correlations}

Partial correlation analysis, which measures the correlation between two variables while controlling for the effects of other variables, confirms the results obtained from the regression analysis. \(A_{AGN1}\), \(\sigma_8\), and \(\Omega_m\) exhibit positive partial correlations with quenching (with values around +0.15, +0.16, and +0.14, respectively), while \(A_{SN1}\) shows a negative partial correlation (–0.11).

\subsubsection{Model Performance}

The full logistic regression model, including all parameters and their interactions, achieves a mean accuracy of approximately 66.5\% and an area under the receiver operating characteristic curve (AUC) of approximately 0.685. A simplified model using only the top three most important features (\(\sigma_8\), \(A_{AGN1}\), and \(\Omega_m\)) yields slightly lower performance (accuracy \(\sim\)64.5\% and AUC \(\sim\)0.645). This suggests that the majority of the predictive power is concentrated in a few key parameters, though the inclusion of other parameters does provide some additional predictive power.

\subsection{Mass Dependence and Parameter Interplay}

The analysis reveals that the dominant quenching mechanisms differ across stellar mass ranges. AGN feedback appears to be the primary driver of quenching in high-mass galaxies, while SN feedback plays a more regulatory role in low to intermediate mass systems.

To further explore the interplay between parameters, we generate two-dimensional heatmaps showing the quenched fraction as a function of pairs of parameters. Figure \ref{fig:heatmap_fquenched} shows the heatmap of the quenched fraction as a function of $A_{AGN1}$ and $A_{SN1}$ for galaxies with stellar masses in the range $8.5 \leq \log_{10}(M_{\rm star}/M_{\odot}) < 9.5$. Figure \ref{fig:heatmap_fquenched_2} and Figure \ref{fig:heatmap_fquenched_3} show the same heatmap for galaxies with stellar masses in the range $9.5 \leq \log_{10}(M_{\star}/M_{\odot}) < 10.5$ and $10.5 \leq \log_{10}(M_{\star}/M_{\odot}) < 11.5$, respectively. These visualizations indicate that the highest quenched fractions occur in regions where \(A_{AGN1}\) is high and \(A_{SN1}\) is low. This suggests a synergistic effect, where quenching is most efficient when AGN feedback is strong and SN feedback is weak. This also suggests that the quenching is not simply a linear combination of the effects of the parameters, but that there are non-linear interactions between them.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/fquenched_heatmap_SN1_AGN1_8_5_10_M_star_M_9_5_20250424_133935.png}
    \caption{\label{fig:heatmap_fquenched} Heatmap of the quenched fraction ($f_{\rm quenched}$) as a function of $A_{\rm AGN1}$ and $A_{\rm SN1}$ for galaxies with stellar masses in the range $8.5 \leq \log_{10}(M_{\rm star}/M_{\odot}) < 9.5$. The quenched fraction increases with increasing $A_{\rm AGN1}$ and *decreasing* $A_{\rm SN1}$, with a more pronounced increase along the $A_{\rm AGN1}$ axis.
}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/fquenched_heatmap_SN1_AGN1_9_5_10_M_star_M_10_5_20250424_133935.png}
    \caption{\label{fig:heatmap_fquenched_2} Quenched fraction heatmap for galaxies with stellar masses in the range $9.5 \leq \log_{10}(M_{\star}/M_{\odot}) < 10.5$. The x-axis represents $A_{AGN1}$ and the y-axis represents $A_{SN1}$. The colorbar indicates the quenched fraction, $f_{\mathrm{quenched}}$. The quenched fraction increases as you move towards larger values of $A_{AGN1}$.
}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project6/plots/fquenched_heatmap_SN1_AGN1_10_5_10_M_star_M_11_5_20250424_133935.png}
    \caption{\label{fig:heatmap_fquenched_3} Quenched fraction of galaxies with stellar mass $10.5 \leq \log_{10}(M_{\star}/M_{\odot}) < 11.5$ as a function of $A_{\rm AGN1}$ and $A_{\rm SN1}$. The quenched fraction increases with increasing $A_{\rm AGN1}$.
}
\end{figure}

\section{Conclusions}
\label{sec:conclusions}

In this study, we have systematically investigated the efficiency of star formation quenching across a wide range of feedback and cosmological parameters using the CAMELS simulations. Our primary goal was to disentangle the complex interplay between supernova (SN) feedback, active galactic nucleus (AGN) feedback, and cosmological parameters in driving the cessation of star formation in galaxies at $z=0$. By leveraging the extensive parameter space coverage of the CAMELS simulations, we aimed to provide quantitative insights into the physical drivers of quenching and offer predictive guidance for galaxy evolution models and future observational surveys.

We utilized galaxy-level data from the IllustrisTNG and SIMBA simulation suites within CAMELS, focusing on key parameters such as SN feedback efficiency (\(A_{SN1}\), \(A_{SN2}\)), AGN feedback efficiency (\(A_{AGN1}\), \(A_{AGN2}\)), matter density parameter (\(\Omega_m\)), and the amplitude of the matter power spectrum (\(\sigma_8\)). We calculated the quenched fraction (\(f_{quenched}\)) for galaxies in different stellar mass bins and explored the dependence of \(f_{quenched}\) on the aforementioned parameters. Statistical techniques, including permutation feature importance, logistic regression, and partial correlation analysis, were employed to quantify the relative importance of each parameter and to uncover potential interactions.

Our results reveal a nuanced picture of galaxy quenching. We found that AGN feedback, particularly the AGN feedback energy per accretion (\(A_{AGN1}\)), is the dominant quenching mechanism in massive galaxies, while SN feedback exhibits a more regulatory effect in lower-mass systems. Specifically, an increase in \(A_{AGN1}\) correlates with a higher quenched fraction, especially in galaxies with \(\log_{10}(M_{star}/M_\odot) \geq 10.5\). Conversely, higher SN wind energy (\(A_{SN1}\)) tends to *decrease* the quenched fraction in low to intermediate mass galaxies. Furthermore, we observed that cosmological parameters (\(\Omega_m\) and \(\sigma_8\)) positively influence quenching efficiency, suggesting that denser cosmic environments and enhanced clustering promote quenching.

From this study, we have learned that the efficiency of star formation quenching is not solely determined by internal feedback processes but is also significantly influenced by the broader cosmological context. The interplay between AGN feedback, SN feedback, and cosmological parameters is complex and nonlinear, with stellar mass acting as a crucial modulator. Our findings underscore the importance of accurately representing AGN feedback in galaxy evolution models, particularly for massive galaxies, and of considering the environmental context when studying quenching. The results also suggest that future models should adopt a joint, nonlinear approach to capture the synergistic effects that operate across different mass regimes.

In conclusion, our analysis of the CAMELS simulations provides a comprehensive map of star formation quenching efficiency across feedback and cosmological parameter space. We have demonstrated that AGN feedback, SN feedback, and cosmological parameters all play significant, interconnected roles in driving the cessation of star formation in galaxies. These findings offer valuable insights for refining galaxy evolution models and interpreting observational data from future surveys.
\

\bibliography{bibliography}{}
\bibliographystyle{aasjournal}

\end{document}

### 2025-04-25 src/paper_node.py
update

@@ -38,7 +38,7 @@ def abstract_node(state: GraphState, config: RunnableConfig):
     """
 
     print(f"Writing Abstract...", end="", flush=True)
-    PROMPT = abstract_prompt(state['idea']['Idea'])
+    PROMPT = abstract_prompt(state)
     result = llm.invoke(PROMPT).content
     
     # Get the abstract
@@ -209,6 +209,12 @@ def plots_node(state: GraphState, config: RunnableConfig):
     files = [f for f in folder_path.iterdir() if f.is_file()]
     num_images = len(files)
 
+    # If more than 25, randomly select 25
+    if num_images > 25:
+        random.seed(1)  # for reproducibility
+        files = random.sample(files, 25)
+        num_images = 25
+
     batch_size = 7
     all_results = []
 
@@ -240,15 +246,7 @@ def plots_node(state: GraphState, config: RunnableConfig):
         # save paper
         save_paper(state, state['files']['Paper_v1'])
 
-        #all_results.append(results)
-
-    # Optionally, combine all sections into one
-    #final_results = "\n".join(all_results)
-
-    # Save and compile
-    #state['paper']['Results'] = final_results
-    #state['paper']['Results'] = results
-    #save_paper(state, state['files']['Paper_v1'])
+    # compile paper
     print('done')
     compile_latex(state, state['files']['Paper_v1'])
 

### 2025-04-25 src/prompts.py

@@ -111,10 +111,10 @@ Respond in the following format:
 
 
 
-def abstract_prompt(idea):
+def abstract_prompt(state):
     
     return [SystemMessage(content="""You are a scientific writer"""),
-            HumanMessage(content=rf"""Given the context below, get a title and write an abstract for a scientific paper. Please, follow these guidelines:
+            HumanMessage(content=rf"""Given the idea, methods, and results below, get a title and write an abstract for a scientific paper. Please, follow these guidelines:
 - What are we trying to do and why is it relevant?
 - Why is this hard? 
 - How do we solve it (i.e. our contribution!)
@@ -123,17 +123,23 @@ def abstract_prompt(idea):
 
 Please make sure the abstract reads smoothly and is well-motivated. This should be one continuous paragraph with no breaks between the lines.
 
-Context:
-{idea}
+Idea:
+{state['idea']['Idea']}
 
-**Respond in this format**
+Methods:
+{state['idea']['Methods']}
+
+Results:
+{state['idea']['Results']}
+
+**Respond in exactly this format**
 
 ```json
 {{"Title": "The title of the paper",
 "Abstract": "The abstract of the paper"}}
 ```
 
-Make sure the text is in LaTex. 
+Make sure the text is in LaTex. Do not write equations or citations in the abstract.
 """)]
 
 

### 2025-04-25 main.py
update

@@ -13,7 +13,7 @@ graph = build_graph(mermaid_diagram=True)
 
 # run the graph
 result = asyncio.run(graph.ainvoke(
-    {"files":{"Folder":       "Project6",   #name of folder containing input files
+    {"files":{"Folder":       "Project4",   #name of folder containing input files
               "Idea":         "idea.md",    #name of file containing idea description
               "Methods":      "methods.md", #name of file with methods description
               "Results":      "results.md", #name of file with results description

### 2025-04-26 main.py
added support for PDF files and improve introduction prompt

@@ -13,7 +13,7 @@ graph = build_graph(mermaid_diagram=True)
 
 # run the graph
 result = asyncio.run(graph.ainvoke(
-    {"files":{"Folder":       "Project4",   #name of folder containing input files
+    {"files":{"Folder":       "Project7",   #name of folder containing input files
               "Idea":         "idea.md",    #name of file containing idea description
               "Methods":      "methods.md", #name of file with methods description
               "Results":      "results.md", #name of file with results description

### 2025-04-26 setup.py

@@ -18,6 +18,8 @@ setup(name='AstroPilot',
                         'requests',
                         'typing-extensions',
                         'pdflatex',
-                        'tqdm'],
+                        'tqdm',
+                        'pymupdf',
+                        'pillow'],
     include_package_data=True,
     zip_safe=False)

### 2025-04-26 src/prompts.py

@@ -195,13 +195,13 @@ Please respond in this format:
 In <INTRODUCTION>, place the introduction of the paper. Please, follow these guidelines:
 - Write in LaTex
 - Longer version of the Abstract, i.e. of the entire paper
-- Text should contain at least 10 paragraphs. Each paragraph should have 5 sentences
 - What are we trying to do and why is it relevant?
 - Why is this hard? 
 - How do we solve it (i.e. our contribution!)
 - How do we verify that we solved it (e.g. Experiments and results)
 - Extra space? Future work!
 - Do not write subsections titles in capital letters
+- The first letter of subsection titles should be in capital
 
 Please make sure the introduction reads smoothly and is well-motivated. If you use equations, please write them in LaTeX.
 """)]
@@ -271,6 +271,7 @@ Follow these guidelines:
 - Do not write the bibliography
 - Write in LaTex
 - Do not write subsections titles in capital letters
+- The first letter of subsection titles should be in capital
 - The text you write, is going to be placed inside a section of a LaTeX paper. Thus, you can create subsections and subsubsections, but not sections 
 
 Respond in this format:
@@ -302,6 +303,7 @@ Follow these guidelines:
 - Do not write the bibliography
 - Write in LaTex
 - Do not write subsections titles in capital letters
+- The first letter of subsection titles should be in capital
 - The text you write, is going to be placed inside a section of a LaTeX paper. Thus, you can create subsections and subsubsections, but not sections
 - You can summarize the results, but do not write a conclusions subsection as there will be a conclusions section written later on
 - The text you write will be placed inside a 2-columns LaTeX document that start with \\documentclass[twocolumn]{{aastex631}}. Thus, for long equations and wide tables, either use the full paper width or write the equations and table so that they occupy a single column.
@@ -370,6 +372,7 @@ Follow these guidelines:
 - Do not write the bibliography
 - Write in LaTex
 - Do not write subsections titles in capital letters
+- The first letter of subsection titles should be in capital
 - Do not write words or sentences between *. E.g. instead of *integrated*, write integrated
 
 Respond in this format:

### 2025-04-26 src/llm.py
added support for PDF files and improve introduction prompt

@@ -17,6 +17,6 @@ PERPLEXITY_API_KEY = os.getenv("PERPLEXITY_API_KEY")
 #llm  = ChatGoogleGenerativeAI(model="gemini-pro", temperature=0)
 #llm  = ChatGroq(model="gemma2-9b-it", temperature=0.7)
 llm = ChatGoogleGenerativeAI(model="gemini-2.0-flash", temperature=0.7)
-#llm = ChatGoogleGenerativeAI(model="gemini-2.5-flash-preview-04-17", temperature=0)
+#llm = ChatGoogleGenerativeAI(model="gemini-2.5-flash-preview-04-17", temperature=0.7)
 #llm2 = ChatOpenAI(model="gpt-4", temperature=0.5)
 #llm3 = ChatAnthropic(model="claude-3-5-sonnet-20240620", temperature=0)

### 2025-04-26 src/paper_node.py

@@ -1,10 +1,10 @@
 from langchain_core.runnables import RunnableConfig
-import sys,os,re,base64
+import sys,os,re,random,base64
 from pathlib import Path
 from tqdm import tqdm
 import asyncio
 from functools import partial
-import random
+import fitz  # PyMuPDF
 
 from src.parameters import GraphState
 from src.prompts import *
@@ -89,13 +89,6 @@ def section_node(state: GraphState, config: RunnableConfig, section_name: str,
     result = llm.invoke(prompt).content
     section_text = extract_latex_block(state, result, section_name)
 
-    # Try to extract section content via markers
-    #pattern = fr"\\begin{{{section_name}}}(.*?)\\end{{{section_name}}}"
-    #match = re.search(pattern, result, re.DOTALL)
-    #if match:
-    #    section_text = match.group(1).strip()
-    #else:
-    #    raise ValueError(f"No valid \\begin{{{section_name}}} section found.")
     state['paper'][section_name] = section_text
 
     # --- Step 2: Optional self-reflection ---
@@ -149,55 +142,18 @@ def conclusions_node(state: GraphState, config: RunnableConfig):
 
 #######################################################################################
 def image_to_base64(image_path):
-    with open(image_path, "rb") as file:
-        binary_data = file.read()
-        image_data = base64.b64encode(binary_data).decode('utf-8')
-        return image_data
-
-#def plots_node(state: GraphState, config: RunnableConfig):
-#    """
-#    This function deals with the plots generated
-#    """
-
-#    folder_path = Path(f"{state['files']['Folder']}/{state['files']['Plots']}")
-#    files = [f for f in folder_path.iterdir() if f.is_file()]
-#    num_images = len(files)
-
-#    # Select a random subset of up to 10 images
-#    random.seed(1)  #use a seed to be able to reproduce results
-#    selected_files = random.sample(files, min(num_images, 15))
-
-#    # do a loop over all images
-#    images = {}
-#    for i, file in enumerate(tqdm(selected_files, desc="Processing figures")):
-
-#        image = image_to_base64(file)
-
-#        PROMPT = caption_prompt(state, image)
-#        result = llm.invoke(PROMPT).content
-#        caption = extract_latex_block(state, result, "Caption")
-#        caption = LaTeX_checker(state, caption)  #make sure is written in LaTeX
-#        images[f"image{i}"] = {'name': file.name, 'caption': caption}
-
[…]

### 2025-04-26 src/paper_node.py
added temporary files

@@ -1,5 +1,5 @@
 from langchain_core.runnables import RunnableConfig
-import sys,os,re,random,base64
+import sys,os,re,random,base64,json
 from pathlib import Path
 from tqdm import tqdm
 import asyncio
@@ -14,20 +14,55 @@ from src.literature import process_tex_file_with_references
 from src.latex import compile_latex, save_paper, save_bib, process_bib_file
 
 
+def temp_file(fin, action, text=None, json_file=False):
+    """
+    This function reads or writes the content of a temporary file
+    fin:  the name of the file
+    action: either 'read' of 'write'
+    text: when action is 'write', the text to write
+    json: whether the file is json or not
+    """
+
+    if action=='read':
+        with open(fin, 'r', encoding='utf-8') as f:
+            if json_file:
+                return json.load(f)
+            else:
+                return f.read()
+    elif action=='write':
+        with open(fin, 'w', encoding='utf-8') as f:
+            if json_file:
+                json.dump(text, f, indent=2)
+            else:
+                f.write(text)
+    else:
+        raise Exception("wrong action chosen!")
+    
+
 def keywords_node(state: GraphState, config: RunnableConfig):
     """
     This agent is in charge of getting the keywords for the paper
     """
 
-    # Extract keywords
-    PROMPT = keyword_prompt(state)
-    result = llm.invoke(PROMPT).content
-    keywords = extract_latex_block(state, result, "Keywords")
-    
-    # Avoid adding \ to the end
-    keywords = keywords.replace("\\", "")
+    # temporary file with the selected keywords
+    f_temp = Path(f"{state['files']['Temp']}/Keywords.tex")
 
-    print(f'Selected keywords: {keywords}')
+    if f_temp.exists():
+        keywords = temp_file(f_temp, 'read')
+
+    else:
+
+        # Extract keywords
+        PROMPT = keyword_prompt(state)
+        result = llm.invoke(PROMPT).content
+        keywords = extract_latex_block(state, result, "Keywords")
+    
+        # Avoid adding \ to the end
+        keywords = keywords.replace("\\", "")
+
+        # write results to temporary file
+        temp_file(f_temp, 'write', keywords)
+        print(f'Selected keywords: {keywords}')
     
     return {'paper': {**state['paper'], 'Keywords': keywords}}
 
@@ -37,33 +72,46 @@ def abstract_node(state: GraphState, config: RunnableConfig):
     This node gets the title and the abstract of the paper
     """
 
[…]

### 2025-04-26 main.py
added temporary files

@@ -13,7 +13,7 @@ graph = build_graph(mermaid_diagram=True)
 
 # run the graph
 result = asyncio.run(graph.ainvoke(
-    {"files":{"Folder":       "Project7",   #name of folder containing input files
+    {"files":{"Folder":       "Project8",   #name of folder containing input files
               "Idea":         "idea.md",    #name of file containing idea description
               "Methods":      "methods.md", #name of file with methods description
               "Results":      "results.md", #name of file with results description

### 2025-04-26 src/parameters.py

@@ -28,6 +28,7 @@ class FILES(TypedDict):
     Paper_v4: str     #name of the file containing the version 4 of the paper
     Error: str        #name of the error file
     LaTeX_log: str    #name of the file with the LaTeX log (when compiling it)
+    Temp: str         #name of the folder with the temporary LaTeX files
 
 # Idea class
 class IDEA(TypedDict):

### 2025-04-26 src/reader.py

@@ -19,7 +19,8 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
                       "Paper_v3":  "paper_v3.tex",
                       "Paper_v4":  "paper_v4.tex",
                       "Error":     "Error.txt",
-                      "LaTeX_log": "LaTeX_compilation.log"}
+                      "LaTeX_log": "LaTeX_compilation.log",
+                      "Temp":      f"{state['files']['Folder']}/Temp"}
     idea = {}
     
     # read input files
@@ -59,10 +60,12 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
         if not(os.path.exists(f_in)):
             os.system(f"cp LaTeX/{f} {state['files']['Folder']}")
 
+    # create a folder to save LaTeX progress
+    os.makedirs(state['files']['Temp'], exist_ok=True)
+
     # deal with repeated plots
     plots_dir    = Path(f"{state['files']['Folder']}/{state['files']['Plots']}")
     repeated_dir = Path(f"{plots_dir}_repeated")
-    repeated_dir.mkdir(exist_ok=True)
 
     # Hash dictionary
     hash_dict = {}
@@ -76,6 +79,7 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
                 file_hash = hashlib.md5(f.read()).hexdigest()
     
             if file_hash in hash_dict:
+                repeated_dir.mkdir(exist_ok=True)
                 # This is a repeated file: copy it to repeated_plots
                 print(f"Repeated: {file.name} (same as {hash_dict[file_hash].name})")
                 shutil.move(file, repeated_dir / file.name)

### 2025-04-28 src/paper_node.py
update

@@ -341,10 +341,29 @@ def check_references(state: GraphState, text: str)-> str:
         
 #######################################################################################
 async def add_citations_async(state, text, section_name):
-    loop = asyncio.get_event_loop()
-    func = partial(process_tex_file_with_references, text)
-    new_text, references = await loop.run_in_executor(None, func)
-    new_text = clean_section(new_text, section_name)
+    """
+    This is the actual function that calls perplexity and gets the new text 
+    and the references.
+    """
+    f_temp1 = Path(f"{state['files']['Temp']}/{section_name}_w_citations.tex")
+    f_temp2 = Path(f"{state['files']['Temp']}/{section_name}.bib")
+
+    # check if this has already been done
+    if f_temp1.exists():
+        new_text   = temp_file(f_temp1, 'read')
+        references = temp_file(f_temp2, 'read')
+
+    else:
+        
+        loop = asyncio.get_event_loop()
+        func = partial(process_tex_file_with_references, text)
+        new_text, references = await loop.run_in_executor(None, func)
+        new_text = clean_section(new_text, section_name)
+
+        # save temporary file
+        temp_file(f_temp2, 'write', references)
+        temp_file(f_temp1, 'write', new_text)
+        
     print(f'    {section_name} done')
     return section_name, new_text, references
 
@@ -393,11 +412,20 @@ async def citations_node(state: GraphState, config: RunnableConfig):
     # make a last clean up of the sections
     print("Making a final check to the sections...")
     for section_name in sections:
-        PROMPT = clean_section_prompt(state, state['paper'][section_name])
-        result = llm.invoke(PROMPT).content
-        section_text = extract_latex_block(state, result, "Text")
-        section_text = LaTeX_checker(state, section_text)          #check LaTeX
-        section_text = clean_section(section_text, section_name)   #remove unwanted LaTeX text
+
+        f_temp = Path(f"{state['files']['Temp']}/{section_name}_w_citations2.tex")
+
+        # check if this has already been done
+        if f_temp.exists():
+            section_text = temp_file(f_temp, 'read')
+        else:
+            PROMPT = clean_section_prompt(state, state['paper'][section_name])
+            result = llm.invoke(PROMPT).content
+            section_text = extract_latex_block(state, result, "Text")
+            section_text = LaTeX_checker(state, section_text)          #check LaTeX
+            section_text = clean_section(section_text, section_name)   #remove unwanted LaTeX text
[…]

### 2025-04-29 main.py
update

@@ -13,11 +13,12 @@ graph = build_graph(mermaid_diagram=True)
 
 # run the graph
 result = asyncio.run(graph.ainvoke(
-    {"files":{"Folder":       "Project8",   #name of folder containing input files
+    {"files":{"Folder":       "Project5",   #name of folder containing input files
               "Idea":         "idea.md",    #name of file containing idea description
               "Methods":      "methods.md", #name of file with methods description
               "Results":      "results.md", #name of file with results description
-              "Plots":        "plots"}      #name of folder containing plots
+              "Plots":        "plots"},     #name of folder containing plots
+     "llm": {"model": "gemini-2.0-flash"},  #name of the LLM model to use
      }, config))
 
 # End timer and report duration in minutes and seconds

### 2025-04-29 src/llm.py
update

@@ -16,7 +16,8 @@ PERPLEXITY_API_KEY = os.getenv("PERPLEXITY_API_KEY")
 #llm  = ChatGroq(model="llama3-8b-8192", temperature=0)
 #llm  = ChatGoogleGenerativeAI(model="gemini-pro", temperature=0)
 #llm  = ChatGroq(model="gemma2-9b-it", temperature=0.7)
-llm = ChatGoogleGenerativeAI(model="gemini-2.0-flash", temperature=0.7)
+llm = ChatGoogleGenerativeAI(model="gemini-2.0-flash", temperature=0.7,
+                             max_output_tokens=8192)
 #llm = ChatGoogleGenerativeAI(model="gemini-2.5-flash-preview-04-17", temperature=0.7)
 #llm2 = ChatOpenAI(model="gpt-4", temperature=0.5)
 #llm3 = ChatAnthropic(model="claude-3-5-sonnet-20240620", temperature=0)

### 2025-04-29 src/paper_node.py

@@ -1,5 +1,5 @@
 from langchain_core.runnables import RunnableConfig
-import sys,os,re,random,base64,json
+import sys,os,re,random,base64,json,time
 from pathlib import Path
 from tqdm import tqdm
 import asyncio
@@ -8,35 +8,10 @@ import fitz  # PyMuPDF
 
 from src.parameters import GraphState
 from src.prompts import *
-from src.llm import llm
-from src.tools import json_parser, fixer, LaTeX_checker, clean_section, extract_latex_block
+from src.tools import json_parser, fixer, LaTeX_checker, clean_section, extract_latex_block, LLM_call, temp_file
 from src.literature import process_tex_file_with_references
 from src.latex import compile_latex, save_paper, save_bib, process_bib_file
 
-
-def temp_file(fin, action, text=None, json_file=False):
-    """
-    This function reads or writes the content of a temporary file
-    fin:  the name of the file
-    action: either 'read' of 'write'
-    text: when action is 'write', the text to write
-    json: whether the file is json or not
-    """
-
-    if action=='read':
-        with open(fin, 'r', encoding='utf-8') as f:
-            if json_file:
-                return json.load(f)
-            else:
-                return f.read()
-    elif action=='write':
-        with open(fin, 'w', encoding='utf-8') as f:
-            if json_file:
-                json.dump(text, f, indent=2)
-            else:
-                f.write(text)
-    else:
-        raise Exception("wrong action chosen!")
     
 
 def keywords_node(state: GraphState, config: RunnableConfig):
@@ -54,7 +29,7 @@ def keywords_node(state: GraphState, config: RunnableConfig):
 
         # Extract keywords
         PROMPT = keyword_prompt(state)
-        result = llm.invoke(PROMPT).content
+        state, result = LLM_call(PROMPT, state)
         keywords = extract_latex_block(state, result, "Keywords")
     
         # Avoid adding \ to the end
@@ -62,9 +37,11 @@ def keywords_node(state: GraphState, config: RunnableConfig):
 
         # write results to temporary file
         temp_file(f_temp, 'write', keywords)
-        print(f'Selected keywords: {keywords}')
+        
+    print(f"Selected keywords: {keywords} {state['tokens']['ti']} {state['tokens']['to']}")
     
-    return {'paper': {**state['paper'], 'Keywords': keywords}}
+    return {'paper': {**state['paper'], 'Keywords': keywords},
+            'tokens': state['tokens']}
 
 
 def abstract_node(state: GraphState, config: RunnableConfig):
[…]

### 2025-04-29 src/parameters.py

@@ -1,4 +1,4 @@
-from typing_extensions import TypedDict
+from typing_extensions import TypedDict, Any
 from langchain_core.messages import AnyMessage, HumanMessage, SystemMessage, AIMessage
 from typing import Annotated, Literal
 from langgraph.graph.message import add_messages
@@ -29,12 +29,26 @@ class FILES(TypedDict):
     Error: str        #name of the error file
     LaTeX_log: str    #name of the file with the LaTeX log (when compiling it)
     Temp: str         #name of the folder with the temporary LaTeX files
+    LLM_calls: str    #name of the file with the calls to the LLM
 
 # Idea class
 class IDEA(TypedDict):
     Idea: str
     Methods: str
     Results: str
+
+# Token class
+class TOKENS(TypedDict):
+    ti: int #total input tokens
+    to: int #total output tokens 
+    i:  int #input tokens (just for individual calls or functions)
+    o:  int #output tokens (just for individual calls or functions)
+
+# LLM class
+class LLM(TypedDict):
+    model: str
+    max_output_tokens: int
+    llm: Any
     
 # Graph state class
 class GraphState(TypedDict):
@@ -42,3 +56,5 @@ class GraphState(TypedDict):
     files: FILES
     idea: IDEA
     paper: PAPER
+    tokens: TOKENS
+    llm: LLM

### 2025-04-29 src/prompts.py

@@ -113,15 +113,16 @@ Respond in the following format:
 
 def abstract_prompt(state):
     
-    return [SystemMessage(content="""You are a scientific writer"""),
+    return [SystemMessage(content="""You are an astrophysicist"""),
             HumanMessage(content=rf"""Given the idea, methods, and results below, get a title and write an abstract for a scientific paper. Please, follow these guidelines:
-- What are we trying to do and why is it relevant?
-- Why is this hard? 
-- How do we solve it (i.e. our contribution!)
-- How do we verify that we solved it (e.g. Experiments and results)
+- Briefly describe the problem
+- Briefly describe how we try to solve it
+- Mention the dataset and methods used
+- Briefly describe the results
 - Write the abstract in LaTex
-
-Please make sure the abstract reads smoothly and is well-motivated. This should be one continuous paragraph with no breaks between the lines.
+- Do not write equations or citations in the abstract
+- Abstract should be a single paragraph, no sections, subsections, or breaks between lines.
+- Please make sure the abstract reads smoothly and is well-motivated.
 
 Idea:
 {state['idea']['Idea']}
@@ -138,34 +139,39 @@ Results:
 {{"Title": "The title of the paper",
 "Abstract": "The abstract of the paper"}}
 ```
-
-Make sure the text is in LaTex. Do not write equations or citations in the abstract.
 """)]
 
 
 def abstract_reflection(state):
 
-    return [SystemMessage(content="""Your are a cosmologist writing a scientific paper."""),
-            HumanMessage(content=rf"""Rewrite the above abstract given the current abstract and the original idea to make it more clear. Abstract should be a single paragraph, no sections, subsections, or breaks between lines.
+    return [SystemMessage(content="""Your are an astrophysicist"""),
+            HumanMessage(content=rf"""Rewrite the below abstract to make it more clear. You are given the idea, methods, and results of the paper together with the previously written abstract.
 
-Original Idea
-Title: {state['paper']['Title']}
-Description: {state['idea']['Idea']}
+Idea:
+{state['idea']['Idea']}
 
-Abstract: {state['paper']['Abstract']}
+Methods:
+{state['idea']['Methods']}
 
-Respond with in the following format:
+Results:
+{state['idea']['Results']}
+
+Previous abstract:
+{state['paper']['Abstract']}
+
+**Respond in exactly this format**
 
 \\begin{{Abstract}}
 <ABSTRACT>
 \\end{{Abstract}}
+            
[…]

### 2025-04-29 src/reader.py

@@ -3,8 +3,21 @@ import sys,os
 from pathlib import Path
 import hashlib
 import shutil
+from langchain_groq import ChatGroq
+from langchain_openai import ChatOpenAI
+from langchain_anthropic import ChatAnthropic
+from langchain_google_genai import ChatGoogleGenerativeAI
+from dotenv import load_dotenv
 
 from src.parameters import GraphState
+
+
+load_dotenv()
+GOOGLE_API_KEY     = os.getenv("GOOGLE_API_KEY")
+PERPLEXITY_API_KEY = os.getenv("PERPLEXITY_API_KEY")
+#OPENAI_API_KEY    = os.getenv("OPENAI_API_KEY")
+#ANTHROPIC_API_KEY = os.getenv("ANTHROPIC_API_KEY")
+#GROQ_API_KEY      = os.getenv("GROQ_API_KEY")
 
 
 def preprocess_node(state: GraphState, config: RunnableConfig):
@@ -12,6 +25,24 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
     This agent reads the input files, clean up files, and set the name of some files
     """
 
+    # set the LLM
+    if state['llm']['model']=='gemini-2.0-flash':
+        state['llm']['llm'] = ChatGoogleGenerativeAI(model="gemini-2.0-flash", temperature=0.7,
+                                                     max_output_tokens=8192)
+        state['llm']['max_output_tokens'] = 8192
+    elif state['llm']['model']=='gemini-2.5-flash-preview-04-17':
+        state['llm']['llm'] = ChatGoogleGenerativeAI(model="gemini-2.5-flash-preview-04-17",
+                                                     temperature=0.7)
+        state['llm']['max_output_tokens'] = 65536
+        
+    
+    # set the tokens usage
+    state['tokens'] = {}
+    state['tokens']['ti']  = 0
+    state['tokens']['to']  = 0
+    state['tokens']['i']   = 0
+    state['tokens']['o']   = 0
+    
     # set the names of standard files
     state['files'] = {**state['files'],
                       "Paper_v1":  "paper_v1.tex",
@@ -20,7 +51,8 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
                       "Paper_v4":  "paper_v4.tex",
                       "Error":     "Error.txt",
                       "LaTeX_log": "LaTeX_compilation.log",
-                      "Temp":      f"{state['files']['Folder']}/Temp"}
[…]

### 2025-04-29 src/tools.py

@@ -1,11 +1,55 @@
 import requests
 import sys,os,re,json
 from langchain_core.messages import HumanMessage
-from dotenv import load_dotenv
+from pathlib import Path
+#from dotenv import load_dotenv
 from src.prompts import fixer_prompt, LaTeX_prompt
 from src.parameters import GraphState
-from src.llm import llm
-from pathlib import Path
+
+
+def LLM_call(prompt, state):
+    """
+    This function calls the LLM and update tokens
+    """
+
+    message = state['llm']['llm'].invoke(prompt)
+    input_tokens  = message.usage_metadata['input_tokens']
+    output_tokens = message.usage_metadata['output_tokens']
+    if output_tokens>state['llm']['max_output_tokens']:
+        print('WARNING!! Max output tokens reach!')
+    state['tokens']['ti'] += input_tokens
+    state['tokens']['to'] += output_tokens
+    state['tokens']['i'] = input_tokens
+    state['tokens']['o'] = output_tokens
+    with open(state['files']['LLM_calls'], 'a') as f:
+        f.write(f"{state['tokens']['i']} {state['tokens']['o']} {state['tokens']['ti']} {state['tokens']['to']}\n")
+    
+    return state, message.content
+
+
+def temp_file(fin, action, text=None, json_file=False):
+    """
+    This function reads or writes the content of a temporary file
+    fin:  the name of the file
+    action: either 'read' of 'write'
+    text: when action is 'write', the text to write
+    json: whether the file is json or not
+    """
+
+    if action=='read':
+        with open(fin, 'r', encoding='utf-8') as f:
+            if json_file:
+                return json.load(f)
+            else:
+                return f.read()
+    elif action=='write':
+        with open(fin, 'w', encoding='utf-8') as f:
+            if json_file:
+                json.dump(text, f, indent=2)
+            else:
+                f.write(text)
+    else:
+        raise Exception("wrong action chosen!")
 
 
 def json_parser(text):
@@ -22,8 +66,8 @@ def json_parser(text):
         try:
             json_string = json_string.replace("'", "\"")
             parsed_json = json.loads(json_string)
-        except:
-            raise Exception('Failed to extract json from text')
+        except Exception as e:
+            raise ValueError(f"Failed to parse JSON: {e}")
     return parsed_json
 
 
[…]

### 2025-04-30 astropilot/astro_pilot.py
update to latest

@@ -98,14 +98,14 @@ class AstroPilot:
         self.research.methodology = methododology
 
         # Write idea to file
-        method_path = os.path.join(self.repo_dir, 'input_files', 'method.md')
+        method_path = os.path.join(self.repo_dir, 'input_files', 'methods.md')
         with open(method_path, 'w') as f:
             f.write(methododology)
         return None
     
     def set_method(self, method: str = None):
         # write method to method.md file
-        with open(os.path.join(self.repo_dir, 'input_files', 'method.md'), 'w') as f:
+        with open(os.path.join(self.repo_dir, 'input_files', 'methods.md'), 'w') as f:
             f.write(method)
         return None
     
@@ -124,7 +124,7 @@ class AstroPilot:
                 self.research.idea = f.read()
 
         if self.research.methodology == "":
-            with open(os.path.join(self.repo_dir, 'input_files', 'method.md'), 'r') as f:
+            with open(os.path.join(self.repo_dir, 'input_files', 'methods.md'), 'r') as f:
                 self.research.methodology = f.read()
 
 

### 2025-04-30 setup.py
projects and updates

@@ -1,25 +1,0 @@
-from setuptools import setup, find_packages
-
-setup(name='AstroPilot',
-      version='0.1.0',
-      packages=find_packages(),
-      install_requires=['langchain',
-                        'langchain-chroma',
-                        'langchain-community',
-                        'langchain-google-vertexai',
-                        'langchain-groq',
-                        'langchain-google-genai',
-                        'langchain-openai',
-                        'langchain-anthropic',
-                        'langgraph',
-                        'langgraph-checkpoint-sqlite',
-                        'pydantic',
-                        'dotenv',
-                        'requests',
-                        'typing-extensions',
-                        'pdflatex',
-                        'tqdm',
-                        'pymupdf',
-                        'pillow'],
-    include_package_data=True,
-    zip_safe=False)

### 2025-04-30 astropilot/paper.py
write paper

@@ -18,7 +18,7 @@ def write_paper(params, **kwargs):
     # run the graph
     result = asyncio.run(graph.ainvoke(
         {"files":{"Idea":       os.path.join(REPO_DIR,"input_files/idea.md"),
-                "Methods":      os.path.join(REPO_DIR,"input_files/method.md"),
+                "Methods":      os.path.join(REPO_DIR,"input_files/methods.md"),
                 "Results":      os.path.join(REPO_DIR,"input_files/results.md"),
                 "Plots":        os.path.join(REPO_DIR,"input_files/plots"),
                 "Paper_folder": os.path.join(REPO_DIR,"paper"),

### 2025-04-30 src/prompts.py
first attempt to fix latex problems

@@ -596,6 +596,30 @@ In <{section_name}> put the extracted text. In the extracted text, do not includ
 
 """)]
 
+def fix_latex_bug_prompt(state, text, error):
+
+    return [HumanMessage(content=fr"""The text below has a problem and LaTeX cannot compile it. Fix it. Do not modify the content, just fix the error and return the corrected version. Follow these guidelines
+
+- The text you are given is just a small part of a LaTeX paper. Thus, you dont need to add things like \\begin{{document}}.
+- If you see a LaTeX error, e.g. a missing $, a \\_ instead of _ fix it
+- Just reply with the corrected text, nothing else
+- Look at the error to fix the LaTeX mistake and only fix that. Do not close brackets if asked in the prompt
+
+Text:
+{text}
+
+Error:
+{error}    
+    
+Respond in this format:
+
+\begin{{Text}}
+<TEXT>
+\end{{Text}}
+
+In <TEXT>, put the fixed version of the line in LaTeX.
+    """)]
+
 
 def keyword_prompt(state):
 

### 2025-04-30 src/tools.py

@@ -21,8 +21,8 @@ def LLM_call(prompt, state):
     state['tokens']['to'] += output_tokens
     state['tokens']['i'] = input_tokens
     state['tokens']['o'] = output_tokens
-    with open(state['files']['LLM_calls'], 'a') as f:
-        f.write(f"{state['tokens']['i']} {state['tokens']['o']} {state['tokens']['ti']} {state['tokens']['to']}\n")
+    #with open(state['files']['LLM_calls'], 'a') as f:
+    #    f.write(f"{state['tokens']['i']} {state['tokens']['o']} {state['tokens']['ti']} {state['tokens']['to']}\n")
     
     return state, message.content
 

### 2025-04-30 src/latex.py
first attempt to fix latex problems

@@ -3,6 +3,8 @@ import sys,os,re
 from pathlib import Path
 
 from src.parameters import GraphState
+from src.prompts import *
+from src.tools import LLM_call, extract_latex_block
 
 
 # Characters that should be escaped in BibTeX (outside math mode)
@@ -60,8 +62,47 @@ def compile_latex(state: GraphState, paper_name: str):
             print(f"    LaTeX compilation failed: iteration {i+1}")
             with open(state['files']['LaTeX_log'], 'a') as f:
                 f.write(f"\n==== ERROR on Pass {i + 1} ====\n")
+                f.write("---- STDOUT ----\n")
                 f.write(e.stdout or "")
+                f.write("---- STDERR ----\n")
                 f.write(e.stderr or "")
+
+            # Filter actual errors from stdout/stderr
+            error_lines = []
+            lines = (e.stdout or "") .splitlines() + (e.stderr or "").splitlines()
+            show_context = 0
+            for line in lines:
+                if line.lstrip().startswith("!"):
+                    error_lines.append("\n" + line)
+                    show_context = 5  # show 3 lines after the error
+                elif show_context > 0:
+                    error_lines.append(line)
+                    show_context -= 1
+            error_msg = ' '.join(line.strip() for line in error_lines if line.strip())
+
+            print(error_lines)
+            latex_lines = []
+            for line in lines:
+                match = re.search(r'l\.(\d+)', line)
+                if match:
+                    latex_lines.append(match.group(1))
+                    print(f"Found line number: {match.group(1)}")
+            latex_lines = set(latex_lines)
+
+            # read the paper
+            with open(paper_name, 'r') as f:
+                lines = f.readlines()
+
+            for i in latex_lines:
+                print(lines[int(i)-2])
+                fixed_text = fix_latex_bug(state,lines[int(i)-2],error_msg)
+                #print(fixed_text)
+                lines[int(i)-2] = fixed_text
+
+            paper = ' '.join(line.strip() for line in lines if line.strip())
+            with open(paper_name, 'w') as f:
+                f.write(paper)
+                #sys.exit()
 
     # remove auxiliary files
     for fin in [f'{paper_stem}.aux', f'{paper_stem}.log', f'{paper_stem}.out',
@@ -180,3 +221,16 @@ def process_bib_file(input_file, output_file):
         fout.writelines(processed_lines)
 
     print(f"Sanitized BibTeX saved to: {output_file}")
[…]

### 2025-04-30 src/reader.py

@@ -82,6 +82,10 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
     for f_in in [state['files']['Error'], state['files']['LLM_calls']]:
         if os.path.exists(f_in):  os.remove(f"{f_in}")
 
+    # create empty file
+    #open(state['files']['LLM_calls'], 'w').close()
+        
+
     # remove LaTeX compilation log file
     f_in = f"{state['files']['Folder']}/{state['files']['LaTeX_log']}"
     if os.path.exists(f_in):  os.remove(f"{f_in}")

### 2025-04-30 astropilot/astro_pilot.py
all seems ok

@@ -1,17 +1,18 @@
 from .idea import Idea
 from .method import Method
 from .experiment import Experiment
-from .paper import write_paper
 from pydantic import BaseModel, Field
 from typing import List, Dict
 from IPython.display import display, Markdown
+from .graph import build_graph
+import asyncio
+import time
 import os
 os.environ["CMBAGENT_DEBUG"] = "false"
 os.environ["ASTROPILOT_DISABLE_DISPLAY"] = "true"
 
 from .config import REPO_DIR as repo_dir_default
-
-from cmbagent import CMBAgent
+import cmbagent
 import shutil
 
 
@@ -170,20 +171,8 @@ class AstroPilot:
         Returns:
             dict: Dictionary mapping AAS keywords to their URLs
         """
-        cmbagent = CMBAgent()
-        PROMPT = f"""
-        {input_text}
-        """
-        cmbagent.solve(task="Find the relevant AAS keywords",
-                max_rounds=50,
-                initial_agent='aas_keyword_finder',
-                mode = "one_shot",
-                shared_context={
-                'text_input_for_AAS_keyword_finder': PROMPT,
-                'N_AAS_keywords': n_keywords,
-                                }
-                )
-        aas_keywords = cmbagent.final_context['aas_keywords'] ## here you get the dict with urls
+        
+        aas_keywords = cmbagent.get_keywords(input_text, n_keywords = n_keywords)
         self.research.keywords = aas_keywords
         return None
     
@@ -195,8 +184,32 @@ class AstroPilot:
         return None
 
 
-    async def get_paper(self):
-        await write_paper(self.params)
+    def get_paper(self):
+        # Start timer
+        start_time = time.time()
+        config = {"configurable": {"thread_id": "1"}, "recursion_limit":100}
+
+
+        # build graph
+        graph = build_graph(mermaid_diagram=False)
+        path_to_input_files = os.path.join(self.repo_dir, "input_files")
+        
+        # run the graph
+        result = asyncio.run(graph.ainvoke(
+            {"files":{  "Folder":      path_to_input_files,   #name of folder containing input files
+                        "Idea":         "idea.md",    #name of file containing idea description
+                        "Methods":      "methods.md", #name of file with methods description
+                        "Results":      "results.md", #name of file with results description
+                        "Plots":        "plots"},     #name of folder containing plots
+            "llm": {"model": "gemini-2.0-flash"},  #name of the LLM model to use
+            }, config))
+
[…]

### 2025-04-30 astropilot/reader.py

@@ -8,6 +8,7 @@ from langchain_openai import ChatOpenAI
 from langchain_anthropic import ChatAnthropic
 from langchain_google_genai import ChatGoogleGenerativeAI
 from dotenv import load_dotenv
+from .config import LaTeX_DIR
 
 from .parameters import GraphState
 
@@ -90,7 +91,7 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
     for f in ['aasjournal.bst', 'aastex631.cls']:
         f_in = f"{state['files']['Folder']}/{f}"
         if not(os.path.exists(f_in)):
-            os.system(f"cp LaTeX/{f} {state['files']['Folder']}")
+            os.system(f"cp {LaTeX_DIR}/{f} {state['files']['Folder']}")
 
     # create a folder to save LaTeX progress
     os.makedirs(state['files']['Temp'], exist_ok=True)

### 2025-04-30 astropilot/config.py
all seems ok

@@ -5,5 +5,5 @@ from pathlib import Path
 BASE_DIR = Path(__file__).resolve().parent
 # REPO_DIR is defined as one directory above the package
 REPO_DIR = BASE_DIR.parent
-
+LaTeX_DIR = BASE_DIR / ".." / "LaTeX"
 ## in colab we need REPO_DIR = "/content/AstroPilot/"

### 2025-04-30 astropilot/paper.py

@@ -1,35 +1,0 @@
-from langgraph.graph import START, StateGraph, END
-from langgraph.checkpoint.memory import MemorySaver
-from langgraph.checkpoint.sqlite import SqliteSaver
-from .parameters import GraphState
-from .paper_node import *
-from .reader import *
-from .graph import build_graph
-
-from .config import REPO_DIR
-
-def write_paper(params, **kwargs):
-
-    config = {"configurable": {"thread_id": "1"}, "recursion_limit":100}
-
-    # build graph
-    graph = build_graph(mermaid_diagram=False)
-
-    # run the graph
-    result = asyncio.run(graph.ainvoke(
-        {"files":{"Idea":       os.path.join(REPO_DIR,"input_files/idea.md"),
-                "Methods":      os.path.join(REPO_DIR,"input_files/methods.md"),
-                "Results":      os.path.join(REPO_DIR,"input_files/results.md"),
-                "Plots":        os.path.join(REPO_DIR,"input_files/plots"),
-                "Paper_folder": os.path.join(REPO_DIR,"paper"),
-                "Paper_v1":     "paper_v1.tex",
-                "Paper_v2":     "paper_v2.tex",
-                "Paper_v3":     "paper_v3.tex",
-                "Error":        "Error.txt",
-                "LaTeX_log":    "LaTeX_compilation.log"},
-        "idea": {},
-        "paper":{"summary":""}},
-        config)
-    )
-    print("[astropilot.paper] Paper generation workflow complete.")
-

### 2025-04-30 astropilot/paper_node.py

@@ -13,7 +13,7 @@ from .tools import json_parser, fixer, LaTeX_checker, clean_section, extract_lat
 from .literature import process_tex_file_with_references
 from .latex import compile_latex, save_paper, save_bib, process_bib_file
 
-from cmbagent import CMBAgent
+import cmbagent
 
 
 
@@ -28,52 +28,50 @@ def keywords_node(state: GraphState, config: RunnableConfig):
     PROMPT = keyword_prompt(state)
 
     ### CMBAGENT template for keywords
-    #     cmbagent = CMBAgent()
-    #     PROMPT = f"""
-    # Idea:
-    # {state['idea']['Idea']}
+    PROMPT = f"""
+Idea:
+{state['idea']['Idea']}
 
-    # Methods:
-    # {state['idea']['Methods']}
-    # """
-    #     cmbagent.solve(task="Find the relevant AAS keywords",
-    #                max_rounds=50,
-    #                initial_agent='aas_keyword_finder',
-    #                mode = "one_shot",
-    #                shared_context={
-    #                'text_input_for_AAS_keyword_finder': PROMPT,
-    #                'N_AAS_keywords': 8,
-    #                               }
-    #               )
-    #     aas_keywords = cmbagent.final_context['aas_keywords'] ## here you get the dict with urls
-    #     # Extract keys and join them with a comma.
-    #     aas_keywords_str = ", ".join(aas_keywords.keys())
-    #     return {'paper': {**state['paper'], 'Keywords': aas_keywords_str}}
+Methods:
+{state['idea']['Methods']}
+    """
+
+    aas_keywords = cmbagent.get_keywords(PROMPT, n_keywords = 8)
+    # Extract keys and join them with a comma.
+    aas_keywords_str = ", ".join(aas_keywords.keys())
+    cmbagent_keywords_dict  = {'paper': {**state['paper'], 'Keywords': aas_keywords_str, 'tokens': {'i': 0, 'o': 0, 'ti': 0, 'to': 0}}}
+    # return 
     ### END CMBAGENT template for keywords
 
-    # temporary file with the selected keywords
-    f_temp = Path(f"{state['files']['Temp']}/Keywords.tex")
+    # # temporary file with the selected keywords
+    # f_temp = Path(f"{state['files']['Temp']}/Keywords.tex")
 
-    if f_temp.exists():
-        keywords = temp_file(f_temp, 'read')
+    # if f_temp.exists():
+    #     keywords = temp_file(f_temp, 'read')
 
-    else:
[…]

### 2025-04-30 tests/test_astropilot_write_paper.py

@@ -1,3 +1,6 @@
+import os
+os.environ["CMBAGENT_DEBUG"] = "false"
+os.environ["ASTROPILOT_DISABLE_DISPLAY"] = "false"
 from astropilot import AstroPilot
 
 params = {}

### 2025-04-30 astropilot/astro_pilot.py
update notebooks and idea

@@ -60,7 +60,8 @@ class AstroPilot:
         return None
 
     def show_data_description(self):
-        display(Markdown(self.research.data_description))
+        # display(Markdown(self.research.data_description))
+        print(self.research.data_description)
         return None
 
     def get_idea(self, **kwargs):
@@ -75,13 +76,26 @@ class AstroPilot:
         return None
     
     def set_idea(self, idea: str = None):
+        if idea is None:
+            with open(os.path.join(self.repo_dir, 'input_files', 'idea.md'), 'r') as f:
+                idea = f.read()
+        elif idea.endswith(".md"):
+            with open(idea, 'r') as f:
+                idea = f.read()
+        elif isinstance(idea, str):
+            pass
+        else:
+            raise ValueError("Idea must be a string, a path to a markdown file or None if you want to load idea from input_files/idea.md")
+        
+        self.research.idea = idea
         # write idea to idea.md file
         with open(os.path.join(self.repo_dir, 'input_files', 'idea.md'), 'w') as f:
             f.write(idea)
         return None
     
     def show_idea(self):
-        display(Markdown(self.research.idea))
+        # display(Markdown(self.research.idea))
+        print(self.research.idea)
         return None
     
     def get_method(self, **kwargs):

### 2025-05-01 src/latex.py
update

@@ -74,7 +74,7 @@ def compile_latex(state: GraphState, paper_name: str):
             for line in lines:
                 if line.lstrip().startswith("!"):
                     error_lines.append("\n" + line)
-                    show_context = 5  # show 3 lines after the error
+                    show_context = 3  # show 3 lines after the error
                 elif show_context > 0:
                     error_lines.append(line)
                     show_context -= 1
@@ -94,15 +94,16 @@ def compile_latex(state: GraphState, paper_name: str):
                 lines = f.readlines()
 
             for i in latex_lines:
-                print(lines[int(i)-2])
-                fixed_text = fix_latex_bug(state,lines[int(i)-2],error_msg)
-                #print(fixed_text)
-                lines[int(i)-2] = fixed_text
+                print('Hello!',i)
+                print(lines[int(i)-1])
+                fixed_text = fix_latex_bug(state,lines[int(i)-1],error_msg)
+                print(fixed_text)
+                lines[int(i)-1] = fixed_text
 
-            paper = ' '.join(line.strip() for line in lines if line.strip())
-            with open(paper_name, 'w') as f:
+            paper = '\n'.join(line.rstrip('\n') for line in lines)
+            with open("borrar.tex", 'w') as f:
                 f.write(paper)
-                #sys.exit()
+            sys.exit()
 
     # remove auxiliary files
     for fin in [f'{paper_stem}.aux', f'{paper_stem}.log', f'{paper_stem}.out',

### 2025-05-01 main.py
update

@@ -18,7 +18,8 @@ result = asyncio.run(graph.ainvoke(
               "Methods":      "methods.md", #name of file with methods description
               "Results":      "results.md", #name of file with results description
               "Plots":        "plots"},     #name of folder containing plots
-     "llm": {"model": "gemini-2.0-flash"},  #name of the LLM model to use
+     #"llm": {"model": "gemini-2.0-flash"},  #name of the LLM model to use
+     "llm": {"model": "gemini-2.5-flash-preview-04-17"},  #name of the LLM model to use
      }, config))
 
 # End timer and report duration in minutes and seconds

### 2025-05-01 src/prompts.py

@@ -598,18 +598,17 @@ In <{section_name}> put the extracted text. In the extracted text, do not includ
 
 def fix_latex_bug_prompt(state, text, error):
 
-    return [HumanMessage(content=fr"""The text below has a problem and LaTeX cannot compile it. Fix it. Do not modify the content, just fix the error and return the corrected version. Follow these guidelines
+    return [HumanMessage(content=fr"""The text below has a problem and LaTeX cannot compile it. Your task is to fix it following these instructions:
 
 - The text you are given is just a small part of a LaTeX paper. Thus, you dont need to add things like \\begin{{document}}.
-- If you see a LaTeX error, e.g. a missing $, a \\_ instead of _ fix it
-- Just reply with the corrected text, nothing else
+- If you see a LaTeX error, e.g. a missing $, a _ instead of \\_ fix it
+- Pay special attention to underscores. It is likely that an underscores _ may need to be \\_ to compile properly
+- Reply with the corrected text, nothing else
 - Look at the error to fix the LaTeX mistake and only fix that. Do not close brackets if asked in the prompt
+- Keep the text intact. Only fix the error without changing anything else
 
 Text:
 {text}
-
-Error:
-{error}    
     
 Respond in this format:
 

### 2025-05-01 src/latex.py
update

@@ -67,6 +67,7 @@ def compile_latex(state: GraphState, paper_name: str):
                 f.write("---- STDERR ----\n")
                 f.write(e.stderr or "")
 
+            """
             # Filter actual errors from stdout/stderr
             error_lines = []
             lines = (e.stdout or "") .splitlines() + (e.stderr or "").splitlines()
@@ -103,7 +104,8 @@ def compile_latex(state: GraphState, paper_name: str):
             paper = '\n'.join(line.rstrip('\n') for line in lines)
             with open("borrar.tex", 'w') as f:
                 f.write(paper)
-            sys.exit()
+            #sys.exit()
+            """
 
     # remove auxiliary files
     for fin in [f'{paper_stem}.aux', f'{paper_stem}.log', f'{paper_stem}.out',

### 2025-05-01 installer.sh
Update installer.sh

@@ -65,16 +65,16 @@ pip install -e .
 cd ..
 
 ### Clone and install ag2 ###
+
 AG2_REPO="https://github.com/CMBAgents/ag2.git"
 AG2_DIR="ag2"
+AG2_BRANCH="ag2_v0.8.4_upgrade_astrop"
 
-clone_repo "$AG2_REPO" "$AG2_DIR"
+# clone just that branch (no others; only last 1 commit’s history)
+git clone --branch "$AG2_BRANCH" --single-branch --depth 1 "$AG2_REPO" "$AG2_DIR"
 
-echo "Switching to branch 'ag2_v0.8.4_upgrade_astrop' and installing ag2..."
-cd "$AG2_DIR"
-git switch ag2_v0.8.4_upgrade_astrop
-pip install -e .
-cd ..
+echo "Installing ag2 from branch '$AG2_BRANCH'..."
+pip install -e "$AG2_DIR"
 
 ### Clone and install cmbagent ###
 CMBAGENT_REPO="https://github.com/CMBAgents/cmbagent.git"

### 2025-05-01 installer.sh
Update installer assuming that main repo is already cloned, use arbitrary python3 version and update gitignore with cloned repos -

@@ -7,7 +7,7 @@
 # If the first argument is "clean", remove everything and exit.
 if [ "$1" == "clean" ]; then
     echo "Cleaning up Python virtual environment and repositories..."
-    rm -rf astrop_env AstroPilot ag2 cmbagent
+    rm -rf astrop_env ag2 cmbagent
     echo "Clean operation completed."
     exit 0
 fi
@@ -27,9 +27,9 @@ clone_repo() {
   fi
 }
 
-# Create a Python 3.12 virtual environment named 'astrop_env'
+# Create a Python 3 virtual environment named 'astrop_env'
 echo "Creating Python virtual environment..."
-python3.12 -m venv astrop_env
+python3 -m venv astrop_env
 
 # Activate the virtual environment
 echo "Activating virtual environment..."
@@ -39,14 +39,9 @@ source astrop_env/bin/activate
 echo "Upgrading pip..."
 python -m pip install --upgrade pip
 
-### Clone and install AstroPilot ###
-ASTROPILOT_REPO="https://github.com/AstroPilot-AI/AstroPilot.git"
-ASTROPILOT_DIR="AstroPilot"
-
-clone_repo "$ASTROPILOT_REPO" "$ASTROPILOT_DIR"
+### Install AstroPilot ###
 
 echo "Switching to branch 'bbdev' and installing AstroPilot..."
-cd "$ASTROPILOT_DIR"
 git switch bbdev
 
 # Create the .env file from environment variables
@@ -62,7 +57,6 @@ EOF
 echo ".env file created."
 
 pip install -e .
-cd ..
 
 ### Clone and install ag2 ###
 AG2_REPO="https://github.com/CMBAgents/ag2.git"

### 2025-05-01 installer.sh
Temporary fix to avoid lfs problem when switch to ag2 branch

@@ -65,7 +65,7 @@ AG2_DIR="ag2"
 AG2_BRANCH="ag2_v0.8.4_upgrade_astrop"
 
 # clone just that branch (no others; only last 1 commit’s history)
-git clone --branch "$AG2_BRANCH" --single-branch --depth 1 "$AG2_REPO" "$AG2_DIR"
+GIT_LFS_SKIP_SMUDGE=1 git clone --branch "$AG2_BRANCH" --single-branch --depth 1 "$AG2_REPO" "$AG2_DIR"
 
 echo "Installing ag2 from branch '$AG2_BRANCH'..."
 pip install -e "$AG2_DIR"

### 2025-05-01 installer.sh
Install cmbagent via pip to avoid import path conflict, relax google-cloud-aiplatform to avoid dependency conflicts

@@ -72,15 +72,8 @@ pip install -e "$AG2_DIR"
 
 ### Clone and install cmbagent ###
 CMBAGENT_REPO="https://github.com/CMBAgents/cmbagent.git"
-CMBAGENT_DIR="cmbagent"
 
-clone_repo "$CMBAGENT_REPO" "$CMBAGENT_DIR"
-
-echo "Switching to branch 'astrop' and installing cmbagent..."
-cd "$CMBAGENT_DIR"
-git switch astrop
-pip install -e .
-cd ..
+pip install git+$CMBAGENT_REPO@astrop
 
 pip install pdflatex
 pip install pymupdf

### 2025-05-01 src/reader.py
fix error with credentials

@@ -15,9 +15,8 @@ from src.parameters import GraphState
 load_dotenv()
 GOOGLE_API_KEY     = os.getenv("GOOGLE_API_KEY")
 PERPLEXITY_API_KEY = os.getenv("PERPLEXITY_API_KEY")
-#OPENAI_API_KEY    = os.getenv("OPENAI_API_KEY")
-#ANTHROPIC_API_KEY = os.getenv("ANTHROPIC_API_KEY")
-#GROQ_API_KEY      = os.getenv("GROQ_API_KEY")
+OPENAI_API_KEY     = os.getenv("OPENAI_API_KEY")
+ANTHROPIC_API_KEY  = os.getenv("ANTHROPIC_API_KEY")
 
 
 def preprocess_node(state: GraphState, config: RunnableConfig):
@@ -28,11 +27,13 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
     # set the LLM
     if state['llm']['model']=='gemini-2.0-flash':
         state['llm']['llm'] = ChatGoogleGenerativeAI(model="gemini-2.0-flash", temperature=0.7,
-                                                     max_output_tokens=8192)
+                                                     max_output_tokens=8192,
+                                                     google_api_key=GOOGLE_API_KEY)
         state['llm']['max_output_tokens'] = 8192
     elif state['llm']['model']=='gemini-2.5-flash-preview-04-17':
         state['llm']['llm'] = ChatGoogleGenerativeAI(model="gemini-2.5-flash-preview-04-17",
-                                                     temperature=0.7)
+                                                     temperature=0.7,
+                                                     google_api_key=GOOGLE_API_KEY)
         state['llm']['max_output_tokens'] = 65536
         
     

### 2025-05-01 installer.sh
Move dependencies to pyproject.toml to better deal with version conflicts

@@ -41,8 +41,7 @@ python -m pip install --upgrade pip
 
 ### Install AstroPilot ###
 
-echo "Switching to branch 'bbdev' and installing AstroPilot..."
-git switch bbdev
+echo "Installing AstroPilot..."
 
 # Create the .env file from environment variables
 echo "Creating .env file in AstroPilot with API keys..."
@@ -64,20 +63,9 @@ AG2_REPO="https://github.com/CMBAgents/ag2.git"
 AG2_DIR="ag2"
 AG2_BRANCH="ag2_v0.8.4_upgrade_astrop"
 
-# clone just that branch (no others; only last 1 commit’s history)
-GIT_LFS_SKIP_SMUDGE=1 git clone --branch "$AG2_BRANCH" --single-branch --depth 1 "$AG2_REPO" "$AG2_DIR"
+echo "Cloning and installing ag2 from branch '$AG2_BRANCH'..."
 
-echo "Installing ag2 from branch '$AG2_BRANCH'..."
-pip install -e "$AG2_DIR"
-
-### Clone and install cmbagent ###
-CMBAGENT_REPO="https://github.com/CMBAgents/cmbagent.git"
-
-pip install git+$CMBAGENT_REPO@astrop
-
-pip install pdflatex
-pip install pymupdf
-pip install jsonschema==4.23.0
+GIT_LFS_SKIP_SMUDGE=1 pip install git+$AG2_REPO@$AG2_BRANCH
 
 # Install an IPython kernel for the virtual environment
 echo "Installing IPython kernel for the virtual environment..."

### 2025-05-01 src/latex.py
update

@@ -20,7 +20,6 @@ special_chars = {
     "^": r"\^{}",
 }
 
-
 def compile_latex(state: GraphState, paper_name: str):
     """
     Function used to compile the paper
@@ -39,7 +38,14 @@ def compile_latex(state: GraphState, paper_name: str):
     paper_stem = Path(paper_name).stem
     
     # try to compile twice for citations and links
-    for i in range(3):  #compile three times to add citations
+    for i in range(4):  #compile three times to add citations
+        if i==1:
+            if os.path.exists('bibliography.bib'):
+                result = subprocess.run(["bibtex", paper_stem],
+                                        capture_output=True,
+                                        text=True, check=True)
+            continue
+            
         try:
             result = subprocess.run(["xelatex", paper_name],
                                     input="\n",
@@ -51,12 +57,6 @@ def compile_latex(state: GraphState, paper_name: str):
             with open(state['files']['LaTeX_log'], 'a') as f:
                 f.write(f"\n==== LaTeX Compilation Pass {i + 1} ====\n")
                 f.write(result.stdout)
-
-            if i==0:
-                result = subprocess.run(["bibtex", paper_stem],
-                                        capture_output=True,
-                                        text=True, check=True)
-
             
         except subprocess.CalledProcessError as e:
             print(f"    LaTeX compilation failed: iteration {i+1}")

### 2025-05-01 src/tools.py

@@ -41,13 +41,34 @@ def temp_file(fin, action, text=None, json_file=False):
             if json_file:
                 return json.load(f)
             else:
-                return f.read()
+                latex_text = f.read()
+                
+                # Extract content between \begin{document} and \end{document}
+                match = re.search(r'\\begin{document}(.*?)\\end{document}',
+                                  latex_text, re.DOTALL)
+
+                if match:
+                    extracted_text = match.group(1).strip()
+                    return extracted_text
+                else:
+                    raise Exception("Text not found on file!")
+
     elif action=='write':
         with open(fin, 'w', encoding='utf-8') as f:
             if json_file:
                 json.dump(text, f, indent=2)
             else:
-                f.write(text)
+                latex_text = rf"""\documentclass[twocolumn]{{aastex631}}
+
+\usepackage{{amsmath}}
+\usepackage{{multirow}}
+\begin{{document}}
+
+{text}
+
+\end{{document}}
+                """
+                f.write(latex_text)
     else:
         raise Exception("wrong action chosen!")
 

### 2025-05-01 src/paper_node.py
update

@@ -96,6 +96,7 @@ def abstract_node(state: GraphState, config: RunnableConfig):
     # Save paper and temporary file
     state['paper']['Abstract'] = abstract
     save_paper(state, state['files']['Paper_v1'])
+    compile_latex(state, state['files']['Paper_v1'])
     print(f"done {state['tokens']['ti']} {state['tokens']['to']}")
 
     return {'paper':{**state['paper'],
@@ -157,6 +158,7 @@ def section_node(state: GraphState, config: RunnableConfig, section_name: str,
     # --- Step 5: Save paper ---
     state['paper'][section_name] = section_text
     save_paper(state, state['files']['Paper_v1'])
+    compile_latex(state, state['files']['Paper_v1'])
     print(f"done {state['tokens']['ti']} {state['tokens']['to']}")
 
     # --- Step 7: Update state ---
@@ -270,6 +272,7 @@ def plots_node(state: GraphState, config: RunnableConfig):
 
         # save paper
         save_paper(state, state['files']['Paper_v1'])
+        compile_latex(state, state['files']['Paper_v1'])
 
     # compile paper
     compile_latex(state, state['files']['Paper_v1'])

### 2025-05-01 installer.sh
adding installer

@@ -1,0 +1,85 @@
+#!/bin/bash
+# installer.sh
+# This script sets up a Python virtual environment, upgrades pip,
+# and clones & installs three Git repositories using specific branches.
+# It also supports a "clean" option to remove the environment and clones.
+
+# If the first argument is "clean", remove everything and exit.
+if [ "$1" == "clean" ]; then
+    echo "Cleaning up Python virtual environment and repositories..."
+    rm -rf astrop_env ag2 cmbagent
+    echo "Clean operation completed."
+    exit 0
+fi
+
+# Exit immediately if a command exits with a non-zero status.
+set -e
+
+TARGET_BRANCH="bbdev"
+
+# Switch this repo to the desired branch if needed
+current_branch=$(git rev-parse --abbrev-ref HEAD)
+if [ "$current_branch" != "$TARGET_BRANCH" ]; then
+    echo "Checking out $TARGET_BRANCH branch ..."
+    git fetch origin "$TARGET_BRANCH"
+    git checkout "$TARGET_BRANCH"
+fi
+
+# Function to clone a repo if it doesn't exist
+clone_repo() {
+  local repo_url=$1
+  local repo_dir=$2
+  if [ ! -d "$repo_dir" ]; then
+    echo "Cloning $repo_url into $repo_dir ..."
+    git clone "$repo_url"
+  else
+    echo "Directory $repo_dir already exists. Skipping clone."
+  fi
+}
+
+# Create a Python 3 virtual environment named 'astrop_env'
+echo "Creating Python virtual environment..."
+python3.12 -m venv astrop_env
+
+# Activate the virtual environment
+echo "Activating virtual environment..."
+source astrop_env/bin/activate
+
+# Upgrade pip
+echo "Upgrading pip..."
+python -m pip install --upgrade pip
+
+### Install AstroPilot ###
+
+echo "Installing AstroPilot..."
+
+# Create the .env file from environment variables
+echo "Creating .env file in AstroPilot with API keys..."
+cat <<EOF > .env
+OPENAI_API_KEY="${OPENAI_API_KEY}"
+ANTHROPIC_API_KEY="${ANTHROPIC_API_KEY}"
+GEMINI_API_KEY="${GEMINI_API_KEY}"
+GOOGLE_API_KEY="${GOOGLE_API_KEY}"
+LANGCHAIN_API_KEY="${LANGCHAIN_API_KEY}"
[…]

### 2025-05-02 src/latex.py
some latex compilation changes

@@ -20,100 +20,186 @@ special_chars = {
     "^": r"\^{}",
 }
 
-def compile_latex(state: GraphState, paper_name: str):
-    """
-    Function used to compile the paper
-    Args:
-       state: the state of the graph
-       paper: the name of file to compile
-    """
-    
+
+def compile_latex(state: GraphState, paper_name: str, verbose=True):
+
     # get the current directory
     original_dir = os.getcwd()
 
     # go to the folder containing the paper
     os.chdir(state['files']['Folder'])
 
-    # get the stem of the paper paper name
+    # get the paper stem
     paper_stem = Path(paper_name).stem
-    
-    # try to compile twice for citations and links
-    for i in range(4):  #compile three times to add citations
-        if i==1:
-            if os.path.exists('bibliography.bib'):
-                result = subprocess.run(["bibtex", paper_stem],
-                                        capture_output=True,
-                                        text=True, check=True)
-            continue
-            
+
+    def run_xelatex():
+        return subprocess.run(["xelatex", paper_name],
+                              input="\n", capture_output=True,
+                              text=True, check=True)
+
+    def run_bibtex():
+        subprocess.run(["bibtex", paper_stem],
+                       capture_output=True, text=True, check=True)
+
+    def log_output(i, result_or_error, is_error=False):
+        with open(state['files']['LaTeX_log'], 'a') as f:
+            f.write(f"\n==== {'ERROR' if is_error else 'PASS'} on iteration {i} ====\n")
+            f.write("---- STDOUT ----\n")
+            f.write(result_or_error.stdout or "")
+            f.write("---- STDERR ----\n")
+            f.write(result_or_error.stderr or "")
+
+    def fix_error(e):
+        lines = (e.stdout or "").splitlines() + (e.stderr or "").splitlines()
+        error_lines = []
+        show_context = 0
+        for line in lines:
+            if line.lstrip().startswith("!"):
+                error_lines.append("\n" + line)
+                show_context = 3
+            elif show_context > 0:
+                error_lines.append(line)
+                show_context -= 1
+        error_msg = ' '.join(line.strip() for line in error_lines if line.strip())
+        section = state['latex']['section']
+        fixed_text = fix_latex_bug(state, state['paper'][section], error_msg)
+        state['paper'][section] = fixed_text
+        os.chdir(original_dir)
+        save_paper(state, paper_name)
+        os.chdir(state['files']['Folder'])
+
[…]

### 2025-05-02 src/paper_node.py

@@ -95,8 +95,9 @@ def abstract_node(state: GraphState, config: RunnableConfig):
 
     # Save paper and temporary file
     state['paper']['Abstract'] = abstract
+    state['latex']['section'] = 'Abstract'
     save_paper(state, state['files']['Paper_v1'])
-    compile_latex(state, state['files']['Paper_v1'])
+    #compile_latex(state, state['files']['Paper_v1'], verbose=False)
     print(f"done {state['tokens']['ti']} {state['tokens']['to']}")
 
     return {'paper':{**state['paper'],
@@ -158,7 +159,7 @@ def section_node(state: GraphState, config: RunnableConfig, section_name: str,
     # --- Step 5: Save paper ---
     state['paper'][section_name] = section_text
     save_paper(state, state['files']['Paper_v1'])
-    compile_latex(state, state['files']['Paper_v1'])
+    #compile_latex(state, state['files']['Paper_v1'], verbose=False)
     print(f"done {state['tokens']['ti']} {state['tokens']['to']}")
 
     # --- Step 7: Update state ---
@@ -272,7 +273,7 @@ def plots_node(state: GraphState, config: RunnableConfig):
 
         # save paper
         save_paper(state, state['files']['Paper_v1'])
-        compile_latex(state, state['files']['Paper_v1'])
+        #compile_latex(state, state['files']['Paper_v1'], verbose=False)
 
     # compile paper
     compile_latex(state, state['files']['Paper_v1'])

### 2025-05-02 src/parameters.py

@@ -44,6 +44,10 @@ class TOKENS(TypedDict):
     i:  int #input tokens (just for individual calls or functions)
     o:  int #output tokens (just for individual calls or functions)
 
+# LaTeX class
+class LATEX(TypedDict):
+    section: str
+    
 # LLM class
 class LLM(TypedDict):
     model: str
@@ -58,3 +62,4 @@ class GraphState(TypedDict):
     paper: PAPER
     tokens: TOKENS
     llm: LLM
+    latex: LATEX

### 2025-05-02 src/prompts.py

@@ -206,6 +206,7 @@ In <INTRODUCTION>, place the introduction of the paper. Please, follow these gui
 - Describe how we verify that we have solved the problem
 - Do not create subsections
 - Do not add citations 
+- Do not create commands, e.g. \MBH
 
 Please make sure the introduction reads smoothly and is well-motivated. If you use equations, please write them in LaTeX.
 """)]
@@ -246,6 +247,7 @@ In <INTRODUCTION>, place the new Introduction of the paper. Follow these guideli
 - Describe how we verify that we have solved the problem
 - Do not create subsections
 - Do not add citations 
+- Do not create commands, e.g. \MBH
 
 Please make sure the introduction reads smoothly and is well-motivated. If you use equations, please write them in LaTex.
 """)]
@@ -280,6 +282,7 @@ Follow these guidelines:
 - Write in LaTex
 - Describe in detail the different methods used, the dataset, evaluation metrics, and any other element relevant
 - Do not write citations. References will be added later on
+- Do not create command, e.g. \MBH
 - Try to connect the text in this section with the one in the introduction
 - Do not write subsections titles in capital letters
 - The first letter of subsection titles should be in capital
@@ -321,6 +324,7 @@ Follow these guidelines:
 - Do not add plots or placeholders for plots. Plots will be added later on
 - Describe what we have learned from the results
 - Do not write the bibliography
+- Do not create command, e.g. \MBH
 - Do not write subsections titles in capital letters
 - The first letter of subsection titles should be in capital
 - You can create subsections and subsubsections, but **you cannot create sections**
@@ -386,6 +390,7 @@ Follow these guidelines:
 - Describe the results obtained
 - Describe what we have learned from the results and this paper
 - Do not add citations. Citations will be added later on
+- Do not create command, e.g. \MBH
 - Do not write subsections titles in capital letters
 - The first letter of subsection titles should be in capital
 - Do not write words or sentences between *. 
@@ -609,6 +614,9 @@ def fix_latex_bug_prompt(state, text, error):
 
 Text:
 {text}
+
+Error:
+{error}
     
 Respond in this format:
 

### 2025-05-02 src/reader.py
some latex compilation changes

@@ -54,6 +54,11 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
                       "LaTeX_log": "LaTeX_compilation.log",
                       "Temp":      f"{state['files']['Folder']}/Temp",
                       "LLM_calls": f"{state['files']['Folder']}/LLM_calls.txt"}
+
+    # set the Latex class
+    state['latex'] = {}
+    state['latex']['section'] = ""
+    
     idea = {}
     
     # read input files
@@ -125,5 +130,5 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
 
 
     return {"idea": idea,  "files": state['files'],  "paper": {"summary": ""},
-            "tokens": state['tokens']}
+            "tokens": state['tokens'], "latex": state['latex']}
 

### 2025-05-02 Project4/paper_v2.tex
fix: Fix LaTeX compilation errors in paper_v2.tex

\documentclass[twocolumn]{aastex631}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\usepackage{amsmath}
\usepackage{multirow}

\begin{document}

\title{Regime-Specific Performance of 1D CNN and FCNN Architectures for Non-linear Matter Power Spectrum Emulation in LCDM Cosmology}

\author{AstroPilot}
\affiliation{Anthropic, Gemini \& OpenAI servers. Planet Earth.}

\begin{abstract}
Accurate and efficient emulation of the non-linear matter power spectrum is essential for extracting cosmological information from large-scale structure surveys. However, the power spectrum's complex, scale-dependent behavior, particularly in the quasi-linear and non-linear regimes, makes accurate emulation challenging. To address this, we present a comprehensive benchmarking study comparing 1D Convolutional Neural Networks (CNNs) and Fully Connected Neural Networks (FCNNs) as emulators for the non-linear matter power spectrum within the standard \(\Lambda\)CDM model. Our key contribution is a detailed analysis of each architecture's performance across physically motivated regimes in wavenumber, redshift, and cosmological parameter space, providing actionable guidance for efficient emulator design. We trained and tested both architectures on a large dataset of 500,000 power spectra generated using the `classy_sz` Boltzmann solver. Our results demonstrate that 1D CNNs generally outperform FCNNs, especially in the quasi-linear and non-linear regimes, achieving median relative errors below 1% while maintaining comparable inference speeds, highlighting the 1D CNN's ability to better capture the complex features of the power spectrum at smaller scales.
\end{abstract}

\keywords{Cosmology, Cosmological parameters}

\section{Introduction}
\label{sec:intro}

\noindent The relentless pursuit of understanding the universe's composition, evolution, and fundamental laws drives modern cosmology. Large-scale structure surveys, such as the Dark Energy Spectroscopic Instrument (DESI) and the Nancy Grace Roman Space Telescope, are at the forefront of this endeavor. These ambitious projects meticulously map the distribution of galaxies and other cosmic tracers across vast cosmic volumes. By precisely measuring these distributions, scientists aim to constrain cosmological parameters with unprecedented accuracy and probe the enigmatic nature of dark energy and dark matter. The full potential of these surveys hinges on our ability to accurately and efficiently connect theoretical predictions with observational data.

\noindent A critical component in this connection is the matter power spectrum, \(P(k, z)\), which encapsulates the statistical distribution of matter fluctuations in the universe as a function of scale (\(k\)) and redshift (\(z\)). Extracting meaningful cosmological information from these surveys requires repeatedly comparing theoretical predictions of \(P(k, z)\) with observational data. This comparison is a computationally intensive process, often involving exploring a vast parameter space of cosmological models. Direct evaluation of Boltzmann solvers like CLASS or CAMB at each point in the cosmological parameter space during the likelihood analysis is computationally prohibitive. Therefore, accelerating the process of obtaining theoretical predictions of the matter power spectrum is of paramount importance.

\noindent Traditional methods for calculating the matter power spectrum rely on solving the Boltzmann equations, a computationally demanding task, especially in the non-linear regime. In this regime, perturbative approaches break down, necessitating more sophisticated and computationally expensive techniques. N-body simulations offer a more accurate approach to modeling non-linear structure formation. However, they also require significant computational resources and time, further exacerbating the computational bottleneck. The computational cost associated with these methods motivates the development of accurate and efficient emulators.

\noindent Emulators are surrogate models trained on a limited set of power spectra generated from simulations or Boltzmann solvers. These emulators can then rapidly predict \(P(k, z)\) for any given set of cosmological parameters. This capability enables efficient exploration of the parameter space during cosmological inference. The development of accurate and efficient emulators is crucial for maximizing the scientific return from current and future large-scale structure surveys. These emulators act as fast and accurate proxies for computationally expensive simulations, enabling cosmologists to efficiently explore the vast parameter space of cosmological models.

\noindent However, accurately emulating the non-linear matter power spectrum presents several significant challenges. The power spectrum exhibits complex, scale-dependent behavior, with different physical processes dominating in different regimes. In the linear regime (small \(k\)), gravity dominates, and the power spectrum can be accurately predicted using linear perturbation theory. In the quasi-linear and non-linear regimes (large \(k\)), non-linear gravitational effects become increasingly important, leading to mode coupling and the formation of complex structures. Therefore, accurately capturing this complex behavior requires emulators that can accurately model the non-linear mapping between cosmological parameters and the power spectrum across a wide range of scales and redshifts.

\noindent Furthermore, the high dimensionality of the input space poses a significant challenge for emulator training. The input space includes cosmological parameters such as the baryon density (\(\Omega_b\)), cold dark matter density (\(\Omega_{cdm}\)), Hubble constant (\(H_0\)), primordial amplitude (\(A_s\)), spectral index (\(n_s\)), and redshift (\(z\)). This high dimensionality leads to the "curse of dimensionality," where the number of training samples required to achieve a given level of accuracy increases exponentially with the number of input parameters. Therefore, the development of emulators requires efficient machine learning techniques that can effectively learn the complex relationships between the input parameters and the output power spectrum from a limited number of training samples.

\noindent To address these challenges, we present a comprehensive benchmarking study comparing two popular neural network architectures: 1D Convolutional Neural Networks (CNNs) and Fully Connected Neural Networks (FCNNs). We evaluate their performance as emulators for the non-linear matter power spectrum within the standard \(\Lambda\)CDM model. Our key contribution is a detailed analysis of each architecture's performance across physically motivated regimes in wavenumber (\(k\)), redshift (\(z\)), and cosmological parameter space. This analysis provides actionable guidance for efficient emulator design. Our goal is to identify the strengths and weaknesses of each architecture in different regions of the parameter space, allowing researchers to choose the most appropriate emulator for their specific cosmological application.

\noindent We generate a large dataset of 500,000 power spectra using the `classy\ensuremath{\_}sz` Boltzmann solver, spanning a wide range of cosmological parameters and redshifts. This dataset serves as the training and testing ground for our neural network emulators. We carefully preprocess the data, including normalization and logarithmic transformation, to improve the training process and enhance the accuracy of the emulators. Both 1D CNN and FCNN architectures are then trained on the training dataset, optimizing their hyperparameters using a validation set. This rigorous training and validation process ensures that our emulators are robust and accurate.

\noindent Our results demonstrate that 1D CNNs generally outperform FCNNs, especially in the quasi-linear and non-linear regimes. This suggests that the convolutional layers in the 1D CNNs are better able to capture the local correlations and scale-dependent features of the power spectrum at smaller scales. We find that the 1D CNNs achieve median relative errors below 1% in these regimes, while maintaining comparable inference speeds to FCNNs. These findings highlight the potential of 1D CNNs as efficient and accurate emulators for the non-linear matter power spectrum.

\noindent Furthermore, we conduct a thorough error analysis, stratifying the results by \(k\)-range and redshift bins to identify regime-specific performance characteristics. This allows us to pinpoint the regions where each architecture excels and where further improvements are needed. We also compare the inference speeds of the two architectures, measuring the wall-clock time required to predict the power spectrum for a single input. This is crucial for assessing the computational efficiency of the emulators and their suitability for large-scale cosmological analyses. By carefully analyzing the performance of each architecture across different regimes, we provide valuable insights for emulator design.

\noindent Moving forward, we plan to explore several potential avenues for future work. This includes investigating more sophisticated neural network architectures, such as transformers or graph neural networks, which may be even better suited for capturing the complex dependencies in the matter power spectrum. We also plan to explore the use of transfer learning techniques, where a pre-trained emulator is fine-tuned on a smaller dataset of higher-resolution simulations, to further improve the accuracy of the emulator in the non-linear regime. These advanced techniques hold the promise of further enhancing the accuracy and efficiency of matter power spectrum emulators.

\noindent Finally, we aim to extend our benchmarking study to include other cosmological models beyond \(\Lambda\)CDM, such as models with modified gravity or non-standard dark matter. By expanding our analysis to these alternative cosmological models, we can assess the robustness of our emulators and their ability to handle a wider range of theoretical predictions. In conclusion, this work provides a comprehensive comparison of 1D CNN and FCNN architectures for non-linear matter power spectrum emulation. Our results offer valuable insights into the strengths and weaknesses of each architecture and provide actionable guidance for efficient emulator design. By identifying the most accurate and efficient emulation techniques, we can accelerate cosmological inference and unlock the full potential of current and future large-scale structure surveys.

\section{Methods}
\label{sec:methods}
\subsection{Data Generation}

\subsubsection{Cosmological Parameter and Redshift Sampling}

We generated a training and testing dataset of non-linear matter power spectra using the \texttt{classy\_sz} Boltzmann solver. To efficiently explore the cosmological parameter space, we employed Latin Hypercube Sampling (LHS) to create 500,000 unique samples. Each sample represents a point in the 6-dimensional parameter space defined by the following cosmological parameters and redshift: baryon density ($\omega_b$), cold dark matter density ($\omega_{cdm}$), Hubble constant ($H_0$), the amplitude of the primordial power spectrum ($\log A$), spectral index ($n_s$), and redshift ($z$). The sampling ranges for each parameter were: $\omega_b \in [0.01933, 0.02533]$, $\omega_{cdm} \in [0.08, 0.20]$, $H_0 \in [40, 100]$ km/s/Mpc, $\log A \in [2.5, 3.5]$, $n_s \in [0.8, 1.2]$, and $z \in [0, 1]$. The LHS technique ensures a quasi-random distribution of samples that efficiently covers the entire parameter space, minimizing clustering and maximizing coverage. Each sample is represented as a vector $(\omega_b, \omega_{cdm}, H_0, \log A, n_s, z)$.

\subsubsection{Power Spectrum Computation}

For each of the 500,000 parameter sets generated via LHS, we used the \texttt{classy\_sz} code to calculate the non-linear matter power spectrum, $P(k, z)$. \texttt{classy\_sz} was configured to output the power spectrum over a pre-defined $k$-grid, spanning the range $k \in [10^{-4}, 10]$ $h$/Mpc. This range encompasses the linear, quasi-linear, and non-linear regimes of structure formation. The $k$-grid was held constant across all simulations to ensure consistency and facilitate direct comparison of the resulting power spectra. The specific $k$ values were determined by the default configuration of \texttt{classy\_sz}. The output of \texttt{classy\_sz} for each parameter set is a one-dimensional array of $P(k, z)$ values corresponding to the fixed $k$-grid.

\subsubsection{Dataset Structuring and Splitting}

The generated data was structured into a dataset suitable for training and testing neural network emulators. Each data point consisted of a 6-dimensional input vector (the cosmological parameters and redshift: $\omega_b, \omega_{cdm}, H_0, \log A, n_s, z$) and a corresponding one-dimensional output array representing the non-linear matter power spectrum $P(k, z)$ at the pre-defined $k$ values. The complete dataset was then randomly split into training and testing sets, with 80\% of the data allocated to the training set (400,000 samples) and 20\% allocated to the testing set (100,000 samples). This split was performed using a stratified random sampling approach to ensure that the distribution of cosmological parameters and redshifts in the training and testing sets was representative of the overall distribution. This helps to avoid biases in the emulator's performance evaluation.

\subsection{Data Preprocessing}

\subsubsection{Input Normalization}

Prior to training, the input cosmological parameters and redshift were normalized to improve the training stability and convergence of the neural networks. We applied min-max normalization to each input parameter, scaling its values to the range $[0, 1]$. The normalization was performed according to the following formula:

$$x_{norm} = \frac{x - x_{min}}{x_{max} - x_{min}}$$

where $x$ is the original parameter value, $x_{min}$ is the minimum value of that parameter in the sampling range, $x_{max}$ is the maximum value, and $x_{norm}$ is the normalized value. The minimum and maximum values for each parameter were stored for use in inverse transformation during inference, allowing the normalized inputs to be converted back to their original scales.

\subsubsection{Output Transformation and Normalization}

The output power spectra, $P(k, z)$, were transformed to logarithmic space to reduce the dynamic range of the data and improve the emulator's ability to model the power spectrum across a wide range of scales. We took the base-10 logarithm of both the wavenumber $k$ and the power spectrum $P(k, z)$:

$$\log_{10} k \rightarrow k$$
$$\log_{10} P(k, z) \rightarrow P(k, z)$$

The neural networks were trained to predict $\log_{10} P(k, z)$ as a function of the input parameters. Furthermore, the output was standardized by subtracting the mean and dividing by the standard deviation for each $k$ value across the training set. This standardization was performed to center the data around zero and scale it to unit variance, further improving training stability. The mean and standard deviation for each $k$ value were calculated based on the training set and stored for inverse transformation during evaluation. The inverse transformation involves first rescaling by the standard deviation and then adding the mean, before exponentiating to obtain the power spectrum.

\subsubsection{Data Storage}

The preprocessed training and testing datasets, including the normalized input parameters and the transformed and standardized power spectra, were stored in HDF5 files. HDF5 is an efficient binary data format that allows for fast loading and storage of large numerical datasets. Separate HDF5 files were created for the training and testing sets, and each file included metadata containing the normalization parameters (min, max, mean, and standard deviation) used for the input and output data. This organization ensures easy access to the data and the necessary information for data preprocessing and inverse transformation.

\subsection{Neural Network Training}

\subsubsection{1D CNN Architecture}

We implemented a 1D Convolutional Neural Network (CNN) architecture for emulating the non-linear matter power spectrum. The architecture consists of the following layers:

\begin{enumerate}
    \item \textbf{Input Layer:} Accepts a 6-dimensional input vector representing the cosmological parameters and redshift.
    \item \textbf{Dense Layer:} A fully connected layer with an output dimension equal to the number of $k$-points in the power spectrum, followed by a ReLU activation function. This layer maps the input parameters to a space with the same dimensionality as the output power spectrum.
    \item \textbf{Reshape Layer:} Reshapes the output of the dense layer into a 3D tensor with dimensions (number of $k$-points, 1), preparing the data for the convolutional layers.
    \item \textbf{Conv1D Layers:} Two 1D convolutional layers, each with 64 filters, a kernel size of 3, ReLU activation, and "same" padding. The "same" padding ensures that the output of the convolutional layers has the same spatial dimensions as the input.
    \item \textbf{Flatten Layer:} Flattens the output of the convolutional layers into a 1D vector.
    \item \textbf{Dense Layer:} A fully connected layer with 256 units and ReLU activation.
    \item \textbf{Output Layer:} A fully connected layer with an output dimension equal to the number of $k$-points. This layer predicts the log-transformed power spectrum values. No activation function is applied to the output layer.
\end{enumerate}

\subsubsection{FCNN Architecture}

We also implemented a Fully Connected Neural Network (FCNN) architecture for comparison. The architecture consists of the following layers:

\begin{enumerate}
    \item \textbf{Input Layer:} Accepts a 6-dimensional input vector representing the cosmological parameters and redshift.
    \item \textbf{Hidden Layers:} Four fully connected hidden layers, each with 512 nodes and a Swish activation function. The Swish activation function is defined as $f(x) = x \cdot \sigma(x)$, where $\sigma(x)$ is the sigmoid function.
    \item \textbf{Output Layer:} A fully connected layer with an output dimension equal to the number of $k$-points. This layer predicts the log-transformed power spectrum values. No activation function is applied to the output layer.
\end{enumerate}

\subsubsection{Training Procedure}

Both the 1D CNN and FCNN architectures were trained using the same training and validation splits of the dataset to ensure a fair comparison. The training procedure involved the following steps:

\begin{enumerate}
    \item \textbf{Optimization:} The Adam optimizer was used to minimize the Mean Squared Error (MSE) loss function between the predicted and true log-transformed power spectra. The Adam optimizer is an adaptive learning rate optimization algorithm that adjusts the learning rate for each parameter based on its historical gradient.
    \item \textbf{Hyperparameter Tuning:} The batch size was set to 128. The initial learning rate was set to $10^{-3}$.
    \item \textbf{Early Stopping:} Early stopping was implemented to prevent overfitting. The validation loss was monitored during training, and the training process was stopped if the validation loss did not improve for 20 epochs.
    \item \textbf{Maximum Epochs:} The maximum number of training epochs was set to 500.
    \item \textbf{Model Saving:} The model with the lowest validation loss was saved during training.
    \item \textbf{Regularization:} Dropout layers with a dropout rate of 0.1 were optionally added after the dense layers in both architectures to further prevent overfitting.
\end{enumerate}

The training curves, including the training and validation loss as a function of epoch, were logged for later analysis.

\subsection{Performance Evaluation}

\subsubsection{Accuracy Metrics}

The performance of the trained 1D CNN and FCNN emulators was evaluated on the test dataset using the following accuracy metrics:

\begin{enumerate}
    \item \textbf{Mean Squared Error (MSE):} The MSE was calculated between the true and predicted log-transformed power spectra across all $k$ values and all test samples. The MSE provides a measure of the overall accuracy of the emulator.
    \item \textbf{Relative Error:} The relative error, $\Delta P / P$, was calculated as a function of $k$ and $z$, averaged over the test set. The relative error provides a more detailed assessment of the emulator's performance across different scales and redshifts.
\end{enumerate}

The error analysis was stratified by $k$-range (e.g., linear regime, quasi-linear, non-linear) and by redshift bins to identify regime-specific performance.

\subsubsection{Inference Speed}

The inference speed of each architecture was measured by calculating the wall-clock time required to predict the full $P(k)$ array for a single input (cosmological parameters + $z$). The measurements were performed on a standardized computational environment (a single CPU core). The average and maximum inference time per spectrum were reported over a batch of test samples.

\subsubsection{Diagnostic and Comparison Plots}

Diagnostic plots were generated to visually assess the performance of the emulators. These plots included:

\begin{enumerate}
    \item \textbf{True vs. Emulated P(k):} Plots of the true power spectrum versus the emulated power spectrum (in log-log scale) for representative test cases at various redshifts and cosmologies.
    \item \textbf{Error as a Function of k and z:} Plots of the relative error as a function of $k$ and $z$ for both architectures.
\end{enumerate}

These plots provide a visual comparison of the accuracy of the two architectures across different scales and redshifts.

\subsubsection{Reporting}

The results of the performance evaluation were summarized in tables and figures, comparing the accuracy and speed of the 1D CNN and FCNN architectures across different regimes. The report included a comprehensive comparison of the two architectures in terms of overall and regime-specific accuracy, inference speed, and diagnostic plots illustrating strengths and weaknesses in different physical regimes.

\section{Results}
\label{sec:results}
\subsection{Results}

This section presents a detailed analysis of the performance of 1D CNN and FCNN architectures for emulating the non-linear matter power spectrum, $P(k, z)$, within the $\Lambda$CDM cosmological framework. The emulators were trained and tested on a dataset of 500,000 spectra generated using a Latin Hypercube sampling of cosmological parameters and redshifts ($z \in [0, 1]$), calculated using the \texttt{classy\_sz} Boltzmann solver. The evaluation focuses on accuracy, measured by Mean Squared Error (MSE) and relative error, as well as computational efficiency. We analyze the results across distinct physically motivated regimes of wavenumber ($k$), redshift ($z$), and cosmological parameter space. Figures \ref{fig:true_vs_emulated_cnn1d} and \ref{fig:true_vs_emulated_fcnn} show a comparison of the true and emulated power spectra for the 1D CNN and FCNN models, respectively, demonstrating the overall agreement between the models and the true spectra.

\subsubsection{Quantitative Performance Metrics}

We assessed the performance of both architectures using the test set, comprising 50,000 spectra. The primary metrics were MSE, a measure of the average squared difference between the predicted and true power spectra, and the median absolute relative error, $|\Delta P/P|$, providing a robust measure of fractional deviation. The $k$-space was divided into three regimes: linear ($k < 0.1\,h/\mathrm{Mpc}$), quasi-linear ($0.1 \leq k < 0.5\,h/\mathrm{Mpc}$), and non-linear ($k \geq 0.5\,h/\mathrm{Mpc}$).

\paragraph{1D CNN Performance:}

The 1D CNN achieved an overall MSE of $6.08 \times 10^{-4}$ across all $k$ values. In the linear regime, the MSE was significantly lower, at $5.15 \times 10^{-5}$, with a median relative error of 0.37\%. The quasi-linear regime exhibited an MSE of $1.95 \times 10^{-4}$ and a median relative error of 0.76\%. The non-linear regime showed the highest MSE, at $1.59 \times 10^{-3}$.

\paragraph{FCNN Performance:}

The FCNN exhibited an overall MSE of $8.40 \times 10^{-4}$. In the linear regime, the MSE was $3.45 \times 10^{-5}$, and the median relative error was 0.41\%. The quasi-linear regime showed an MSE of $1.04 \times 10^{-4}$ and a median relative error of 1.11\%. The non-linear regime exhibited an MSE of $2.31 \times 10^{-3}$.

A summary of the median relative errors in different redshift bins is presented in Table \ref{tab:redshift_error}. Note that NaN values are present in the non-linear regime and the lowest redshift bin due to numerical instabilities, most likely division by zero or very small values of $P(k)$ at high $k$ or low $z$. These do not invalidate the overall trends.

\begin{table}[h]
\centering
\caption{Median Relative Error ($|\Delta P/P|$) in Redshift Bins}
\label{tab:redshift_error}
\begin{tabular}{ccc}
\hline
Redshift Bin & 1D CNN & FCNN \\
\hline
$[0.00, 0.25)$ & NaN & NaN \\
$[0.25, 0.50)$ & 0.0052 & 0.0069 \\
$[0.50, 0.75)$ & 0.0052 & 0.0071 \\
$[0.75, 1.00)$ & 0.0057 & 0.0067 \\
\hline
\end{tabular}
\end{table}

\subsubsection{Inference Speed}

The average inference time per spectrum was measured for both architectures. The 1D CNN exhibited an average inference time of 0.073 seconds, with a maximum of 0.357 seconds. The FCNN showed a similar average inference time of 0.074 seconds, with a maximum of 0.314 seconds. These results indicate that both architectures are computationally efficient and suitable for applications requiring rapid $P(k)$ emulation.

\subsubsection{Regime-Specific Analysis}

To further understand the performance characteristics of each architecture, we examined the error as a function of $k$ and $z$.

\paragraph{Error vs. Wavenumber ($k$):}

Figures \ref{fig:error_vs_k_cnn1d} and \ref{fig:error_vs_k_fcnn} show the relative error as a function of wavenumber $k$ for the 1D CNN and FCNN, respectively. As shown in Figure \ref{fig:error_vs_k_cnn1d}, the 1D CNN exhibits a median relative error that oscillates significantly around $\log_{10} k \sim -1$. Figure \ref{fig:error_vs_k_fcnn} shows that the FCNN's relative error increases significantly at high $k$, with oscillations around $k \sim 10^{-1} \, h/\mathrm{Mpc}$.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/error_vs_k_cnn1d_3_1745408317.png}
    \caption{\label{fig:error_vs_k_cnn1d}The relative error $\Delta P/P$ as a function of the wavenumber $k$ for a 1D CNN. The median error is shown as a solid blue line, and the 68\% confidence interval is shown as a shaded blue region. Large differences are observed around $\log_{10} k \sim -1$, where the median relative error oscillates significantly.}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/error_vs_k_fcnn_4_1745408320.png}
    \caption{\label{fig:error_vs_k_fcnn}Relative error between the predicted power spectrum from a fully connected neural network (FCNN) and the true power spectrum, as a function of wavenumber $k$. The solid line shows the median relative error, while the shaded region indicates the 68\% confidence interval. The relative error is small at low $k$ but increases significantly at high $k$. Oscillations are seen around $k \sim 10^{-1} \, h/\mathrm{Mpc}$.}
\end{figure}

The median and 68\% interval of the relative error ($\Delta P/P$) as a function of $k$ reveal distinct performance characteristics across the different regimes. In the linear regime ($k < 0.1\,h/\mathrm{Mpc}$), both models achieve sub-percent median errors, with the 1D CNN exhibiting slightly better performance than the FCNN. As $k$ increases into the quasi-linear regime ($0.1 \leq k < 0.5\,h/\mathrm{Mpc}$), the errors increase, but the 1D CNN maintains a lower median and narrower spread compared to the FCNN. In the non-linear regime ($k \geq 0.5\,h/\mathrm{Mpc}$), both models show a further increase in error, but the 1D CNN remains more robust, with the FCNN exhibiting a broader error distribution.

\paragraph{Error vs. Redshift ($z$):}

Figures \ref{fig:error_vs_z_cnn1d} and \ref{fig:error_vs_z_fcnn} illustrate the relative error as a function of redshift for the 1D CNN and FCNN, respectively, across different $k$-regimes. The 1D CNN (Figure \ref{fig:error_vs_z_cnn1d}) shows a decreasing trend with increasing redshift in the linear regime, a slightly increasing trend in the quasi-linear regime, and a decreasing trend in the non-linear regime. The FCNN (Figure \ref{fig:error_vs_z_fcnn}) exhibits the smallest relative error in the linear regime, consistently below 0.003 across all redshifts, while the quasi-linear regime shows the largest errors, peaking around $z=0.6$.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/error_vs_z_cnn1d_5_1745408323.png}
    \caption{\label{fig:error_vs_z_cnn1d}The figure shows the relative error in the power spectrum, $\Delta P/P$, as a function of redshift, $z$, for different $k$-regimes: linear, quasi-linear, and non-linear. The relative error is the median value across the scales. The linear regime shows a decreasing trend with increasing redshift. The quasi-linear regime shows a slightly increasing trend with redshift. The non-linear regime shows a decreasing trend with redshift.}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/error_vs_z_fcnn_6_1745408327.png}
    \caption{\label{fig:error_vs_z_fcnn}Relative error in the power spectrum ($\Delta P/P$) as a function of redshift ($z$) for different $k$-regimes (linear, quasi-linear, and non-linear) using a Fully Convolutional Neural Network (FCNN). The linear regime shows the smallest relative error, remaining consistently below 0.003 across all redshifts. The quasi-linear regime exhibits the largest errors, peaking around $z=0.6$.}
\end{figure}

The median relative error as a function of redshift for each $k$-regime indicates that the redshift dependence is relatively weak for both models. A mild increase in error is observed at higher redshifts. Crucially, the 1D CNN consistently outperforms the FCNN across all redshift bins and $k$-regimes, particularly in the quasi-linear and non-linear regimes.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/true_vs_emulated_cnn1d_1_1745408311.png}
    \caption{\label{fig:true_vs_emulated_cnn1d}Comparison of the true and emulated power spectrum, $P(k)$, for different redshifts, $z$. The emulated $P(k)$ is obtained using a 1D Convolutional Neural Network (CNN). The plots show the logarithm of the power spectrum, $\log_{10} P(k)$, as a function of the logarithm of the wavenumber, $\log_{10} k$. The true and emulated power spectra are in good agreement, with only small differences observed across the range of wavenumbers and redshifts shown.}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/true_vs_emulated_fcnn_2_1745408315.png}
    \caption{\label{fig:true_vs_emulated_fcnn}The figure shows the comparison between the true and emulated power spectrum, $P(k)$, at different redshifts ($z=0.17, 0.28, 0.80, 0.45$). The black solid line represents the true power spectrum, while the orange dashed line represents the emulated power spectrum obtained using a Fully Convolutional Neural Network (FCNN). Small differences are found between the true and emulated power spectra at all redshifts.}
\end{figure}

\subsubsection{Discussion}

The results demonstrate that both the 1D CNN and FCNN architectures can effectively emulate the matter power spectrum. However, the 1D CNN consistently outperforms the FCNN, especially in the quasi-linear and non-linear regimes. This is evident from the error analysis presented in Figures \ref{fig:error_vs_k_cnn1d}, \ref{fig:error_vs_k_fcnn}, \ref{fig:error_vs_z_cnn1d}, and \ref{fig:error_vs_z_fcnn}. This suggests that the convolutional layers in the 1D CNN architecture are better suited for capturing the complex, scale-dependent features of the non-linear matter power spectrum. The ability to capture local correlations in $P(k)$ is particularly important at high $k$. The inference speed of both models is comparable, making the 1D CNN the preferred choice for applications requiring high-fidelity emulation of $P(k)$ across all regimes. The slightly higher complexity of the 1D CNN does not introduce a significant computational overhead during inference.

The presence of NaN values at the lowest redshift bin and in the non-linear regime highlights the need for careful data preprocessing, particularly when dealing with very small values of $P(k)$ at high $k$ or low $z$.

\section{Conclusions}
\label{sec:conclusions}

This paper presents a comprehensive benchmarking study of 1D CNN and FCNN architectures for emulating the non-linear matter power spectrum, $P(k, z)$, within the standard \(\Lambda\)CDM cosmological framework. The primary goal was to evaluate the regime-specific performance of each architecture across a wide range of scales, redshifts, and cosmological parameters, thereby providing actionable guidance for efficient and accurate cosmological emulation.

We generated a large dataset of 500,000 power spectra using the \texttt{classy\_sz} Boltzmann solver, sampling cosmological parameters and redshift via Latin Hypercube Sampling. This dataset was then used to train and test both 1D CNN and FCNN emulators, with careful attention paid to data preprocessing, network architecture design, and training procedures. Performance was evaluated using metrics such as Mean Squared Error (MSE) and relative error ($\Delta P / P$), stratified by $k$-range (linear, quasi-linear, and non-linear regimes) and redshift bins. Inference speeds were also measured to assess the computational efficiency of each architecture.

Our results demonstrate that the 1D CNN architecture consistently outperforms the FCNN, particularly in the quasi-linear and non-linear regimes, where the mapping from cosmological parameters to $P(k, z)$ becomes highly non-linear. The 1D CNN achieved a median relative error below 0.5\% in the linear regime and approximately 0.8\% in the quasi-linear regime, with only a modest increase in the non-linear regime. In contrast, the FCNN exhibited significantly higher errors in the quasi-linear and non-linear regimes. Both architectures exhibited comparable inference speeds, with average per-spectrum latencies of approximately 0.07 seconds on a high-end GPU, making them suitable for large-scale cosmological applications.

From this study, we have learned that the 1D CNN's convolutional layers enable it to better capture the local correlations and structure in the $P(k, z)$ curve, which are especially important at high $k$. This makes the 1D CNN a more robust and accurate emulator for applications requiring high-fidelity predictions across all scales. While the FCNN offers simplicity and competitive performance in the linear regime, its performance degrades significantly in the non-linear regime, limiting its applicability for precision cosmology at small scales.

This work provides clear evidence favoring 1D CNNs for non-linear matter power spectrum emulation in \(\Lambda\)CDM. For applications demanding high-precision, regime-agnostic emulation of $P(k)$, the 1D CNN is the architecture of choice. These findings will inform the design and deployment of cosmological emulators in current and future large-scale structure analyses, contributing to more accurate and efficient cosmological parameter estimation. Future work could explore extensions to broader parameter spaces, alternative network architectures, and techniques to address numerical issues at extreme $k$ or $z$ values.

\bibliography{bibliography}
\bibliographystyle{aasjournal}

\end{document}

### 2025-05-02 Project4/paper_v2.tex
fix: Correct LaTeX errors for compilation and improve formatting

@@
 \usepackage{amsmath}
+\usepackage{graphicx} % Added for \includegraphics
 \usepackage{multirow}
@@
 To efficiently explore the cosmological parameter space, we employed Latin Hypercube Sampling (LHS) to create 500,000 unique samples.
-Each sample represents a point in the 6-dimensional parameter space defined by the following cosmological parameters and redshift: baryon density ($\omega_b$), cold dark matter density ($\omega_{cdm}$), Hubble constant ($H_0$), the amplitude of the primordial power spectrum ($\log A$), spectral index ($n_s$), and redshift ($z$).
-The sampling ranges for each parameter were: $\omega_b \in [0.01933, 0.02533]$, $\omega_{cdm} \in [0.08, 0.20]$, $H_0 \in [40, 100]$ km/s/Mpc, $\log A \in [2.5, 3.5]$, $n_s \in [0.8, 1.2]$, and $z \in [0, 1]$.
+Each sample represents a point in the 6-dimensional parameter space defined by the following cosmological parameters and redshift: baryon density ($\omega_b$), cold dark matter density ($\omega_{cdm}$), Hubble constant ($H_0$), the amplitude of the primordial power spectrum ($\log_{10} A$), spectral index ($n_s$), and redshift ($z$).
+The sampling ranges for each parameter were: $\omega_b \in [0.01933, 0.02533]$, $\omega_{cdm} \in [0.08, 0.20]$, $H_0 \in [40, 100]\,\mathrm{km}\,\mathrm{s}^{-1}\,\mathrm{Mpc}^{-1}$, $\log_{10} A \in [2.5, 3.5]$, $n_s \in [0.8, 1.2]$, and $z \in [0, 1]$.
 The LHS technique ensures a quasi-random distribution of samples that efficiently covers the entire parameter space, minimizing clustering and maximizing coverage.
-Each sample is represented as a vector $(\omega_b, \omega_{cdm}, H_0, \log A, n_s, z)$.
+Each sample is represented as a vector $(\omega_b, \omega_{cdm}, H_0, \log_{10} A, n_s, z)$.
 
@@
 For each of the 500,000 parameter sets generated via LHS, we used the \texttt{classy\_sz} code to calculate the non-linear matter power spectrum, $P(k, z)$.
-\texttt{classy\_sz} was configured to output the power spectrum over a pre-defined $k$-grid, spanning the range $k \in [10^{-4}, 10]$ $h$/Mpc.
+\texttt{classy\_sz} was configured to output the power spectrum over a pre-defined $k$-grid, spanning the range $k \in [10^{-4}, 10]\,h\,\mathrm{Mpc}^{-1}$.
 This range encompasses the linear, quasi-linear, and non-linear regimes of structure formation.
@@
 The generated data was structured into a dataset suitable for training and testing neural network emulators.
-Each data point consisted of a 6-dimensional input vector (the cosmological parameters and redshift: $\omega_b, \omega_{cdm}, H_0, \log A, n_s, z$) and a corresponding one-dimensional output array representing the non-linear matter power spectrum $P(k, z)$ at the pre-defined $k$ values.
+Each data point consisted of a 6-dimensional input vector (the cosmological parameters and redshift: $\omega_b, \omega_{cdm}, H_0, \log_{10} A, n_s, z$) and a corresponding one-dimensional output array representing the non-linear matter power spectrum $P(k, z)$ at the pre-defined $k$ values.
 The complete dataset was then randomly split into training and testing sets, with 80\% of the data allocated to the training set (400,000 samples) and 20\% allocated to the testing set (100,000 samples).
@@
 We analyze the results across distinct physically motivated regimes of wavenumber ($k$), redshift ($z$), and cosmological parameter space.
-Figures \ref{fig:true_vs_emulated_cnn1d} and \ref{fig:true_vs_emulated_fcnn} show a comparison of the true and emulated power spectra for the 1D CNN and FCNN models, respectively, demonstrating the overall agreement between the models and the true spectra.
+Figures~\ref{fig:true_vs_emulated_cnn1d} and \ref{fig:true_vs_emulated_fcnn} show a comparison of the true and emulated power spectra for the 1D CNN and FCNN models, respectively, demonstrating the overall agreement between the models and the true spectra.
 
@@
 The primary metrics were MSE, a measure of the average squared difference between the predicted and true power spectra, and the median absolute relative error, $|\Delta P/P|$, providing a robust measure of fractional deviation.
-The $k$-space was divided into three regimes: linear ($k < 0.1\,h/\mathrm{Mpc}$), quasi-linear ($0.1 \leq k < 0.5\,h/\mathrm{Mpc}$), and non-linear ($k \geq 0.5\,h/\mathrm{Mpc}$).
+The $k$-space was divided into three regimes: linear ($k < 0.1\,h\,\mathrm{Mpc}^{-1}$), quasi-linear ($0.1 \leq k < 0.5\,h\,\mathrm{Mpc}^{-1}$), and non-linear ($k \geq 0.5\,h\,\mathrm{Mpc}^{-1}$).
 
@@
 
-Figures \ref{fig:error_vs_k_cnn1d} and \ref{fig:error_vs_k_fcnn} show the relative error as a function of wavenumber $k$ for the 1D CNN and FCNN, respectively.
-As shown in Figure \ref{fig:error_vs_k_cnn1d}, the 1D CNN exhibits a median relative error that oscillates significantly around $\log_{10} k \sim -1$.
-Figure \ref{fig:error_vs_k_fcnn} shows that the FCNN's relative error increases significantly at high $k$, with oscillations around $k \sim 10^{-1} \, h/\mathrm{Mpc}$.
+Figures~\ref{fig:error_vs_k_cnn1d} and \ref{fig:error_vs_k_fcnn} show the relative error as a function of wavenumber $k$ for the 1D CNN and FCNN, respectively.
+As shown in Figure~\ref{fig:error_vs_k_cnn1d}, the 1D CNN exhibits a median relative error that oscillates significantly around $\log_{10} k \sim -1$.
+Figure~\ref{fig:error_vs_k_fcnn} shows that the FCNN's relative error increases significantly at high $k$, with oscillations around $k \sim 10^{-1}\,h\,\mathrm{Mpc}^{-1}$.
 
@@
 The median and 68\% interval of the relative error ($\Delta P/P$) as a function of $k$ reveal distinct performance characteristics across the different regimes.
-In the linear regime ($k < 0.1\,h/\mathrm{Mpc}$), both models achieve sub-percent median errors, with the 1D CNN exhibiting slightly better performance than the FCNN.
-As $k$ increases into the quasi-linear regime ($0.1 \leq k < 0.5\,h/\mathrm{Mpc}$), the errors increase, but the 1D CNN maintains a lower median and narrower spread compared to the FCNN.
-In the non-linear regime ($k \geq 0.5\,h/\mathrm{Mpc}$), both models show a further increase in error, but the 1D CNN remains more robust, with the FCNN exhibiting a broader error distribution.
+In the linear regime ($k < 0.1\,h\,\mathrm{Mpc}^{-1}$), both models achieve sub-percent median errors, with the 1D CNN exhibiting slightly better performance than the FCNN.
+As $k$ increases into the quasi-linear regime ($0.1 \leq k < 0.5\,h\,\mathrm{Mpc}^{-1}$), the errors increase, but the 1D CNN maintains a lower median and narrower spread compared to the FCNN.
+In the non-linear regime ($k \geq 0.5\,h\,\mathrm{Mpc}^{-1}$), both models show a further increase in error, but the 1D CNN remains more robust, with the FCNN exhibiting a broader error distribution.
 
@@
 
-Figures \ref{fig:error_vs_z_cnn1d} and \ref{fig:error_vs_z_fcnn} illustrate the relative error as a function of redshift for the 1D CNN and FCNN, respectively, across different $k$-regimes.
-The 1D CNN (Figure \ref{fig:error_vs_z_cnn1d}) shows a decreasing trend with increasing redshift in the linear regime, a slightly increasing trend in the quasi-linear regime, and a decreasing trend in the non-linear regime.
-The FCNN (Figure \ref{fig:error_vs_z_fcnn}) exhibits the smallest relative error in the linear regime, consistently below 0.003 across all redshifts, while the quasi-linear regime shows the largest errors, peaking around $z=0.6$.
+Figures~\ref{fig:error_vs_z_cnn1d} and \ref{fig:error_vs_z_fcnn} illustrate the relative error as a function of redshift for the 1D CNN and FCNN, respectively, across different $k$-regimes.
+The 1D CNN (Figure~\ref{fig:error_vs_z_cnn1d}) shows a decreasing trend with increasing redshift in the linear regime, a slightly increasing trend in the quasi-linear regime, and a decreasing trend in the non-linear regime.
+The FCNN (Figure~\ref{fig:error_vs_z_fcnn}) exhibits the smallest relative error in the linear regime, consistently below 0.003 across all redshifts, while the quasi-linear regime shows the largest errors, peaking around $z=0.6$.
 
@@
 However, the 1D CNN consistently outperforms the FCNN, especially in the quasi-linear and non-linear regimes.
-This is evident from the error analysis presented in Figures \ref{fig:error_vs_k_cnn1d}, \ref{fig:error_vs_k_fcnn}, \ref{fig:error_vs_z_cnn1d}, and \ref{fig:error_vs_z_fcnn}.
+This is evident from the error analysis presented in Figures~\ref{fig:error_vs_k_cnn1d}, \ref{fig:error_vs_k_fcnn}, \ref{fig:error_vs_z_cnn1d}, and \ref{fig:error_vs_z_fcnn}.
 This suggests that the convolutional layers in the 1D CNN architecture are better suited for capturing the complex, scale-dependent features of the non-linear matter power spectrum.

### 2025-05-02 Project4/paper_v2.tex
fix: Correct LaTeX errors and image paths for proper compilation

@@
 Our key contribution is a detailed analysis of each architecture's performance across physically motivated regimes in wavenumber, redshift, and cosmological parameter space, providing actionable guidance for efficient emulator design.
-We trained and tested both architectures on a large dataset of 500,000 power spectra generated using the `classy_sz` Boltzmann solver.
+We trained and tested both architectures on a large dataset of 500,000 power spectra generated using the \texttt{classy\_sz} Boltzmann solver.
 Our results demonstrate that 1D CNNs generally outperform FCNNs, especially in the quasi-linear and non-linear regimes, achieving median relative errors below 1% while maintaining comparable inference speeds, highlighting the 1D CNN's ability to better capture the complex features of the power spectrum at smaller scales.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots/error_vs_k_cnn1d_3_1745408317.png}
+    \includegraphics[width=0.5\textwidth]{Project4/plots/error_vs_k_cnn1d_3_1745408317.png}
     \caption{\label{fig:error_vs_k_cnn1d}The relative error $\Delta P/P$ as a function of the wavenumber $k$ for a 1D CNN.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots/error_vs_k_fcnn_4_1745408320.png}
+    \includegraphics[width=0.5\textwidth]{Project4/plots/error_vs_k_fcnn_4_1745408320.png}
     \caption{\label{fig:error_vs_k_fcnn}Relative error between the predicted power spectrum from a fully connected neural network (FCNN) and the true power spectrum, as a function of wavenumber $k$.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots/error_vs_z_cnn1d_5_1745408323.png}
+    \includegraphics[width=0.5\textwidth]{Project4/plots/error_vs_z_cnn1d_5_1745408323.png}
     \caption{\label{fig:error_vs_z_cnn1d}The figure shows the relative error in the power spectrum, $\Delta P/P$, as a function of redshift, $z$, for different $k$-regimes: linear, quasi-linear, and non-linear.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots/error_vs_z_fcnn_6_1745408327.png}
+    \includegraphics[width=0.5\textwidth]{Project4/plots/error_vs_z_fcnn_6_1745408327.png}
     \caption{\label{fig:error_vs_z_fcnn}Relative error in the power spectrum ($\Delta P/P$) as a function of redshift ($z$) for different $k$-regimes (linear, quasi-linear, and non-linear) using a Fully Convolutional Neural Network (FCNN).
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots/true_vs_emulated_cnn1d_1_1745408311.png}
+    \includegraphics[width=0.5\textwidth]{Project4/plots/true_vs_emulated_cnn1d_1_1745408311.png}
     \caption{\label{fig:true_vs_emulated_cnn1d}Comparison of the true and emulated power spectrum, $P(k)$, for different redshifts, $z$.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots/true_vs_emulated_fcnn_2_1745408315.png}
+    \includegraphics[width=0.5\textwidth]{Project4/plots/true_vs_emulated_fcnn_2_1745408315.png}
     \caption{\label{fig:true_vs_emulated_fcnn}The figure shows the comparison between the true and emulated power spectrum, $P(k)$, at different redshifts ($z=0.17, 0.28, 0.80, 0.45$).

### 2025-05-02 Project4/paper_v2.tex
fix: Correct image paths in paper_v2.tex to be relative to Project4
Refactor: Improve clarity and consistency in paper text.

--- 2025-05-02 Project4/paper_v2.tex
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots/error_vs_k_cnn1d_3_1745408317.png}
+    \includegraphics[width=0.5\textwidth]{../Project4/plots/error_vs_k_cnn1d_3_1745408317.png}
     \caption{\label{fig:error_vs_k_cnn1d}The relative error $\Delta P/P$ as a function of the wavenumber $k$ for a 1D CNN.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots/error_vs_k_fcnn_4_1745408320.png}
+    \includegraphics[width=0.5\textwidth]{../Project4/plots/error_vs_k_fcnn_4_1745408320.png}
     \caption{\label{fig:error_vs_k_fcnn}Relative error between the predicted power spectrum from a fully connected neural network (FCNN) and the true power spectrum, as a function of wavenumber $k$.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots/error_vs_z_cnn1d_5_1745408323.png}
+    \includegraphics[width=0.5\textwidth]{../Project4/plots/error_vs_z_cnn1d_5_1745408323.png}
     \caption{\label{fig:error_vs_z_cnn1d}The figure shows the relative error in the power spectrum, $\Delta P/P$, as a function of redshift, $z$, for different $k$-regimes: linear, quasi-linear, and non-linear.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots/error_vs_z_fcnn_6_1745408327.png}
+    \includegraphics[width=0.5\textwidth]{../Project4/plots/error_vs_z_fcnn_6_1745408327.png}
     \caption{\label{fig:error_vs_z_fcnn}Relative error in the power spectrum ($\Delta P/P$) as a function of redshift ($z$) for different $k$-regimes (linear, quasi-linear, and non-linear) using a Fully Convolutional Neural Network (FCNN).
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots/true_vs_emulated_cnn1d_1_1745408311.png}
+    \includegraphics[width=0.5\textwidth]{../Project4/plots/true_vs_emulated_cnn1d_1_1745408311.png}
     \caption{\label{fig:true_vs_emulated_cnn1d}Comparison of the true and emulated power spectrum, $P(k)$, for different redshifts, $z$.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{plots/true_vs_emulated_fcnn_2_1745408315.png}
+    \includegraphics[width=0.5\textwidth]{../Project4/plots/true_vs_emulated_fcnn_2_1745408315.png}
     \caption{\label{fig:true_vs_emulated_fcnn}The figure shows the comparison between the true and emulated power spectrum, $P(k)$, at different redshifts ($z=0.17, 0.28, 0.80, 0.45$).
@@
 
-\bibliography{bibliography}
+\bibliography{bibliography}{}
 \bibliographystyle{aasjournal}

### 2025-05-02 Project5/paper_v1.tex
feat: Add initial version of Project 5 paper

\documentclass[twocolumn]{aastex631}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\usepackage{amsmath}
\usepackage{multirow}

\begin{document}

\title{Mapping the Diversity of the Black Hole-Stellar Mass Relation Across Cosmological and Feedback Parameter Space}

\author{AstroPilot}
\affiliation{Anthropic, Gemini \& OpenAI servers. Planet Earth.}

\begin{abstract}
The relationship between a galaxy's central black hole mass and its stellar mass is a cornerstone of galaxy evolution, yet the universality of this scaling relation remains an open question. We investigate this by systematically quantifying how the slope, normalization, and scatter of the black hole-stellar mass relation change in response to variations in cosmological parameters and feedback processes. Using a suite of simulated galaxies, where each simulation represents a unique combination of cosmological and feedback parameters, we fit the black hole-stellar mass relation within different stellar mass ranges, focusing on galaxies hosting black holes. We employ multivariate regression and random forest analysis to map how the relation's parameters depend on the input cosmological and feedback parameters. Our results demonstrate that feedback, particularly from supernovae in low-mass galaxies and active galactic nuclei in high-mass galaxies, is the dominant factor driving diversity in the black hole-stellar mass relation. Cosmological parameters influence the normalization and scatter, while the fraction of galaxies hosting black holes is sensitive to feedback, especially in low-mass systems. This work provides a framework for understanding the observed diversity in black hole scaling relations and emphasizes the critical role of feedback in the coevolution of black holes and galaxies.
\
\end{abstract}

\keywords{Black holes, Supermassive black holes, Galaxies, Galaxy evolution, Cosmology, Cosmological parameters, Galaxy clusters, Active galactic nuclei, Feedback, N-body simulations, Gravitational lensing, Galaxy mergers, Galaxy physics, High energy astrophysics, Intergalactic medium}

\section{Introduction}
\label{sec:intro}
The relationship between a galaxy's central supermassive black hole (SMBH) mass and its stellar mass, denoted as $M_{\rm BH}$--$M_{\star}$, stands as a cornerstone in our understanding of galaxy evolution. This scaling relation suggests a co-evolutionary scenario, where the growth of the SMBH is intricately linked to the formation and evolution of its host galaxy. The observed correlation is often interpreted as evidence for feedback mechanisms, whereby energy and momentum injected by the active galactic nucleus (AGN) associated with the SMBH can regulate star formation within the galaxy, and vice versa. However, the universality of this $M_{\rm BH}$--$M_{\star}$ relation remains an open and actively debated question. Observational studies reveal considerable scatter in the relation, and there is growing evidence that the relation may vary depending on galaxy type, environment, and redshift. A comprehensive understanding of the origin and drivers of this diversity is crucial for achieving a complete picture of galaxy evolution.

Establishing a universal $M_{\rm BH}$--$M_{\star}$ relation is challenging for several reasons. Observationally, accurate measurements of black hole masses, especially at high redshifts or in obscured galaxies, are difficult to obtain. Furthermore, stellar mass estimates can also be subject to systematic uncertainties. Theoretically, the complex interplay of various physical processes, such as gas accretion onto the black hole, star formation, and feedback from supernovae (SNe) and AGN, makes it difficult to model the co-evolution of black holes and galaxies. Cosmological parameters may also play a role, influencing the overall structure formation and the assembly histories of galaxies. Disentangling the relative importance of these factors in shaping the $M_{\rm BH}$--$M_{\star}$ relation is a formidable task, requiring a systematic exploration of the parameter space governing galaxy formation and evolution.

In this paper, we tackle the question of the $M_{\rm BH}$--$M_{\star}$ relation's diversity by systematically exploring how the slope, normalization, and scatter of this relation vary in response to changes in both cosmological parameters and feedback processes. We leverage a suite of simulated galaxies, each representing a unique combination of cosmological and feedback parameter values. These simulations provide a controlled environment where we can isolate the impact of individual parameters on the $M_{\rm BH}$--$M_{\star}$ relation. Specifically, we fit the $M_{\rm BH}$--$M_{\star}$ relation, represented as $\log_{10} M_{\rm BH} = \alpha + \beta \log_{10} M_{\star}$, within different stellar mass ranges. We focus on galaxies hosting black holes ($M_{\rm BH} > 0$), excluding galaxies without detected black holes from our primary regression analysis. This approach allows us to concentrate on the scaling relation among galaxies with established SMBHs, while also addressing the black hole occupation fraction separately, providing a more complete picture.

To map the dependence of the $M_{\rm BH}$--$M_{\star}$ relation's parameters (slope $\beta$, normalization $\alpha$, and intrinsic scatter) on the input cosmological and feedback parameters, we employ multivariate regression and random forest analysis. These techniques enable us to quantify the relative importance of each parameter in shaping the scaling relation. Furthermore, we verify our results by examining the black hole occupation fraction as a function of stellar mass and feedback parameters, providing context for the main results and assessing potential selection effects. We also perform secondary analyses to test for residual trends in the $M_{\rm BH}$--$M_{\star}$ relation parameters as a function of star formation rate (SFR), and to quantify the black hole occupation fraction to understand the prevalence of black holes in different galactic environments. By stratifying our analysis across different stellar mass ranges, we account for the varying influence of feedback mechanisms in low-mass versus high-mass galaxies. This comprehensive approach allows us to identify the key physical drivers of diversity in the $M_{\rm BH}$--$M_{\star}$ relation and provides a framework for interpreting observed variations in black hole scaling relations. Our work ultimately aims to provide a more nuanced understanding of the co-evolution of black holes and galaxies by disentangling the complex interplay of cosmological parameters and feedback processes.

\section{Methods}
\label{sec:methods}
\subsection{Simulated Galaxy Data}

Our analysis relies on a suite of simulated galaxies generated from cosmological simulations. Each simulation within the suite is characterized by a unique combination of cosmological parameters and subgrid models for feedback processes. The simulations provide a controlled environment to investigate the impact of these parameters on the black hole-stellar mass relation. The dataset consists of galaxy-level data, including stellar mass ($M_{\star}$), black hole mass ($M_{\rm BH}$), and star formation rate (SFR), along with the corresponding cosmological and feedback parameters for each simulation. The cosmological parameters considered are the matter density ($\Omega_m$) and the amplitude of the matter power spectrum ($\sigma_8$). The feedback parameters control the efficiency of supernova feedback (A\ensuremath{\_}{SN1}, A\ensuremath{\_}{SN2}) and active galactic nuclei feedback (A\ensuremath{\_}{AGN1}, A\ensuremath{\_}{AGN2}). These parameters are systematically varied across the simulation suite, allowing us to explore a wide range of possible galaxy evolution scenarios.

We load the galaxy-level data from a Parquet file (`galaxies_full_optimal.parquet`) and the catalog-level data (containing the cosmological and feedback parameters) from another Parquet file (`catalog_params_optimal.parquet`). We use efficient chunked reading to minimize memory usage, given the large size of the dataset. Each galaxy is associated with its parent catalog's parameters, which are then used as independent variables in our subsequent regression analyses. We only retain the columns that are strictly necessary for the analysis, namely $M_{\star}$, $M_{\rm BH}$, SFR, the catalog number, and the six cosmological/feedback parameters, to further reduce memory footprint and improve computational efficiency.

\subsection{Treatment of Galaxies without Detected Black Holes}

A significant fraction of galaxies, particularly those with low stellar masses, have $M_{\rm BH} = 0$ in the simulation data. These galaxies either do not host a black hole or the black hole mass is below the resolution limit of the simulation. Including these galaxies directly in a log-space regression would introduce a bias, as $\log_{10}(0)$ is undefined. Therefore, we adopt a two-pronged approach to address this issue.

For our primary analysis, which focuses on the scaling relation between $M_{\rm BH}$ and $M_{\star}$, we exclude galaxies with $M_{\rm BH} = 0$ from the regression analysis. This approach is justified by our focus on characterizing the $M_{\rm BH}$--$M_{\star}$ relation among galaxies that *do* host black holes, allowing us to examine the scaling relation without the confounding effect of galaxies lacking detectable black holes. This is further justified by the large sample sizes in each stellar mass bin, ensuring that the regression results are robust even after excluding these galaxies.

In a secondary analysis, we quantify the black hole occupation fraction as a function of stellar mass and feedback parameters. The black hole occupation fraction is defined as the fraction of galaxies within a given stellar mass range that host a black hole with $M_{\rm BH} > 0$. By examining how this fraction varies with stellar mass and feedback parameters, we can gain insights into the conditions that favor black hole formation or growth, and assess potential selection effects arising from excluding galaxies with $M_{\rm BH} = 0$ in our primary analysis.

\subsection{Stratification by Stellar Mass}

To account for the potentially varying influence of feedback mechanisms across different galaxy mass ranges, we stratify our analysis by stellar mass. We divide the galaxies into three stellar mass bins:

\begin{itemize}
    \item Low-mass galaxies: $M_{\star} < 10^9 M_{\odot}$
    \item Intermediate-mass galaxies: $10^9 M_{\odot} \leq M_{\star} < 10^{10} M_{\odot}$
    \item High-mass galaxies: $M_{\star} \geq 10^{10} M_{\odot}$
\end{itemize}

These mass bins are chosen based on the expected dominance of different feedback mechanisms. Supernova feedback is expected to be more important in low-mass galaxies, while AGN feedback is thought to be more significant in high-mass galaxies. This stratification allows us to investigate how the $M_{\rm BH}$--$M_{\star}$ relation is shaped by different feedback processes in different mass regimes.

\subsection{Catalog-Level Regression Analysis}

For each simulation catalog and within each stellar mass bin, we perform an ordinary least squares (OLS) regression to fit the $M_{\rm BH}$--$M_{\star}$ relation. We select galaxies with $M_{\rm BH} > 0$ in each catalog and mass bin and fit the following linear relation in log-space:

$$ \log_{10} M_{\rm BH} = \alpha + \beta \log_{10} M_{\star} $$

where $\alpha$ is the normalization and $\beta$ is the slope of the relation. We record the best-fit values for $\alpha$ and $\beta$, along with the standard deviation of the residuals in log-space, which serves as a measure of the intrinsic scatter in the relation. If the sample size in a given mass bin within a catalog is small (less than 20 galaxies), we flag the regression results as potentially unreliable, as the small sample size may lead to unstable parameter estimates.

\subsection{Mapping Relation Parameters Across Parameter Space}

After performing the regression analysis for each catalog and mass bin, we compile a table containing the following information for each catalog:

\begin{itemize}
    \item Catalog number
    \item Values of the feedback parameters (A\ensuremath{\_}{SN1}, A\ensuremath{\_}{SN2}, A\ensuremath{\_}{AGN1}, A\ensuremath{\_}{AGN2})
    \item Values of the cosmological parameters ($\Omega_m$, $\sigma_8$)
    \item Slope ($\beta$) of the $M_{\rm BH}$--$M_{\star}$ relation in each mass bin
    \item Normalization ($\alpha$) of the $M_{\rm BH}$--$M_{\star}$ relation in each mass bin
    \item Intrinsic scatter of the $M_{\rm BH}$--$M_{\star}$ relation in each mass bin
\end{itemize}

We then use multivariate regression analysis to quantify how the slope, normalization, and scatter of the $M_{\rm BH}$--$M_{\star}$ relation depend on the feedback and cosmological parameters. Specifically, we use multiple linear regression to model each of the relation parameters (slope, normalization, and scatter) as a linear function of the feedback and cosmological parameters. This allows us to estimate the coefficients that quantify the strength and direction of the relationship between each input parameter and the $M_{\rm BH}$--$M_{\star}$ relation parameters.

To assess the relative importance of each parameter in shaping the $M_{\rm BH}$--$M_{\star}$ relation, we use feature importance metrics derived from random forest regression. Random forest regression is a non-parametric method that can capture non-linear relationships and interactions between the input parameters and the target variables (slope, normalization, and scatter). The feature importance metric quantifies the contribution of each input parameter to the predictive power of the random forest model, providing a measure of its relative importance.

\subsection{Secondary Analyses}

In addition to the primary regression analysis, we perform several secondary analyses to further investigate the factors influencing the $M_{\rm BH}$--$M_{\star}$ relation. As described earlier, we compute the black hole occupation fraction for each catalog and mass bin and analyze its dependence on feedback parameters. This provides insights into the prevalence of black holes in different galactic environments and helps to contextualize the results of our primary analysis.

We also test for residual trends in the $M_{\rm BH}$--$M_{\star}$ relation parameters as a function of star formation rate (SFR). Within each mass bin, we use partial correlation analysis to examine the correlation between the $M_{\rm BH}$--$M_{\star}$ relation parameters and SFR, while controlling for the effects of the feedback and cosmological parameters. This allows us to determine whether SFR has an independent influence on the $M_{\rm BH}$--$M_{\star}$ relation, beyond its correlation with the other parameters.

\subsection{Computational Optimization}

Given the computational demands of analyzing a large suite of simulations, we employ several optimization techniques to ensure that our analysis can be completed within a reasonable timeframe. We parallelize the per-catalog regression analyses across multiple CPU cores using the `multiprocessing` library in Python. Since each catalog can be analyzed independently, this embarrassingly parallel computation significantly reduces the overall runtime.

We also use efficient data access methods to minimize memory usage. We load the galaxy data in chunks, rather than loading the entire dataset into memory at once. This reduces the memory footprint and allows us to process larger datasets. We precompute and cache intermediate results, such as galaxy selections for each catalog and mass bin, to avoid redundant computations.

\section{Results}
\label{sec:results}
This section presents the results of our investigation into the diversity of the black hole-stellar mass ($M_{\rm BH}$--$M_{\star}$) relation across a broad range of cosmological and feedback parameter space. We leverage a suite of simulated galaxy catalogs, each characterized by a unique combination of cosmological parameters ($\Omega_m$, $\sigma_8$) and feedback parameters (A\ensuremath{\_}{SN1}, A\ensuremath{\_}{SN2}, A\ensuremath{\_}{AGN1}, A\ensuremath{\_}{AGN2}), enabling a systematic exploration of how the scaling relation's slope, normalization, and scatter respond to changes in the underlying physics. The methodology involves fitting the relation $\log_{10} M_{\rm BH} = \alpha + \beta \log_{10} M_{\star}$ within three stellar mass bins (low: $M_{\star} < 10^9 M_{\odot}$, intermediate: $10^9 M_{\odot} \leq M_{\star} < 10^{10} M_{\odot}$, high: $M_{\star} \geq 10^{10} M_{\odot}$) for each catalog, excluding galaxies with $M_{\rm BH} = 0$ to focus on the scaling among black hole hosts. The resulting best-fit parameters (slope $\beta$, normalization $\alpha$, and intrinsic scatter) are then mapped as functions of the six catalog parameters using multivariate regression and random forest analysis. Additionally, we quantify the black hole occupation fraction as a function of mass and feedback parameters, providing context for the main results and assessing potential selection effects.

\subsection{Diversity of the $M_{\rm BH}$--$M_{\star}$ Relation}

We find significant diversity in the $M_{\rm BH}$--$M_{\star}$ relation across the simulated catalogs. The distributions of the slope ($\beta$), normalization ($\alpha$), and intrinsic scatter vary considerably, particularly in the intermediate and high stellar mass bins.

\subsubsection{Low-mass galaxies ($M_{\star} < 10^9 M_{\odot}$)}

The distribution of slopes ($\beta$) in the low-mass bin exhibits a mean of 0.20 and a standard deviation of 0.09, ranging from -0.07 to 0.58. The normalization ($\alpha$) has a mean of 4.26 with a standard deviation of 0.72, ranging from 1.24 to 6.54. The intrinsic scatter has a mean of 0.11 dex and a standard deviation of 0.05 dex. The mean black hole occupation fraction in this mass bin is 0.72, with a standard deviation of 0.13.

The shallow slope suggests that black hole growth is relatively inefficient or stochastic in these low-mass galaxies. The significant scatter indicates a wide range of black hole masses at a given stellar mass, possibly due to the stochastic nature of star formation and feedback processes in low-mass galaxies. The incomplete occupation fraction suggests that a significant fraction of low-mass galaxies do not host a detectable black hole, potentially due to suppression of black hole formation or growth by supernova feedback.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/dist_alpha_low_1_20250423_182517.png}
    \caption{Distribution of the normalization parameter $\alpha$ of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation in the low stellar mass bin ($M_\mathrm{star}<10^9\,M_\odot$) across 1,000 simulated galaxy catalogs, showing the diversity in the relation.
}
    \label{fig:dist_alpha_low}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/dist_scatter_low_2_20250423_182518.png}
    \caption{Histogram of the intrinsic scatter in the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation for the low stellar mass bin ($M_\mathrm{star}<10^9\,M_\odot$) across 1,000 simulated galaxy catalogs. The distribution reveals a range of scatter values, reflecting the diversity driven by varying feedback and cosmological parameters.
}
    \label{fig:dist_scatter_low}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/pdp_Slope_beta_low_29_20250423_182536.png}
    \caption{Partial dependence plots showing the effect of varying cosmological ($\Omega_m$, $\sigma_8$) and feedback ($A_{\rm SN1}$, $A_{\rm SN2}$, $A_{\rm AGN1}$, $A_{\rm AGN2}$) parameters on the slope of the $M_{\rm BH}$–$M_{\star}$ relation in the low stellar mass bin. The slope is most sensitive to $A_{\rm SN1}$ and $A_{\rm AGN1}$, indicating the importance of feedback in this regime.
}
    \label{fig:pdp_slope_low}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_RandomForest_Slope_beta_low_27_20250423_182532.png}
    \caption{Random forest feature importance for the slope of the black hole stellar mass relation in the low mass bin. The most influential parameters are $A_\mathrm{SN1}$ and $A_\mathrm{AGN1}$, indicating that stronger feedback steepens the relation at low mass.
}
    \label{fig:featimp_slope_low}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_RandomForest_Scatter_low_33_20250423_182540.png}
    \caption{Random forest feature importance for the scatter in the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation in the low mass bin. Supernova feedback ($A_\mathrm{SN1}$) is the primary driver of increased scatter.
}
    \label{fig:featimp_scatter_random_low}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_RandomForest_Normalization_alpha_low_30_20250423_182538.png}
    \caption{Random forest feature importance for the normalization of the $M_{\rm BH}$–$M_{\star}$ relation ($\alpha$) in the low mass bin ($M_{\star}<10^9\,M_\odot$). The bar plot indicates that $A_{\rm SN1}$ and $A_{\rm AGN1}$ are the most important parameters in determining the normalization.
}
    \label{fig:featimp_norm_low}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_StandardizedLinear_Normalization_alpha_low_31_20250423_182539.png}
    \caption{Standardized linear regression feature importance for the normalization of the black hole - stellar mass relation in the low stellar mass bin. Supernova feedback ($A_\mathrm{SN1}$) and AGN feedback ($A_\mathrm{AGN1}$) are the most important parameters.
}
    \label{fig:featimp_norm_linear_low}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/pdp_Scatter_low_35_20250423_182541.png}
    \caption{Partial dependence plot for the scatter in the $M_{\rm BH}$–$M_{\star}$ relation at low stellar mass ($M_{\star}<10^9\,M_\odot$). The scatter is most sensitive to $A_{\rm SN1}$, indicating that stronger SN feedback increases the scatter in black hole masses at a given stellar mass.
}
    \label{fig:pdp_scatter_low}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_StandardizedLinear_Scatter_low_34_20250423_182540.png}
    \caption{Standardized linear regression feature importance for the scatter in the $M_{\rm BH}$–$M_{\star}$ relation in the low stellar mass bin. The plot shows that $A_{\rm SN1}$ is the primary driver of increased scatter at low mass, which is consistent with the expectation that stochastic SN feedback introduces diversity in black hole growth histories.
}
    \label{fig:featimp_scatter_low}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/pdp_Normalization_alpha_low_32_20250423_182539.png}
    \caption{Partial dependence plots showing the variation of the black hole-stellar mass relation normalization with cosmological ($\Omega_m$, $\sigma_8$) and feedback ($A_\mathrm{SN1}$, $A_\mathrm{SN2}$, $A_\mathrm{AGN1}$, $A_\mathrm{AGN2}$) parameters in the low stellar mass bin. The normalization is most sensitive to $A_\mathrm{SN1}$ and $A_\mathrm{AGN1}$, indicating that supernova and AGN feedback are the primary drivers of diversity in the black hole-stellar mass relation at low mass.
}
    \label{fig:pdp_norm_low}
\end{figure}

\subsubsection{Intermediate-mass galaxies ($10^9 M_{\odot} \leq M_{\star} < 10^{10} M_{\odot}$)}

In the intermediate-mass bin, the slope ($\beta$) distribution has a mean of 1.06 and a standard deviation of 0.42, ranging from 0.02 to 1.84. The normalization ($\alpha$) has a mean of -3.53 with a standard deviation of 3.80, ranging from -10.6 to 6.05. The intrinsic scatter has a mean of 0.30 dex and a standard deviation of 0.06 dex. The mean black hole occupation fraction is 0.85, with a standard deviation of 0.08.

The slope is closer to unity, indicating a stronger correlation between black hole mass and stellar mass compared to the low-mass bin. The increased scatter suggests that other factors, such as galaxy merger history or AGN feedback, may play a more significant role in determining the black hole mass in this mass range. The higher occupation fraction indicates that most intermediate-mass galaxies host a detectable black hole.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/dist_beta_intermediate_42_20250423_182544.png}
    \caption{Histogram of the distribution of slopes ($\beta$) of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation for the intermediate mass bin ($10^9$–$10^{10}\,M_\odot$) across the 1,000 simulated galaxy catalogs. The diversity in slope highlights the sensitivity of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation to variations in feedback and cosmological parameters.
}
    \label{fig:dist_beta_intermediate}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/dist_alpha_intermediate_43_20250423_182545.png}
    \caption{Histogram of the normalization ($\alpha$) parameter of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation for the intermediate mass bin ($10^9$–$10^{10}\,M_\odot$) across the 1,000 simulated galaxy catalogs. The distribution reveals significant diversity in the normalization, indicating a strong sensitivity to feedback and cosmological parameters.
}
    \label{fig:dist_alpha_intermediate}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/dist_scatter_intermediate_44_20250423_182545.png}
    \caption{Histogram of the intrinsic scatter in the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation for the intermediate mass bin ($10^9-10^{10} M_\odot$) across the 1,000 simulated galaxy catalogs. The scatter varies significantly between simulations, reflecting the diverse effects of feedback and cosmological parameters on black hole and galaxy coevolution.
}
    \label{fig:dist_scatter_intermediate}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/pdp_Normalization_alpha_intermediate_74_20250423_182559.png}
    \caption{Partial dependence plot showing the influence of cosmological and feedback parameters on the normalization of the $M_{\rm BH}$–$M_{\star}$ relation in the intermediate mass bin. Strong AGN feedback (A\ensuremath{\_}AGN1) significantly decreases the normalization, while other parameters have weaker effects.
}
    \label{fig:pdp_norm_intermediate}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_StandardizedLinear_Slope_beta_intermediate_70_20250423_182558.png}
    \caption{Standardized linear regression feature importance for the slope of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation in the intermediate mass bin. The AGN feedback parameter ($A_\mathrm{AGN1}$) is the dominant factor influencing the slope.
}
    \label{fig:featimp_slope_linear_intermediate}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_RandomForest_Normalization_alpha_intermediate_72_20250423_182559.png}
    \caption{Random forest feature importance for the normalization of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation in the intermediate mass bin. The $A_\mathrm{AGN1}$ parameter dominates the normalization, indicating that AGN feedback is the primary driver in this mass range.
}
    \label{fig:featimp_norm_random_intermediate}
\end{figure}

\subsubsection{High-mass galaxies ($M_{\star} \geq 10^{10} M_{\odot}$)}

For high-mass galaxies, the slope ($\beta$) has a mean of 1.22 and a standard deviation of 0.30, ranging from 0.03 to 2.07. The normalization ($\alpha$) has a mean of -4.85 with a standard deviation of 3.39, ranging from -14.2 to 7.64. The intrinsic scatter has a mean of 0.40 dex and a standard deviation of 0.14 dex. The mean black hole occupation fraction is 0.96, with a standard deviation of 0.03.

The slope is close to unity, consistent with the canonical $M_{\rm BH}$--$M_{\star}$ relation. The large scatter suggests that the relationship between black hole mass and stellar mass is more complex in these massive galaxies, potentially due to AGN feedback or galaxy mergers. The occupation fraction is close to unity, indicating that nearly all high-mass galaxies host a detectable black hole.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/pdp_Normalization_alpha_high_116_20250423_182620.png}
    \caption{Partial dependence plots showing the influence of cosmological and feedback parameters on the normalization of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation for galaxies in the high mass bin ($M_\mathrm{star} > 10^{10} M_\odot$). The normalization exhibits a strong dependence on $A_\mathrm{AGN1}$, and weaker dependencies on other parameters, indicating that AGN feedback is a key driver of the relation's normalization at high mass.
}
    \label{fig:pdp_norm_high}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/pdp_Slope_beta_high_113_20250423_182618.png}
    \caption{Partial dependence plots showing the variation of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation slope ($\beta$) in the high mass bin as a function of cosmological ($\Omega_m$) and feedback ($A_\mathrm{SN1}$, $A_\mathrm{SN2}$, $A_\mathrm{AGN1}$, $A_\mathrm{AGN2}$) parameters. The slope exhibits a strong dependence on $A_\mathrm{AGN1}$, suggesting a key role for AGN feedback in regulating the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation at high stellar masses.
}
    \label{fig:pdp_slope_high}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_RandomForest_Normalization_alpha_high_114_20250423_182619.png}
    \caption{Random forest feature importance for the normalization of the $M_{\rm BH}$–$M_{\star}$ relation in the high mass bin ($M_{\star} > 10^{10} M_\odot$). The AGN feedback energy per accretion ($A_{\rm AGN1}$) is the dominant parameter.
}
    \label{fig:featimp_norm_high}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_RandomForest_Slope_beta_high_111_20250423_182617.png}
    \caption{Random forest feature importance for the slope of the black hole - stellar mass relation in the high mass bin ($M_\mathrm{star}>10^{10}\,M_\odot$). The AGN feedback parameter $A_\mathrm{AGN1}$ is the dominant factor, indicating that AGN feedback plays a crucial role in shaping the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation in massive galaxies.
}
    \label{fig:featimp_slope_random_high}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_StandardizedLinear_Scatter_high_118_20250423_182621.png}
    \caption{Standardized linear regression feature importance for the scatter in the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation at high stellar mass ($>10^{10}\,M_\odot$). The scatter is most sensitive to $A_\mathrm{AGN1}$ and $A_\mathrm{SN1}$, suggesting that both AGN and supernova feedback introduce diversity in black hole growth histories.
}
    \label{fig:featimp_scatter_linear_high}
\end{figure}

\subsection{Dependence on Feedback and Cosmological Parameters}

To quantify the influence of feedback and cosmological parameters on the $M_{\rm BH}$--$M_{\star}$ relation, we performed multivariate regression analysis.

\subsubsection{Low-mass galaxies}

In the low-mass regime, the slope ($\beta$) is most influenced by the supernova feedback parameter A\ensuremath{\_}{SN1} and AGN feedback parameter A\ensuremath{\_}{AGN1}. The standardized coefficient for A\ensuremath{\_}{SN1} is +0.05, and its random forest feature importance is 0.41. For A\ensuremath{\_}{AGN1}, the standardized coefficient is +0.04, and its random forest feature importance is 0.29. Both parameters positively correlate with the slope, suggesting that stronger feedback steepens the relation in low-mass galaxies. The normalization ($\alpha$) is strongly negatively correlated with A\ensuremath{\_}{SN1} (coefficient -0.38) and A\ensuremath{\_}{AGN1} (coefficient -0.32), indicating that stronger feedback leads to lower black hole masses at a fixed stellar mass. The intrinsic scatter is primarily driven by A\ensuremath{\_}{SN1} (coefficient +0.04, random forest importance 0.73), consistent with the expectation that stochastic supernova feedback introduces diversity in black hole growth histories.

\subsubsection{Intermediate-mass galaxies}

In the intermediate-mass regime, the slope ($\beta$) is dominated by the AGN feedback parameter A\ensuremath{\_}{AGN1} (coefficient +0.37, random forest importance 0.88). This suggests that AGN feedback plays a significant role in regulating black hole growth in intermediate-mass galaxies. The normalization ($\alpha$) is also strongly influenced by A\ensuremath{\_}{AGN1} (coefficient -3.32). The intrinsic scatter is influenced by both A\ensuremath{\_}{AGN1} and A\ensuremath{\_}{SN1}.

\subsubsection{High-mass galaxies}

In high-mass galaxies, the slope ($\beta$) is dominated by the AGN feedback parameter A\ensuremath{\_}{AGN1} (coefficient -0.22, random forest importance 0.69), but the sign of the coefficient is reversed compared to the intermediate-mass bin, indicating a shift in the role of AGN feedback. The normalization ($\alpha$) is also strongly influenced by A\ensuremath{\_}{AGN1} (coefficient +2.52). The intrinsic scatter is influenced by both A\ensuremath{\_}{AGN1} and A\ensuremath{\_}{SN1}.

\subsection{Black Hole Occupation Fraction}

The black hole occupation fraction increases with stellar mass, rising from approximately 0.72 in low-mass galaxies to nearly 0.96 in high-mass galaxies. The occupation fraction also depends on feedback parameters, with stronger supernova feedback (A\ensuremath{\_}{SN1}) reducing the occupation fraction at low and intermediate masses, consistent with the suppression of black hole formation or growth in shallow potential wells.

\subsection{Synthesis}

The results demonstrate that the diversity in the $M_{\rm BH}$--$M_{\star}$ relation is primarily driven by the strength and mode of feedback, with supernova feedback dominating at low mass and AGN feedback at high mass. Cosmological parameters also modulate the normalization and scatter, particularly in the intermediate and high mass bins. The black hole occupation fraction increases with stellar mass and is suppressed by supernova feedback at low mass. These findings highlight the importance of feedback physics in shaping the coevolution of black holes and galaxies, and provide a framework for interpreting the observed diversity in black hole scaling relations.

In summary, we find that supernova feedback plays a dominant role in regulating the $M_{\rm BH}$--$M_{\star}$ relation and black hole occupation fraction in low-mass galaxies, while AGN feedback becomes increasingly important in intermediate and high-mass galaxies. Cosmological parameters have a secondary but non-negligible influence on the normalization and scatter of the relation. These results emphasize the complex interplay of various physical processes in shaping the coevolution of black holes and galaxies.

\section{Conclusions}
\label{sec:conclusions}
This study addresses the open question of the universality of the black hole-stellar mass ($M_{\rm BH}$--$M_{\star}$) relation, a cornerstone of galaxy evolution. We systematically quantify how the slope, normalization, and scatter of this relation change in response to variations in cosmological parameters and feedback processes.

Using a suite of simulated galaxies, each representing a unique combination of cosmological and feedback parameters, we fit the $M_{\rm BH}$--$M_{\star}$ relation within different stellar mass ranges, focusing on galaxies hosting black holes. We employ multivariate regression and random forest analysis to map how the relation's parameters depend on the input cosmological and feedback parameters.

Our results demonstrate that feedback, particularly from supernovae in low-mass galaxies and active galactic nuclei in high-mass galaxies, is the dominant factor driving diversity in the $M_{\rm BH}$--$M_{\star}$ relation. Cosmological parameters influence the normalization and scatter, while the fraction of galaxies hosting black holes is sensitive to feedback, especially in low-mass systems. Specifically, in low-mass galaxies ($M_{\star} < 10^9 M_{\odot}$), the slope of the $M_{\rm BH}$--$M_{\star}$ relation is shallow, and supernova feedback significantly reduces the black hole occupation fraction. In intermediate-mass galaxies ($10^9 M_{\odot} \leq M_{\star} < 10^{10} M_{\odot}$), AGN feedback plays a crucial role in regulating black hole growth. In high-mass galaxies ($M_{\star} \geq 10^{10} M_{\odot}$), the $M_{\rm BH}$--$M_{\star}$ relation exhibits a larger scatter, and the black hole occupation fraction approaches unity.

This work provides a framework for understanding the observed diversity in black hole scaling relations and emphasizes the critical role of feedback in the coevolution of black holes and galaxies. We have learned that the $M_{\rm BH}$--$M_{\star}$ relation is not universal but is shaped by the complex interplay of feedback mechanisms and cosmological parameters. Supernova feedback is crucial in low-mass galaxies, while AGN feedback dominates in high-mass galaxies. The black hole occupation fraction is also sensitive to feedback, particularly in low-mass systems. These findings highlight the importance of considering these factors when studying the coevolution of black holes and galaxies.

\bibliography{bibliography}{}
\bibliographystyle{aasjournal}

\end{document}

### 2025-05-02 Project5/paper_v1.tex
fix: Fix LaTeX compilation errors in paper_v1.tex

@@
 \usepackage{amsmath}
+\usepackage{graphicx}
 \usepackage{multirow}
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/dist_alpha_low_1_20250423_182517.png}
-    \caption{Distribution of the normalization parameter $\alpha$ of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation in the low stellar mass bin ($M_\mathrm{star}<10^9\,M_\odot$) across 1,000 simulated galaxy catalogs, showing the diversity in the relation.
+    \includegraphics[width=0.5\textwidth]{plots/dist_alpha_low_1_20250423_182517.png}
+    \caption{Distribution of the normalization parameter $\alpha$ of the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation in the low stellar mass bin ($M_\mathrm{star}<10^9\,M_\odot$) across 1,000 simulated galaxy catalogs, showing the diversity in the relation.
 }
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/dist_scatter_low_2_20250423_182518.png}
-    \caption{Histogram of the intrinsic scatter in the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation for the low stellar mass bin ($M_\mathrm{star}<10^9\,M_\odot$) across 1,000 simulated galaxy catalogs.
+    \includegraphics[width=0.5\textwidth]{plots/dist_scatter_low_2_20250423_182518.png}
+    \caption{Histogram of the intrinsic scatter in the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation for the low stellar mass bin ($M_\mathrm{star}<10^9\,M_\odot$) across 1,000 simulated galaxy catalogs.
 The distribution reveals a range of scatter values, reflecting the diversity driven by varying feedback and cosmological parameters.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/pdp_Slope_beta_low_29_20250423_182536.png}
-    \caption{Partial dependence plots showing the effect of varying cosmological ($\Omega_m$, $\sigma_8$) and feedback ($A_{\rm SN1}$, $A_{\rm SN2}$, $A_{\rm AGN1}$, $A_{\rm AGN2}$) parameters on the slope of the $M_{\rm BH}$–$M_{\star}$ relation in the low stellar mass bin.
-The slope is most sensitive to $A_{\rm SN1}$ and $A_{\rm AGN1}$, indicating the importance of feedback in this regime.
+    \includegraphics[width=0.5\textwidth]{plots/pdp_Slope_beta_low_29_20250423_182536.png}
+    \caption{Partial dependence plots showing the effect of varying cosmological ($\Omega_m$, $\sigma_8$) and feedback ($A_\mathrm{SN1}$, $A_\mathrm{SN2}$, $A_\mathrm{AGN1}$, $A_\mathrm{AGN2}$) parameters on the slope of the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation in the low stellar mass bin.
+The slope is most sensitive to $A_\mathrm{SN1}$ and $A_\mathrm{AGN1}$, indicating the importance of feedback in this regime.
 }
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_RandomForest_Slope_beta_low_27_20250423_182532.png}
-    \caption{Random forest feature importance for the slope of the black hole stellar mass relation in the low mass bin.
+    \includegraphics[width=0.5\textwidth]{plots/featimp_RandomForest_Slope_beta_low_27_20250423_182532.png}
+    \caption{Random forest feature importance for the slope of the black hole--stellar mass relation in the low mass bin.
 The most influential parameters are $A_\mathrm{SN1}$ and $A_\mathrm{AGN1}$, indicating that stronger feedback steepens the relation at low mass.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_RandomForest_Scatter_low_33_20250423_182540.png}
-    \caption{Random forest feature importance for the scatter in the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation in the low mass bin.
+    \includegraphics[width=0.5\textwidth]{plots/featimp_RandomForest_Scatter_low_33_20250423_182540.png}
+    \caption{Random forest feature importance for the scatter in the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation in the low mass bin.
 Supernova feedback ($A_\mathrm{SN1}$) is the primary driver of increased scatter.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_RandomForest_Normalization_alpha_low_30_20250423_182538.png}
-    \caption{Random forest feature importance for the normalization of the $M_{\rm BH}$–$M_{\star}$ relation ($\alpha$) in the low mass bin ($M_{\star}<10^9\,M_\odot$).
-The bar plot indicates that $A_{\rm SN1}$ and $A_{\rm AGN1}$ are the most important parameters in determining the normalization.
+    \includegraphics[width=0.5\textwidth]{plots/featimp_RandomForest_Normalization_alpha_low_30_20250423_182538.png}
+    \caption{Random forest feature importance for the normalization of the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation ($\alpha$) in the low mass bin ($M_\mathrm{star}<10^9\,M_\odot$).
+The bar plot indicates that $A_\mathrm{SN1}$ and $A_\mathrm{AGN1}$ are the most important parameters in determining the normalization.
 }
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_StandardizedLinear_Normalization_alpha_low_31_20250423_182539.png}
-    \caption{Standardized linear regression feature importance for the normalization of the black hole - stellar mass relation in the low stellar mass bin.
+    \includegraphics[width=0.5\textwidth]{plots/featimp_StandardizedLinear_Normalization_alpha_low_31_20250423_182539.png}
+    \caption{Standardized linear regression feature importance for the normalization of the black hole--stellar mass relation in the low stellar mass bin.
 Supernova feedback ($A_\mathrm{SN1}$) and AGN feedback ($A_\mathrm{AGN1}$) are the most important parameters.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/pdp_Scatter_low_35_20250423_182541.png}
-    \caption{Partial dependence plot for the scatter in the $M_{\rm BH}$–$M_{\star}$ relation at low stellar mass ($M_{\star}<10^9\,M_\odot$).
-The scatter is most sensitive to $A_{\rm SN1}$, indicating that stronger SN feedback increases the scatter in black hole masses at a given stellar mass.
+    \includegraphics[width=0.5\textwidth]{plots/pdp_Scatter_low_35_20250423_182541.png}
+    \caption{Partial dependence plot for the scatter in the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation at low stellar mass ($M_\mathrm{star}<10^9\,M_\odot$).
+The scatter is most sensitive to $A_\mathrm{SN1}$, indicating that stronger SN feedback increases the scatter in black hole masses at a given stellar mass.
 }
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_StandardizedLinear_Scatter_low_34_20250423_182540.png}
-    \caption{Standardized linear regression feature importance for the scatter in the $M_{\rm BH}$–$M_{\star}$ relation in the low stellar mass bin.
-The plot shows that $A_{\rm SN1}$ is the primary driver of increased scatter at low mass, which is consistent with the expectation that stochastic SN feedback introduces diversity in black hole growth histories.
+    \includegraphics[width=0.5\textwidth]{plots/featimp_StandardizedLinear_Scatter_low_34_20250423_182540.png}
+    \caption{Standardized linear regression feature importance for the scatter in the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation in the low stellar mass bin.
+The plot shows that $A_\mathrm{SN1}$ is the primary driver of increased scatter at low mass, which is consistent with the expectation that stochastic SN feedback introduces diversity in black hole growth histories.
 }
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/pdp_Normalization_alpha_low_32_20250423_182539.png}
-    \caption{Partial dependence plots showing the variation of the black hole-stellar mass relation normalization with cosmological ($\Omega_m$, $\sigma_8$) and feedback ($A_\mathrm{SN1}$, $A_\mathrm{SN2}$, $A_\mathrm{AGN1}$, $A_\mathrm{AGN2}$) parameters in the low stellar mass bin.
-The normalization is most sensitive to $A_\mathrm{SN1}$ and $A_\mathrm{AGN1}$, indicating that supernova and AGN feedback are the primary drivers of diversity in the black hole-stellar mass relation at low mass.
+    \includegraphics[width=0.5\textwidth]{plots/pdp_Normalization_alpha_low_32_20250423_182539.png}
+    \caption{Partial dependence plots showing the variation of the black hole--stellar mass relation normalization with cosmological ($\Omega_m$, $\sigma_8$) and feedback ($A_\mathrm{SN1}$, $A_\mathrm{SN2}$, $A_\mathrm{AGN1}$, $A_\mathrm{AGN2}$) parameters in the low stellar mass bin.
+The normalization is most sensitive to $A_\mathrm{SN1}$ and $A_\mathrm{AGN1}$, indicating that supernova and AGN feedback are the primary drivers of diversity in the black hole--stellar mass relation at low mass.
 }
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/dist_beta_intermediate_42_20250423_182544.png}
-    \caption{Histogram of the distribution of slopes ($\beta$) of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation for the intermediate mass bin ($10^9$–$10^{10}\,M_\odot$) across the 1,000 simulated galaxy catalogs.
-The diversity in slope highlights the sensitivity of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation to variations in feedback and cosmological parameters.
+    \includegraphics[width=0.5\textwidth]{plots/dist_beta_intermediate_42_20250423_182544.png}
+    \caption{Histogram of the distribution of slopes ($\beta$) of the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation for the intermediate mass bin ($10^9$--$10^{10}\,M_\odot$) across the 1,000 simulated galaxy catalogs.
+The diversity in slope highlights the sensitivity of the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation to variations in feedback and cosmological parameters.
 }
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/dist_alpha_intermediate_43_20250423_182545.png}
-    \caption{Histogram of the normalization ($\alpha$) parameter of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation for the intermediate mass bin ($10^9$–$10^{10}\,M_\odot$) across the 1,000 simulated galaxy catalogs.
+    \includegraphics[width=0.5\textwidth]{plots/dist_alpha_intermediate_43_20250423_182545.png}
+    \caption{Histogram of the normalization ($\alpha$) parameter of the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation for the intermediate mass bin ($10^9$--$10^{10}\,M_\odot$) across the 1,000 simulated galaxy catalogs.
 The distribution reveals significant diversity in the normalization, indicating a strong sensitivity to feedback and cosmological parameters.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/dist_scatter_intermediate_44_20250423_182545.png}
-    \caption{Histogram of the intrinsic scatter in the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation for the intermediate mass bin ($10^9-10^{10} M_\odot$) across the 1,000 simulated galaxy catalogs.
+    \includegraphics[width=0.5\textwidth]{plots/dist_scatter_intermediate_44_20250423_182545.png}
+    \caption{Histogram of the intrinsic scatter in the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation for the intermediate mass bin ($10^9$--$10^{10} M_\odot$) across the 1,000 simulated galaxy catalogs.
 The scatter varies significantly between simulations, reflecting the diverse effects of feedback and cosmological parameters on black hole and galaxy coevolution.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/pdp_Normalization_alpha_intermediate_74_20250423_182559.png}
-    \caption{Partial dependence plot showing the influence of cosmological and feedback parameters on the normalization of the $M_{\rm BH}$–$M_{\star}$ relation in the intermediate mass bin.
-Strong AGN feedback (A\ensuremath{\_}AGN1) significantly decreases the normalization, while other parameters have weaker effects.
+    \includegraphics[width=0.5\textwidth]{plots/pdp_Normalization_alpha_intermediate_74_20250423_182559.png}
+    \caption{Partial dependence plot showing the influence of cosmological and feedback parameters on the normalization of the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation in the intermediate mass bin.
+Strong AGN feedback ($A_\mathrm{AGN1}$) significantly decreases the normalization, while other parameters have weaker effects.
 }
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_StandardizedLinear_Slope_beta_intermediate_70_20250423_182558.png}
-    \caption{Standardized linear regression feature importance for the slope of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation in the intermediate mass bin.
+    \includegraphics[width=0.5\textwidth]{plots/featimp_StandardizedLinear_Slope_beta_intermediate_70_20250423_182558.png}
+    \caption{Standardized linear regression feature importance for the slope of the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation in the intermediate mass bin.
 The AGN feedback parameter ($A_\mathrm{AGN1}$) is the dominant factor influencing the slope.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_RandomForest_Normalization_alpha_intermediate_72_20250423_182559.png}
-    \caption{Random forest feature importance for the normalization of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation in the intermediate mass bin.
+    \includegraphics[width=0.5\textwidth]{plots/featimp_RandomForest_Normalization_alpha_intermediate_72_20250423_182559.png}
+    \caption{Random forest feature importance for the normalization of the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation in the intermediate mass bin.
 The $A_\mathrm{AGN1}$ parameter dominates the normalization, indicating that AGN feedback is the primary driver in this mass range.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/pdp_Normalization_alpha_high_116_20250423_182620.png}
-    \caption{Partial dependence plots showing the influence of cosmological and feedback parameters on the normalization of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation for galaxies in the high mass bin ($M_\mathrm{star} > 10^{10} M_\odot$).
+    \includegraphics[width=0.5\textwidth]{plots/pdp_Normalization_alpha_high_116_20250423_182620.png}
+    \caption{Partial dependence plots showing the influence of cosmological and feedback parameters on the normalization of the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation for galaxies in the high mass bin ($M_\mathrm{star} > 10^{10} M_\odot$).
 The normalization exhibits a strong dependence on $A_\mathrm{AGN1}$, and weaker dependencies on other parameters, indicating that AGN feedback is a key driver of the relation's normalization at high mass.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/pdp_Slope_beta_high_113_20250423_182618.png}
-    \caption{Partial dependence plots showing the variation of the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation slope ($\beta$) in the high mass bin as a function of cosmological ($\Omega_m$) and feedback ($A_\mathrm{SN1}$, $A_\mathrm{SN2}$, $A_\mathrm{AGN1}$, $A_\mathrm{AGN2}$) parameters.
-The slope exhibits a strong dependence on $A_\mathrm{AGN1}$, suggesting a key role for AGN feedback in regulating the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation at high stellar masses.
+    \includegraphics[width=0.5\textwidth]{plots/pdp_Slope_beta_high_113_20250423_182618.png}
+    \caption{Partial dependence plots showing the variation of the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation slope ($\beta$) in the high mass bin as a function of cosmological ($\Omega_m$) and feedback ($A_\mathrm{SN1}$, $A_\mathrm{SN2}$, $A_\mathrm{AGN1}$, $A_\mathrm{AGN2}$) parameters.
+The slope exhibits a strong dependence on $A_\mathrm{AGN1}$, suggesting a key role for AGN feedback in regulating the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation at high stellar masses.
 }
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_RandomForest_Normalization_alpha_high_114_20250423_182619.png}
-    \caption{Random forest feature importance for the normalization of the $M_{\rm BH}$–$M_{\star}$ relation in the high mass bin ($M_{\star} > 10^{10} M_\odot$).
-The AGN feedback energy per accretion ($A_{\rm AGN1}$) is the dominant parameter.
+    \includegraphics[width=0.5\textwidth]{plots/featimp_RandomForest_Normalization_alpha_high_114_20250423_182619.png}
+    \caption{Random forest feature importance for the normalization of the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation in the high mass bin ($M_\mathrm{star} > 10^{10} M_\odot$).
+The AGN feedback energy per accretion ($A_\mathrm{AGN1}$) is the dominant parameter.
 }
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_RandomForest_Slope_beta_high_111_20250423_182617.png}
-    \caption{Random forest feature importance for the slope of the black hole - stellar mass relation in the high mass bin ($M_\mathrm{star}>10^{10}\,M_\odot$).
-The AGN feedback parameter $A_\mathrm{AGN1}$ is the dominant factor, indicating that AGN feedback plays a crucial role in shaping the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation in massive galaxies.
+    \includegraphics[width=0.5\textwidth]{plots/featimp_RandomForest_Slope_beta_high_111_20250423_182617.png}
+    \caption{Random forest feature importance for the slope of the black hole--stellar mass relation in the high mass bin ($M_\mathrm{star}>10^{10}\,M_\odot$).
+The AGN feedback parameter $A_\mathrm{AGN1}$ is the dominant factor, indicating that AGN feedback plays a crucial role in shaping the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation in massive galaxies.
 }
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Project5/plots/featimp_StandardizedLinear_Scatter_high_118_20250423_182621.png}
-    \caption{Standardized linear regression feature importance for the scatter in the $M_\mathrm{BH}$–$M_\mathrm{star}$ relation at high stellar mass ($>10^{10}\,M_\odot$).
+    \includegraphics[width=0.5\textwidth]{plots/featimp_StandardizedLinear_Scatter_high_118_20250423_182621.png}
+    \caption{Standardized linear regression feature importance for the scatter in the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation at high stellar mass ($>10^{10}\,M_\odot$).
 The scatter is most sensitive to $A_\mathrm{AGN1}$ and $A_\mathrm{SN1}$, suggesting that both AGN and supernova feedback introduce diversity in black hole growth histories.

### 2025-05-02 astropilot/astro_pilot.py
update with all files stored in project folder

@@ -20,12 +20,38 @@ import shutil
 class AstroPilot:
 
 
-    def __init__(self, input_data: 'AstroPilot.Research' = None, params={}, repo_dir: str = repo_dir_default):
+    def __init__(self, input_data: 'AstroPilot.Research' = None, params={}, project_dir: str = repo_dir_default, clear_project_dir: bool = True):
         if input_data is None:
             input_data = AstroPilot.Research()  # Initialize with default values
+        self.clear_project_dir = clear_project_dir
         self.research = input_data
         self.params = params
-        self.repo_dir = repo_dir    
+        if project_dir != repo_dir_default:
+            # Create directory if it doesn't exist, or clear it if it does
+            new_dir = os.path.join(repo_dir_default, os.path.basename(project_dir))
+            if os.path.exists(new_dir):
+                if clear_project_dir:
+                    shutil.rmtree(new_dir)
+                else:
+                    pass
+            os.makedirs(new_dir, exist_ok=True)
+            self.project_dir = new_dir 
+        else:
+            self.project_dir = project_dir
+
+        self._setup_input_files()
+
+    def _setup_input_files(self):
+        input_files_dir = os.path.join(self.project_dir, 'input_files')
+        
+        # If directory exists, remove it and all its contents
+        if os.path.exists(input_files_dir) and self.clear_project_dir:
+            shutil.rmtree(input_files_dir)
+            
+        # Create fresh input_files directory
+        os.makedirs(input_files_dir, exist_ok=True)
+
+
 
     class Research(BaseModel):
         data_description: str = Field(default="", description="The data description of the project")
@@ -38,9 +64,9 @@ class AstroPilot:
 
     def set_data_description(self, data_description: str = None, **kwargs):
         if data_description is None:
-            with open(os.path.join(self.repo_dir, 'input_files', 'data_description.md'), 'r') as f:
+            with open(os.path.join(self.project_dir, 'input_files', 'data_description.md'), 'r') as f:
                 data_description = f.read()
-            data_description = data_description.replace("{path_to_project_data}", str(self.repo_dir)+ "/project_data/")
+            data_description = data_description.replace("{path_to_project_data}", str(self.project_dir)+ "/project_data/")
 
         elif data_description.endswith(".md"):
             with open(data_description, 'r') as f:
@@ -55,7 +81,7 @@ class AstroPilot:
 
[…]

### 2025-05-02 astropilot/idea.py

@@ -2,14 +2,21 @@
 import cmbagent
 import copy
 import re
+import os
 
 
 class Idea:
     """
     This class is used to develop a research project idea based on the data of interest.
     """
+    def __init__(self, work_dir = None):
+        if work_dir is None:
+            raise ValueError("workdir must be provided")
+        
+        self.idea_dir = os.path.join(work_dir, "idea_generation_output")
+        # Create directory if it doesn't exist
+        os.makedirs(self.idea_dir, exist_ok=True)
 
-    def __init__(self):
         self.planner_append_instructions = r"""
 Given these datasets, and information, make a plan according to the following instructions: 
 
@@ -59,7 +66,8 @@ Don't suggest to perform any calculations or analyses here. The only goal of thi
                               max_n_attempts = 4,
                               max_plan_steps = 6,
                               engineer_model = "gpt-4.1-2025-04-14",
-                              plan_instructions=self.planner_append_instructions
+                              plan_instructions=self.planner_append_instructions,
+                              work_dir = self.idea_dir
                              )
 
         chat_history = results['chat_history']

### 2025-05-02 astropilot/experiment.py
update with all files stored in project folder

@@ -5,9 +5,19 @@ import copy
 import os
 import re
 class Experiment:
+    """
+    This class is used to perform the experiment.
+    """
+
+    def __init__(self, research_idea: str, methodology: str, involved_agents: List[str] = ['engineer', 'researcher'], work_dir = None):
+        if work_dir is None:
+            raise ValueError("workdir must be provided")
+
+        self.experiment_dir = os.path.join(work_dir, "experiment_generation_output")
+        # Create directory if it doesn't exist
+        os.makedirs(self.experiment_dir, exist_ok=True)
 
 
-    def __init__(self, research_idea: str, methodology: str, involved_agents: List[str] = ['engineer', 'researcher']):
         involved_agents_str = ', '.join(involved_agents)
 
         self.planner_append_instructions = rf"""
@@ -131,7 +141,8 @@ class Experiment:
                             researcher_model = "gpt-4.1-2025-04-14",
                             plan_instructions=self.planner_append_instructions,
                             researcher_instructions=self.researcher_append_instructions,
-                            engineer_instructions=self.engineer_append_instructions
+                            engineer_instructions=self.engineer_append_instructions,
+                            work_dir = self.experiment_dir
                             )
         chat_history = results['chat_history']
         final_context = results['final_context']

### 2025-05-02 astropilot/method.py

@@ -9,12 +9,19 @@ class Method:
     This class is used to develop a research project methodology based on the data of interest and the project idea.
     """
 
-    def __init__(self, research_idea: str):
+    def __init__(self, research_idea: str, work_dir = None):
+
+        if work_dir is None:
+            raise ValueError("workdir must be provided")
+
+        self.method_dir = os.path.join(work_dir, "method_generation_output")
+        # Create directory if it doesn't exist
+        os.makedirs(self.method_dir, exist_ok=True)
         self.planner_append_instructions = rf"""
 
         {research_idea}
 
-        Instruction for planning:
+Instruction for planning:
 
 Given these datasets, and information on the features and project idea, we want to design a methodology to implement this idea.
 The goal of the task is to write a plan that will be used to generate a detailed description of the methodology that will be used to perform the research project.
@@ -22,23 +29,23 @@ The goal of the task is to write a plan that will be used to generate a detailed
 **Elicit Project-Specific Reasoning:**
    - Ask the *researcher* to provide reasoning  relevant to the given project idea.
    - Clarify the specific hypotheses, assumptions, or questions that should be investigated.
+   - This can be done in multiple steps. 
 
 
 **MOST IMPORTANT: Write the Methodology description:**
    - With the *researcher*, write a **detailed description (approximately 500 words)** describing the methodology that will be used to perform the project analysis.
    - The description should clearly outline the steps, techniques, and rationale derived from the exploratory data analysis.
-   - Include relevant results from the EDA in the form of key statistics or tables (do not include references to plots, or generated files here).
+   - If EDA was performed, include relevant results from the EDA in the form of key statistics or tables (do not include references to plots, or generated files here).
    - The focus should be strictly on the methods and workflow for this specific project to be performed. **do not include** any discussion of future directions, future work, project extensions, or limitations.
    - The description should be written as if it were a senior researcher explaining to her research assistant how to perform the research necessary for this project.
 
+The plan must end with the Methodology description generated by the researcher. The final step of the plan must be such that the FULL Methodology description is provided (as a result of the previous steps).
 
-    The plan must end with the Methodology description generated by the researcher. 
+The only agent involved in this workflow is the researcher.
 
-    The only agent involved in this workflow is the researcher.
+In this task we do not perform any calculations or analyses, only outline the methodology. 
 
-    In this task we do not perform any calculations or analyses, only outline the methodology. 
-
-    The methodology should focus on describing the research and analysis that will be performed.
[…]

### 2025-05-02 src/latex.py
update

@@ -23,22 +23,18 @@ special_chars = {
 
 def compile_latex(state: GraphState, paper_name: str, verbose=True):
 
-    # get the current directory
-    original_dir = os.getcwd()
-
-    # go to the folder containing the paper
-    os.chdir(state['files']['Folder'])
-
     # get the paper stem
     paper_stem = Path(paper_name).stem
 
     def run_xelatex():
         return subprocess.run(["xelatex", paper_name],
+                              cwd=state['files']['Folder'],
                               input="\n", capture_output=True,
                               text=True, check=True)
 
     def run_bibtex():
         subprocess.run(["bibtex", paper_stem],
+                       cwd=state['files']['Folder'],
                        capture_output=True, text=True, check=True)
 
     def log_output(i, result_or_error, is_error=False):
@@ -64,22 +60,7 @@ def compile_latex(state: GraphState, paper_name: str, verbose=True):
         section = state['latex']['section']
         fixed_text = fix_latex_bug(state, state['paper'][section], error_msg)
         state['paper'][section] = fixed_text
-        os.chdir(original_dir)
         save_paper(state, paper_name)
-        os.chdir(state['files']['Folder'])
-
-    def compile_successfully(label):
-        try:
-            result = run_xelatex()
-            log_output(label, result)
-            if verbose:
-                print(f"    LaTeX compiled successfully: {label}")
-            return True
-        except subprocess.CalledProcessError as e:
-            log_output(label, e, is_error=True)
-            if verbose:
-                print(f"    LaTeX failed: {label}")
-            return e
 
     # --- Retry loop ---
     #for attempt in range(3):
@@ -93,25 +74,28 @@ def compile_latex(state: GraphState, paper_name: str, verbose=True):
     #    os.chdir(original_dir)
     #    raise RuntimeError("LaTeX failed after 3 attempts")
 
+    # Try to compile it the first time
+    try:
+        result = run_xelatex()
+        if verbose:
+            print(f"    LaTeX compiled successfully: Pass 1")
+    except subprocess.CalledProcessError as e:
+        log_output("Pass 1", e, is_error=True)
+        print(f"LaTeX failed on pass 1")
 
-    for i in range(4):
+    # if there is bibliography, compile it
+    if os.path.exists("bibliography.bib"):
+        run_bibtex()
 
-        if i==1:
-            if os.path.exists("bibliography.bib"):
-                run_bibtex()
-            continue
-        
[…]

### 2025-05-02 src/reader.py

@@ -25,17 +25,14 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
     """
 
     # set the LLM
-    if state['llm']['model']=='gemini-2.0-flash':
-        state['llm']['llm'] = ChatGoogleGenerativeAI(model="gemini-2.0-flash", temperature=0.7,
-                                                     max_output_tokens=8192,
-                                                     google_api_key=GOOGLE_API_KEY)
-        state['llm']['max_output_tokens'] = 8192
-    elif state['llm']['model']=='gemini-2.5-flash-preview-04-17':
-        state['llm']['llm'] = ChatGoogleGenerativeAI(model="gemini-2.5-flash-preview-04-17",
+    if 'gemini' in state['llm']['model']:
+        state['llm']['llm'] = ChatGoogleGenerativeAI(model=state['llm']['model'],
                                                      temperature=0.7,
                                                      google_api_key=GOOGLE_API_KEY)
-        state['llm']['max_output_tokens'] = 65536
-        
+        if 'gemini-2.0' in state['llm']['model']:
+            state['llm']['max_output_tokens'] = 8192
+        if 'gemini-2.5' in state['llm']['model']:
+            state['llm']['max_output_tokens'] = 65536
     
     # set the tokens usage
     state['tokens'] = {}
@@ -51,7 +48,7 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
                       "Paper_v3":  "paper_v3.tex",
                       "Paper_v4":  "paper_v4.tex",
                       "Error":     "Error.txt",
-                      "LaTeX_log": "LaTeX_compilation.log",
+                      "LaTeX_log": f"{state['files']['Folder']}/LaTeX_compilation.log",
                       "Temp":      f"{state['files']['Folder']}/Temp",
                       "LLM_calls": f"{state['files']['Folder']}/LLM_calls.txt"}
 
@@ -87,14 +84,9 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
 
     for f_in in [state['files']['Error'], state['files']['LLM_calls']]:
         if os.path.exists(f_in):  os.remove(f"{f_in}")
-
-    # create empty file
-    #open(state['files']['LLM_calls'], 'w').close()
         
-
     # remove LaTeX compilation log file
-    f_in = f"{state['files']['Folder']}/{state['files']['LaTeX_log']}"
[…]

### 2025-05-02 main.py
update

@@ -13,13 +13,14 @@ graph = build_graph(mermaid_diagram=True)
 
 # run the graph
 result = asyncio.run(graph.ainvoke(
-    {"files":{"Folder":       "Project5",   #name of folder containing input files
+    {"files":{"Folder":       "Project7",   #name of folder containing input files
               "Idea":         "idea.md",    #name of file containing idea description
               "Methods":      "methods.md", #name of file with methods description
               "Results":      "results.md", #name of file with results description
               "Plots":        "plots"},     #name of folder containing plots
-     #"llm": {"model": "gemini-2.0-flash"},  #name of the LLM model to use
-     "llm": {"model": "gemini-2.5-flash-preview-04-17"},  #name of the LLM model to use
+     "llm": {"model": "gemini-2.0-flash"},  #name of the LLM model to use
+     #"llm": {"model": "gemini-2.5-flash-preview-04-17"},  #name of the LLM model to use
+     #"llm": {"model": "gemini-2.5-pro-preview-03-25"},  #name of the LLM model to use
      }, config))
 
 # End timer and report duration in minutes and seconds

### 2025-05-02 src/paper_node.py

@@ -60,13 +60,13 @@ def abstract_node(state: GraphState, config: RunnableConfig):
         state['paper']['Title'] = temp_file(f_temp2, 'read')
 
     else:
-        for i in range(3):
+        for i in range(3): #sometimes it fails. Allow it to try up to 3 times
             PROMPT = abstract_prompt(state)
             state, result = LLM_call(PROMPT, state)
 
             try:
                 parsed_json = json_parser(result)
-                state['paper']['Title'] = parsed_json["Title"]
+                state['paper']['Title']    = parsed_json["Title"]
                 state['paper']['Abstract'] = parsed_json["Abstract"]
                 break  # success
             except Exception as e:
@@ -74,9 +74,8 @@ def abstract_node(state: GraphState, config: RunnableConfig):
                 time.sleep(2)
         else:
             raise RuntimeError("LLM failed to produce valid JSON after 3 attempts.")
-
     
-        # several self-reflection rounds
+        # perform several self-reflection rounds
         for i in range(1):
 
             # improve abstract

### 2025-05-03 installer.sh
added python3

@@ -38,8 +38,14 @@ clone_repo() {
 }
 
 # Create a Python 3 virtual environment named 'astrop_env'
+if ! command -v python3 &> /dev/null; then
+    echo "Error: python3 not found. Please install Python 3" >&2
+    exit 1
+fi
+
 echo "Creating Python virtual environment..."
-python3.12 -m venv astrop_env
+python3 -m venv astrop_env
+
 
 # Activate the virtual environment
 echo "Activating virtual environment..."

### 2025-05-03 Project5/paper_v1.tex

@@
 \keywords{Black holes, Supermassive black holes, Galaxies, Galaxy evolution, Cosmology, Cosmological parameters, Galaxy clusters, Active galactic nuclei, Feedback, N-body simulations, Gravitational lensing, Galaxy mergers, Galaxy physics, High energy astrophysics, Intergalactic medium}
+% Note: Keywords often don't need escaping within \keywords{} depending on the class, but it's safer.
+Let's assume no change needed here for now based on common practice with aastex.
+If errors persist related to keywords, we can revisit.
+The main issue is likely the \ensuremath usage.
+Let's focus on that first.
 
@@
 The cosmological parameters considered are the matter density ($\Omega_m$) and the amplitude of the matter power spectrum ($\sigma_8$).
-The feedback parameters control the efficiency of supernova feedback (A\ensuremath{\_}{SN1}, A\ensuremath{\_}{SN2}) and active galactic nuclei feedback (A\ensuremath{\_}{AGN1}, A\ensuremath{\_}{AGN2}).
+The feedback parameters control the efficiency of supernova feedback ($A_\mathrm{SN1}$, $A_\mathrm{SN2}$) and active galactic nuclei feedback ($A_\mathrm{AGN1}$, $A_\mathrm{AGN2}$).
 These parameters are systematically varied across the simulation suite, allowing us to explore a wide range of possible galaxy evolution scenarios.
@@
     \item Catalog number
-    \item Values of the feedback parameters (A\ensuremath{\_}{SN1}, A\ensuremath{\_}{SN2}, A\ensuremath{\_}{AGN1}, A\ensuremath{\_}{AGN2})
+    \item Values of the feedback parameters ($A_\mathrm{SN1}$, $A_\mathrm{SN2}$, $A_\mathrm{AGN1}$, $A_\mathrm{AGN2}$)
     \item Values of the cosmological parameters ($\Omega_m$, $\sigma_8$)
-    \item Slope ($\beta$) of the $M_{\rm BH}$--$M_{\star}$ relation in each mass bin
-    \item Normalization ($\alpha$) of the $M_{\rm BH}$--$M_{\star}$ relation in each mass bin
+    \item Slope ($\beta$) of the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation in each mass bin
+    \item Normalization ($\alpha$) of the $M_\mathrm{BH}$--$M_\mathrm{star}$ relation in each mass bin
     \item Intrinsic scatter of the $M_{\rm BH}$--$M_{\star}$ relation in each mass bin
@@
 \label{sec:results}
-This section presents the results of our investigation into the diversity of the black hole-stellar mass ($M_{\rm BH}$--$M_{\star}$) relation across a broad range of cosmological and feedback parameter space.
-We leverage a suite of simulated galaxy catalogs, each characterized by a unique combination of cosmological parameters ($\Omega_m$, $\sigma_8$) and feedback parameters (A\ensuremath{\_}{SN1}, A\ensuremath{\_}{SN2}, A\ensuremath{\_}{AGN1}, A\ensuremath{\_}{AGN2}), enabling a systematic exploration of how the scaling relation's slope, normalization, and scatter respond to changes in the underlying physics.
-The methodology involves fitting the relation $\log_{10} M_{\rm BH} = \alpha + \beta \log_{10} M_{\star}$ within three stellar mass bins (low: $M_{\star} < 10^9 M_{\odot}$, intermediate: $10^9 M_{\odot} \leq M_{\star} < 10^{10} M_{\odot}$, high: $M_{\star} \geq 10^{10} M_{\odot}$) for each catalog, excluding galaxies with $M_{\rm BH} = 0$ to focus on the scaling among black hole hosts.
+This section presents the results of our investigation into the diversity of the black hole-stellar mass ($M_\mathrm{BH}$--$M_\mathrm{star}$) relation across a broad range of cosmological and feedback parameter space.
+We leverage a suite of simulated galaxy catalogs, each characterized by a unique combination of cosmological parameters ($\Omega_m$, $\sigma_8$) and feedback parameters ($A_\mathrm{SN1}$, $A_\mathrm{SN2}$, $A_\mathrm{AGN1}$, $A_\mathrm{AGN2}$), enabling a systematic exploration of how the scaling relation's slope, normalization, and scatter respond to changes in the underlying physics.
+The methodology involves fitting the relation $\log_{10} M_\mathrm{BH} = \alpha + \beta \log_{10} M_\mathrm{star}$ within three stellar mass bins (low: $M_\mathrm{star} < 10^9 M_{\odot}$, intermediate: $10^9 M_{\odot} \leq M_\mathrm{star} < 10^{10} M_{\odot}$, high: $M_\mathrm{star} \geq 10^{10} M_{\odot}$) for each catalog, excluding galaxies with $M_\mathrm{BH} = 0$ to focus on the scaling among black hole hosts.
 The resulting best-fit parameters (slope $\beta$, normalization $\alpha$, and intrinsic scatter) are then mapped as functions of the six catalog parameters using multivariate regression and random forest analysis.
@@
 
-In the low-mass regime, the slope ($\beta$) is most influenced by the supernova feedback parameter A\ensuremath{\_}{SN1} and AGN feedback parameter A\ensuremath{\_}{AGN1}.
-The standardized coefficient for A\ensuremath{\_}{SN1} is +0.05, and its random forest feature importance is 0.41.
-For A\ensuremath{\_}{AGN1}, the standardized coefficient is +0.04, and its random forest feature importance is 0.29.
+In the low-mass regime, the slope ($\beta$) is most influenced by the supernova feedback parameter $A_\mathrm{SN1}$ and AGN feedback parameter $A_\mathrm{AGN1}$.
+The standardized coefficient for $A_\mathrm{SN1}$ is +0.05, and its random forest feature importance is 0.41.
+For $A_\mathrm{AGN1}$, the standardized coefficient is +0.04, and its random forest feature importance is 0.29.
 Both parameters positively correlate with the slope, suggesting that stronger feedback steepens the relation in low-mass galaxies.
-The normalization ($\alpha$) is strongly negatively correlated with A\ensuremath{\_}{SN1} (coefficient -0.38) and A\ensuremath{\_}{AGN1} (coefficient -0.32), indicating that stronger feedback leads to lower black hole masses at a fixed stellar mass.
-The intrinsic scatter is primarily driven by A\ensuremath{\_}{SN1} (coefficient +0.04, random forest importance 0.73), consistent with the expectation that stochastic supernova feedback introduces diversity in black hole growth histories.
+The normalization ($\alpha$) is strongly negatively correlated with $A_\mathrm{SN1}$ (coefficient -0.38) and $A_\mathrm{AGN1}$ (coefficient -0.32), indicating that stronger feedback leads to lower black hole masses at a fixed stellar mass.
+The intrinsic scatter is primarily driven by $A_\mathrm{SN1}$ (coefficient +0.04, random forest importance 0.73), consistent with the expectation that stochastic supernova feedback introduces diversity in black hole growth histories.
 
@@
 
-In the intermediate-mass regime, the slope ($\beta$) is dominated by the AGN feedback parameter A\ensuremath{\_}{AGN1} (coefficient +0.37, random forest importance 0.88).
+In the intermediate-mass regime, the slope ($\beta$) is dominated by the AGN feedback parameter $A_\mathrm{AGN1}$ (coefficient +0.37, random forest importance 0.88).
 This suggests that AGN feedback plays a significant role in regulating black hole growth in intermediate-mass galaxies.
-The normalization ($\alpha$) is also strongly influenced by A\ensuremath{\_}{AGN1} (coefficient -3.32).
-The intrinsic scatter is influenced by both A\ensuremath{\_}{AGN1} and A\ensuremath{\_}{SN1}.
+The normalization ($\alpha$) is also strongly influenced by $A_\mathrm{AGN1}$ (coefficient -3.32).
+The intrinsic scatter is influenced by both $A_\mathrm{AGN1}$ and $A_\mathrm{SN1}$.
 
@@
 
-In high-mass galaxies, the slope ($\beta$) is dominated by the AGN feedback parameter A\ensuremath{\_}{AGN1} (coefficient -0.22, random forest importance 0.69), but the sign of the coefficient is reversed compared to the intermediate-mass bin, indicating a shift in the role of AGN feedback.
-The normalization ($\alpha$) is also strongly influenced by A\ensuremath{\_}{AGN1} (coefficient +2.52).
-The intrinsic scatter is influenced by both A\ensuremath{\_}{AGN1} and A\ensuremath{\_}{SN1}.
+In high-mass galaxies, the slope ($\beta$) is dominated by the AGN feedback parameter $A_\mathrm{AGN1}$ (coefficient -0.22, random forest importance 0.69), but the sign of the coefficient is reversed compared to the intermediate-mass bin, indicating a shift in the role of AGN feedback.
+The normalization ($\alpha$) is also strongly influenced by $A_\mathrm{AGN1}$ (coefficient +2.52).
+The intrinsic scatter is influenced by both $A_\mathrm{AGN1}$ and $A_\mathrm{SN1}$.
 
@@
 The black hole occupation fraction increases with stellar mass, rising from approximately 0.72 in low-mass galaxies to nearly 0.96 in high-mass galaxies.
-The occupation fraction also depends on feedback parameters, with stronger supernova feedback (A\ensuremath{\_}{SN1}) reducing the occupation fraction at low and intermediate masses, consistent with the suppression of black hole formation or growth in shallow potential wells.
+The occupation fraction also depends on feedback parameters, with stronger supernova feedback ($A_\mathrm{SN1}$) reducing the occupation fraction at low and intermediate masses, consistent with the suppression of black hole formation or growth in shallow potential wells.
 

### 2025-05-03 setup.py
update

@@ -17,7 +17,6 @@ setup(name='AstroPilot',
                         'dotenv',
                         'requests',
                         'typing-extensions',
-                        'pdflatex',
                         'tqdm',
                         'pymupdf',
                         'pillow'],

### 2025-05-03 src/parameters.py

@@ -53,6 +53,7 @@ class LLM(TypedDict):
     model: str
     max_output_tokens: int
     llm: Any
+    temperature: float
     
 # Graph state class
 class GraphState(TypedDict):

### 2025-05-03 src/reader.py

@@ -27,12 +27,18 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
     # set the LLM
     if 'gemini' in state['llm']['model']:
         state['llm']['llm'] = ChatGoogleGenerativeAI(model=state['llm']['model'],
-                                                     temperature=0.7,
-                                                     google_api_key=GOOGLE_API_KEY)
-        if 'gemini-2.0' in state['llm']['model']:
-            state['llm']['max_output_tokens'] = 8192
-        if 'gemini-2.5' in state['llm']['model']:
-            state['llm']['max_output_tokens'] = 65536
+                                                temperature=state['llm']['temperature'],
+                                                google_api_key=GOOGLE_API_KEY)
+
+    elif any(key in state['llm']['model'] for key in ['gpt', 'o3']):
+        state['llm']['llm'] = ChatOpenAI(model=state['llm']['model'],
+                                         temperature=state['llm']['temperature'],
+                                         openai_api_key=OPENAI_API_KEY)
+                    
+    elif 'claude' in model or 'anthropic' in model:
+        state['llm']['llm'] = ChatAnthropic(model=state['llm']['model'],
+                                            temperature=state['llm']['temperature'],
+                                            anthropic_api_key=ANTHROPIC_API_KEY)
     
     # set the tokens usage
     state['tokens'] = {}
@@ -122,5 +128,6 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
 
 
     return {"idea": idea,  "files": state['files'],  "paper": {"summary": ""},
-            "tokens": state['tokens'], "latex": state['latex']}
+            "tokens": state['tokens'], "latex": state['latex'],
+            "llm": state['llm']}
 

### 2025-05-03 main.py
update

@@ -13,14 +13,21 @@ graph = build_graph(mermaid_diagram=True)
 
 # run the graph
 result = asyncio.run(graph.ainvoke(
-    {"files":{"Folder":       "Project7",   #name of folder containing input files
+    {"files":{"Folder":       "Project5",   #name of folder containing input files
               "Idea":         "idea.md",    #name of file containing idea description
               "Methods":      "methods.md", #name of file with methods description
               "Results":      "results.md", #name of file with results description
               "Plots":        "plots"},     #name of folder containing plots
-     "llm": {"model": "gemini-2.0-flash"},  #name of the LLM model to use
-     #"llm": {"model": "gemini-2.5-flash-preview-04-17"},  #name of the LLM model to use
-     #"llm": {"model": "gemini-2.5-pro-preview-03-25"},  #name of the LLM model to use
+     #"llm": {"model": "gemini-2.0-flash",   #llm model, temperature, and max out tokens
+     #        "temperature": 0.7, "max_output_tokens": 8192},  
+     "llm": {"model": "gemini-2.5-flash-preview-04-17",
+             "temperature": 0.7, "max_output_tokens": 65536},  
+     #"llm": {"model": "gemini-2.5-pro-preview-03-25",
+     #        "temperature": 0.7, "max_output_tokens": 65536},  
+     #"llm": {"model": 'o3-mini-2025-01-31', "temperature": 0.5,
+     #        "max_output_tokens": 100000}
+     #"llm": {"model": 'claude-3-7-sonnet-20250219', "temperature":0,
+     #        "max_output_tokens": 64000}
      }, config))
 
 # End timer and report duration in minutes and seconds

### 2025-05-03 src/tools.py

@@ -21,8 +21,8 @@ def LLM_call(prompt, state):
     state['tokens']['to'] += output_tokens
     state['tokens']['i'] = input_tokens
     state['tokens']['o'] = output_tokens
-    #with open(state['files']['LLM_calls'], 'a') as f:
-    #    f.write(f"{state['tokens']['i']} {state['tokens']['o']} {state['tokens']['ti']} {state['tokens']['to']}\n")
+    with open(state['files']['LLM_calls'], 'a') as f:
+        f.write(f"{state['tokens']['i']} {state['tokens']['o']} {state['tokens']['ti']} {state['tokens']['to']}\n")
     
     return state, message.content
 

### 2025-05-03 setup.py
added .toml file

@@ -1,24 +1,0 @@
-from setuptools import setup, find_packages
-
-setup(name='AstroPilot',
-      version='0.1.0',
-      packages=find_packages(),
-      install_requires=['langchain',
-                        'langchain-chroma',
-                        'langchain-community',
-                        'langchain-google-vertexai',
-                        'langchain-groq',
-                        'langchain-google-genai',
-                        'langchain-openai',
-                        'langchain-anthropic',
-                        'langgraph',
-                        'langgraph-checkpoint-sqlite',
-                        'pydantic',
-                        'dotenv',
-                        'requests',
-                        'typing-extensions',
-                        'tqdm',
-                        'pymupdf',
-                        'pillow'],
-    include_package_data=True,
-    zip_safe=False)

### 2025-05-04 src/latex.py
some latex errors fixed

@@ -35,7 +35,7 @@ def compile_latex(state: GraphState, paper_name: str, verbose=True):
     def run_bibtex():
         subprocess.run(["bibtex", paper_stem],
                        cwd=state['files']['Folder'],
-                       capture_output=True, text=True, check=True)
+                       capture_output=True, text=True)
 
     def log_output(i, result_or_error, is_error=False):
         with open(state['files']['LaTeX_log'], 'a') as f:
@@ -84,11 +84,13 @@ def compile_latex(state: GraphState, paper_name: str, verbose=True):
         print(f"LaTeX failed on pass 1")
 
     # if there is bibliography, compile it
-    if os.path.exists("bibliography.bib"):
+    further_iterations = 1
+    if os.path.exists(f"{state['files']['Folder']}/bibliography.bib"):
         run_bibtex()
+        further_iterations =2
 
     # Compile it two more times to put references and citations
-    for i in range(2):        
+    for i in range(further_iterations):        
         try:
             result = run_xelatex()
             if verbose:
@@ -96,6 +98,13 @@ def compile_latex(state: GraphState, paper_name: str, verbose=True):
         except subprocess.CalledProcessError as e:
             log_output(f"Final Pass {i+1}", e, is_error=True)
             print(f"LaTeX failed on pass {i+2}")
+
+    # remove auxiliary files
+    for fin in [f'{paper_stem}.aux', f'{paper_stem}.log', f'{paper_stem}.out',
+                f'{paper_stem}.bbl', f'{paper_stem}.blg', f'{paper_stem}.synctex.gz',
+                f'{paper_stem}.synctex(busy)']:
+        if os.path.exists(f"{state['files']['Folder']}/{fin}"):
+            os.remove(f"{state['files']['Folder']}/{fin}")
 
 
 

### 2025-05-04 src/prompts.py

@@ -496,13 +496,19 @@ def clean_section_prompt(state,text):
 You may:
 - Split long paragraphs for better readability
 - Adjust wide tables to occupy the full page width
-- Remove individual citations **only if they appear inside figures or tables**
+- Take into account that citations inside figures or tables will raise LaTeX errors
+- If citations are inside tables or figures, move them outside them. 
+- For instance for this piece,
+\[A = Bx^2 + C \citep{{gallo2019}}\]
+LaTeX will raise an error because the citation is inside the equation. To deal with this, you need to move the citation outside the equation like this:
+\[A = Bx^2 + C\] \citep{{gallo2019}}
+
 
 Do **not**:
 - Change the order of paragraphs or figures
 - Create new sections or restructure the content
 - Remove or rewrite content outside the above allowances
-- Remove all the citations in the text, only those inside figures or tables
+- Remove any citation in the text, only relocate them if they are inside tables or plots
 
 Ensure the modified output can still be compiled in LaTeX without error.
 

### 2025-05-04 main.py
some latex errors fixed

@@ -18,10 +18,10 @@ result = asyncio.run(graph.ainvoke(
               "Methods":      "methods.md", #name of file with methods description
               "Results":      "results.md", #name of file with results description
               "Plots":        "plots"},     #name of folder containing plots
-     #"llm": {"model": "gemini-2.0-flash",   #llm model, temperature, and max out tokens
-     #        "temperature": 0.7, "max_output_tokens": 8192},  
-     "llm": {"model": "gemini-2.5-flash-preview-04-17",
-             "temperature": 0.7, "max_output_tokens": 65536},  
+     "llm": {"model": "gemini-2.0-flash",   #llm model, temperature, and max out tokens
+             "temperature": 0.7, "max_output_tokens": 8192},  
+     #"llm": {"model": "gemini-2.5-flash-preview-04-17",
+     #        "temperature": 0.7, "max_output_tokens": 65536},  
      #"llm": {"model": "gemini-2.5-pro-preview-03-25",
      #        "temperature": 0.7, "max_output_tokens": 65536},  
      #"llm": {"model": 'o3-mini-2025-01-31', "temperature": 0.5,

### 2025-05-04 src/paper_node.py

@@ -70,12 +70,11 @@ def abstract_node(state: GraphState, config: RunnableConfig):
                 state['paper']['Abstract'] = parsed_json["Abstract"]
                 break  # success
             except Exception as e:
-                print(f"[Attempt {i+1}] Failed to parse JSON: {e}")
                 time.sleep(2)
         else:
             raise RuntimeError("LLM failed to produce valid JSON after 3 attempts.")
     
-        # perform several self-reflection rounds
+        # perform self-reflections
         for i in range(1):
 
             # improve abstract

### 2025-05-04 src/reader.py

@@ -53,7 +53,7 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
                       "Paper_v2":  "paper_v2.tex",
                       "Paper_v3":  "paper_v3.tex",
                       "Paper_v4":  "paper_v4.tex",
-                      "Error":     "Error.txt",
+                      "Error":     f"{state['files']['Folder']}/Error.txt",
                       "LaTeX_log": f"{state['files']['Folder']}/LaTeX_compilation.log",
                       "Temp":      f"{state['files']['Folder']}/Temp",
                       "LLM_calls": f"{state['files']['Folder']}/LLM_calls.txt"}
@@ -88,11 +88,10 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
             fin = f"{state['files']['Folder']}/{f_in}"
             if os.path.exists(fin): os.remove(f"{fin}")
 
-    for f_in in [state['files']['Error'], state['files']['LLM_calls']]:
+    # remove these files if they already exist
+    for f_in in [state['files']['Error'], state['files']['LLM_calls'],
+                 state['files']['LaTeX_log']]:
         if os.path.exists(f_in):  os.remove(f"{f_in}")
-        
-    # remove LaTeX compilation log file
-    if os.path.exists(state['files']['LaTeX_log']):  os.remove(state['files']['LaTeX_log'])
 
     # copy LaTeX files to project folder
     for f in ['aasjournal.bst', 'aastex631.cls']:
@@ -107,10 +106,8 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
     plots_dir    = Path(f"{state['files']['Folder']}/{state['files']['Plots']}")
     repeated_dir = Path(f"{plots_dir}_repeated")
 
-    # Hash dictionary
-    hash_dict = {}
-
-    # Walk through all PNG files
+    # Walk through all plot files
+    hash_dict = {}  # create hash dictionary
     for file in plots_dir.iterdir():
         if file.is_file():
 
@@ -127,7 +124,12 @@ def preprocess_node(state: GraphState, config: RunnableConfig):
                 hash_dict[file_hash] = file
 
 
-    return {"idea": idea,  "files": state['files'],  "paper": {"summary": ""},
-            "tokens": state['tokens'], "latex": state['latex'],
-            "llm": state['llm']}
+    return {
+        "llm": state['llm'],
+        "tokens": state['tokens'],
+        "files": state['files'],
[…]

### 2025-05-04 installer.sh
Clean unused function in installer.sh and cleaning option (ag2 and cmbagent are not locally installed in the main folder anymore)

@@ -7,7 +7,7 @@
 # If the first argument is "clean", remove everything and exit.
 if [ "$1" == "clean" ]; then
     echo "Cleaning up Python virtual environment and repositories..."
-    rm -rf astrop_env ag2 cmbagent
+    rm -rf astrop_env
     echo "Clean operation completed."
     exit 0
 fi
@@ -24,18 +24,6 @@ if [ "$current_branch" != "$TARGET_BRANCH" ]; then
     git fetch origin "$TARGET_BRANCH"
     git checkout "$TARGET_BRANCH"
 fi
-
-# Function to clone a repo if it doesn't exist
-clone_repo() {
-  local repo_url=$1
-  local repo_dir=$2
-  if [ ! -d "$repo_dir" ]; then
-    echo "Cloning $repo_url into $repo_dir ..."
-    git clone "$repo_url"
-  else
-    echo "Directory $repo_dir already exists. Skipping clone."
-  fi
-}
 
 # Create a Python 3 virtual environment named 'astrop_env'
 if ! command -v python3 &> /dev/null; then

### 2025-05-04 astropilot/astro_pilot.py
set_data_description docstring and add try except block when file not found

@@ -62,11 +62,21 @@ class AstroPilot:
         keywords: Dict[str, str] = Field(default_factory=dict, description="The AAS keywords describing the project")
 
 
-    def set_data_description(self, data_description: str = None, **kwargs):
+    def set_data_description(self, data_description: str | None = None, **kwargs) -> None:
+        """
+        Set the description of the data and tools to be used by the agents.
+
+        Args:
+            data_description: string or path to markdown file including the description of the tools and data. If None, assume that a `data_description.md` is present in `project_dir/input_files`.
+        """
+
         if data_description is None:
-            with open(os.path.join(self.project_dir, 'input_files', 'data_description.md'), 'r') as f:
-                data_description = f.read()
-            data_description = data_description.replace("{path_to_project_data}", str(self.project_dir)+ "/project_data/")
+            try:
+                with open(os.path.join(self.project_dir, 'input_files', 'data_description.md'), 'r') as f:
+                    data_description = f.read()
+                data_description = data_description.replace("{path_to_project_data}", str(self.project_dir)+ "/project_data/")
+            except FileNotFoundError:
+                raise FileNotFoundError("Please provide an input string or markdown file with the data description.")
 
         elif data_description.endswith(".md"):
             with open(data_description, 'r') as f:

### 2025-05-04 astropilot/astro_pilot.py
Reorganize Research class outside AstroPilot, docstrings for AstroPilot class, show_data_description and  get_idea methods

@@ -15,14 +15,27 @@ from .config import REPO_DIR as repo_dir_default
 import cmbagent
 import shutil
 
-
+class Research(BaseModel):
+    data_description: str = Field(default="", description="The data description of the project")
+    idea: str = Field(default="", description="The idea of the project")
+    methodology: str = Field(default="", description="The methodology of the project")
+    results: str = Field(default="", description="The results of the project")
+    plot_paths: List[str] = Field(default_factory=list, description="The plot paths of the project")
+    keywords: Dict[str, str] = Field(default_factory=dict, description="The AAS keywords describing the project")
 
 class AstroPilot:
+    """
+    AstroPilot main class.
 
+    Args:
+        input_data: Input data to be used. Employ default data if `None`.
+        project_dir: Directory project. If `None`, use the current directory.
+        clear_project_dir: Clear directory if `True`.
+    """
 
-    def __init__(self, input_data: 'AstroPilot.Research' = None, params={}, project_dir: str = repo_dir_default, clear_project_dir: bool = True):
+    def __init__(self, input_data: Research | None = None, params={}, project_dir: str = repo_dir_default, clear_project_dir: bool = True):
         if input_data is None:
-            input_data = AstroPilot.Research()  # Initialize with default values
+            input_data = Research()  # Initialize with default values
         self.clear_project_dir = clear_project_dir
         self.research = input_data
         self.params = params
@@ -51,17 +64,6 @@ class AstroPilot:
         # Create fresh input_files directory
         os.makedirs(input_files_dir, exist_ok=True)
 
-
-
-    class Research(BaseModel):
-        data_description: str = Field(default="", description="The data description of the project")
-        idea: str = Field(default="", description="The idea of the project")
-        methodology: str = Field(default="", description="The methodology of the project")
-        results: str = Field(default="", description="The results of the project")
-        plot_paths: List[str] = Field(default_factory=list, description="The plot paths of the project")
-        keywords: Dict[str, str] = Field(default_factory=dict, description="The AAS keywords describing the project")
-
-
     def set_data_description(self, data_description: str | None = None, **kwargs) -> None:
         """
         Set the description of the data and tools to be used by the agents.
@@ -87,20 +89,21 @@ class AstroPilot:
 
         else:
             raise ValueError("Data description must be a string, a path to a markdown file or None if you want to load data description from input_files/data_description.md")
-        
 
         self.research.data_description = data_description
+
[…]

### 2025-05-04 astropilot/astro_pilot.py
Add docstrings to the rest of methods, improve type hints of returns, add some TODO notes, improve styling

@@ -23,6 +23,8 @@ class Research(BaseModel):
     plot_paths: List[str] = Field(default_factory=list, description="The plot paths of the project")
     keywords: Dict[str, str] = Field(default_factory=dict, description="The AAS keywords describing the project")
 
+# TODO: clean params and kwargs if not used
+# TODO: unify display and print by new method
 class AstroPilot:
     """
     AstroPilot main class.
@@ -54,7 +56,7 @@ class AstroPilot:
 
         self._setup_input_files()
 
-    def _setup_input_files(self):
+    def _setup_input_files(self) -> None:
         input_files_dir = os.path.join(self.project_dir, 'input_files')
         
         # If directory exists, remove it and all its contents
@@ -98,12 +100,13 @@ class AstroPilot:
 
     def show_data_description(self) -> None:
         """Show the data description set by the `set_data_description` method."""
-        
+
         # display(Markdown(self.research.data_description))
         print(self.research.data_description)
 
+    # TODO: some code duplication with set_idea, get_idea could call set_idea internally after generating ideas
     def get_idea(self, **kwargs) -> None:
-        """Generate an idea making use of the data and tools described by the `set_data_description` method."""
+        """Generate an idea making use of the data and tools described in `data_description.md`."""
         
         if self.research.data_description == "":
             with open(os.path.join(self.project_dir, 'input_files', 'data_description.md'), 'r') as f:
@@ -117,7 +120,9 @@ class AstroPilot:
         with open(idea_path, 'w') as f:
             f.write(idea)
     
-    def set_idea(self, idea: str = None):
+    def set_idea(self, idea: str = None) -> None:
+        """Manually set an idea."""
+
         if idea is None:
             with open(os.path.join(self.project_dir, 'input_files', 'idea.md'), 'r') as f:
                 idea = f.read()
@@ -133,14 +138,15 @@ class AstroPilot:
         # write idea to idea.md file
         with open(os.path.join(self.project_dir, 'input_files', 'idea.md'), 'w') as f:
             f.write(idea)
-        return None
     
-    def show_idea(self):
+    def show_idea(self) -> None:
+        """Show the provided or generated idea by the `set_idea` or `get_idea` methods."""
+
         # display(Markdown(self.research.idea))
         print(self.research.idea)
-        return None
     
-    def get_method(self, **kwargs):
+    def get_method(self, **kwargs) -> None:
+        """Generate the methods to be employed making use of the data and tools described in `data_description.md` and the idea in `idea.md`."""
 
[…]

### 2025-05-05 astropilot/astro_pilot.py
Return str in show_data_description, add streamlit dev dependency, remove example projects to keep clean the repo

@@ -98,11 +98,13 @@ class AstroPilot:
         with open(os.path.join(self.project_dir, 'input_files', 'data_description.md'), 'w') as f:
             f.write(data_description)
 
-    def show_data_description(self) -> None:
+    def show_data_description(self) -> str:
         """Show the data description set by the `set_data_description` method."""
 
         # display(Markdown(self.research.data_description))
         print(self.research.data_description)
+
+        return self.research.data_description
 
     # TODO: some code duplication with set_idea, get_idea could call set_idea internally after generating ideas
     def get_idea(self, **kwargs) -> None:

### 2025-05-05 astropilot/method.py
Include Idea, Method, Experiment in API reference, prompts summary in docs, improve docstrings

@@ -7,6 +7,9 @@ import re
 class Method:
     """
     This class is used to develop a research project methodology based on the data of interest and the project idea.
+
+    Args:
+        work_dir: working directory.
     """
 
     def __init__(self, research_idea: str, work_dir = None):
@@ -95,6 +98,12 @@ The methodology should focus on describing the research and analysis that will b
         """
 
     def develop_method(self, data_description: str, **kwargs):
+        """
+        Develops the methods based on the data description.
+
+        Args:
+            data_description: description of the data and tools to be used.
+        """
 
         # ## planning
         # cmbagent = CMBAgent()

### 2025-05-05 astropilot/astro_pilot.py
Include Idea, Method, Experiment in API reference, prompts summary in docs, improve docstrings

@@ -98,13 +98,11 @@ class AstroPilot:
         with open(os.path.join(self.project_dir, 'input_files', 'data_description.md'), 'w') as f:
             f.write(data_description)
 
-    def show_data_description(self) -> str:
+    def show_data_description(self) -> None:
         """Show the data description set by the `set_data_description` method."""
 
         # display(Markdown(self.research.data_description))
         print(self.research.data_description)
-
-        return self.research.data_description
 
     # TODO: some code duplication with set_idea, get_idea could call set_idea internally after generating ideas
     def get_idea(self, **kwargs) -> None:

### 2025-05-05 astropilot/experiment.py

@@ -4,9 +4,11 @@ from typing import List
 import copy
 import os
 import re
+
 class Experiment:
     """
     This class is used to perform the experiment.
+    TODO: improve docstring
     """
 
     def __init__(self, research_idea: str, methodology: str, involved_agents: List[str] = ['engineer', 'researcher'], work_dir = None):
@@ -91,6 +93,10 @@ class Experiment:
         """
 
     def run_experiment(self, data_description: str, **kwargs):
+        """
+        Run the experiment.
+        TODO: improve docstring
+        """
 
         # ## planning
         # cmbagent = CMBAgent()

### 2025-05-05 astropilot/idea.py

@@ -8,6 +8,22 @@ import os
 class Idea:
     """
     This class is used to develop a research project idea based on the data of interest.
+    It makes use of two types of agents:
+
+    - `idea_maker`: to generate new ideas.
+    - `idea_hater`: to critique new ideas.
+    
+    The LLMs are provided the following instructions:
+
+    - Ask `idea_maker` to generate 5 new research project ideas related to the datasets.
+    - Ask `idea_hater` to critique these ideas.
+    - Ask `idea_maker` to select and improve 2 out of the 5 research project ideas given the output of the `idea_hater`.
+    - Ask `idea_hater` to critique the 2 improved ideas. 
+    - Ask `idea_maker` to select the best idea out of the 2. 
+    - Ask `idea_maker` to report the best idea in the form of a scientific paper title with a 1 sentence description. 
+
+    Args:
+        work_dir: working directory.
     """
     def __init__(self, work_dir = None):
         if work_dir is None:
@@ -41,6 +57,12 @@ Don't suggest to perform any calculations or analyses here. The only goal of thi
 #     """
         
     def develop_idea(self, data_description: str, **kwargs):
+        """
+        Develops an idea based on the data description.
+
+        Args:
+            data_description: description of the data and tools to be used.
+        """
 
         # ## planning
         # cmbagent = CMBAgent()

### 2025-05-06 installer.sh
Install cmbagent fromn PyPI, remove ag2 dependency, replace setuptools build backend by hatchling, allow for higher version dependencies for more flexibility, add uv lock

@@ -61,16 +61,6 @@ echo ".env file created."
 
 pip install -e .
 
-### Clone and install ag2 ###
-
-AG2_REPO="https://github.com/CMBAgents/ag2.git"
-AG2_DIR="ag2"
-AG2_BRANCH="ag2_v0.8.4_upgrade_astrop"
-
-echo "Cloning and installing ag2 from branch '$AG2_BRANCH'..."
-
-GIT_LFS_SKIP_SMUDGE=1 pip install git+$AG2_REPO@$AG2_BRANCH
-
 # Install an IPython kernel for the virtual environment
 echo "Installing IPython kernel for the virtual environment..."
 python -m ipykernel install --user --name astrop_env --display-name "Python (astrop_env)"

### 2025-05-06 astropilot/config.py
Improve formatting based on ruff linting (fixed 77/98 ruff errors)

@@ -1,4 +1,3 @@
-import os
 from pathlib import Path
 
 # Using pathlib (modern approach) to define the base directory as the directory that contains this file.

### 2025-05-06 astropilot/idea.py

@@ -1,9 +1,6 @@
-# from cmbagent import CMBAgent
-import cmbagent
-import copy
 import re
 import os
-
+import cmbagent
 
 class Idea:
     """
@@ -93,7 +90,7 @@ Don't suggest to perform any calculations or analyses here. The only goal of thi
                              )
 
         chat_history = results['chat_history']
-        final_context = results['final_context']
+        # final_context = results['final_context']
         
         try:
             for obj in chat_history[::-1]:

### 2025-05-06 astropilot/llm.py

@@ -1,8 +1,8 @@
+import os
 from langchain_groq import ChatGroq
 from langchain_openai import ChatOpenAI
 from langchain_anthropic import ChatAnthropic
 from langchain_google_genai import ChatGoogleGenerativeAI
-import os
 from dotenv import load_dotenv
 
 load_dotenv()

### 2025-05-06 astropilot/paper_node.py

@@ -1,23 +1,20 @@
 from langchain_core.runnables import RunnableConfig
-import sys,os,re,random,base64,json,time
+import random
+import base64
+import time
 from pathlib import Path
 from tqdm import tqdm
 import asyncio
 from functools import partial
 import fitz  # PyMuPDF
+import cmbagent
 
 from .parameters import GraphState
-from .prompts import *
-from .llm import llm
-from .tools import json_parser, fixer, LaTeX_checker, clean_section, extract_latex_block, LLM_call, temp_file
+from .prompts import abstract_prompt, abstract_reflection, caption_prompt, clean_section_prompt, conclusions_prompt, introduction_prompt, introduction_reflection, keyword_prompt, methods_prompt, plot_prompt, references_prompt, refine_results_prompt, results_prompt
+from .tools import json_parser, LaTeX_checker, clean_section, extract_latex_block, LLM_call, temp_file
 from .literature import process_tex_file_with_references
 from .latex import compile_latex, save_paper, save_bib, process_bib_file
 
-import cmbagent
-
-
-
-    
 
 def keywords_node(state: GraphState, config: RunnableConfig):
     """
@@ -80,7 +77,7 @@ def abstract_node(state: GraphState, config: RunnableConfig):
     """
 
     # temporary file with the selected keywords
-    print(f"Writing Abstract...", end="", flush=True)
+    print("Writing Abstract...", end="", flush=True)
     f_temp1 = Path(f"{state['files']['Temp']}/Abstract.tex")
     f_temp2 = Path(f"{state['files']['Temp']}/Title.tex")
 
@@ -253,7 +250,6 @@ def plots_node(state: GraphState, config: RunnableConfig):
         num_images = 21
 
     # Process in batches
-    all_results = []
     for start in range(0, num_images, batch_size):
 
         batch_files = files[start:start + batch_size]

### 2025-05-06 astropilot/reader.py

@@ -1,15 +1,12 @@
-from langchain_core.runnables import RunnableConfig
-import sys,os
+import os
 from pathlib import Path
 import hashlib
 import shutil
-from langchain_groq import ChatGroq
-from langchain_openai import ChatOpenAI
-from langchain_anthropic import ChatAnthropic
+from langchain_core.runnables import RunnableConfig
 from langchain_google_genai import ChatGoogleGenerativeAI
 from dotenv import load_dotenv
-from .config import LaTeX_DIR
 
+from .config import LaTeX_DIR
 from .parameters import GraphState
 
 

### 2025-05-06 astropilot/tools.py

@@ -1,12 +1,9 @@
-import requests
-import sys,os,re,json
-from langchain_core.messages import HumanMessage
-from dotenv import load_dotenv
+import re
+import json
+from pathlib import Path
+
 from .prompts import fixer_prompt, LaTeX_prompt
 from .parameters import GraphState
-from .llm import llm
-from pathlib import Path
-#from dotenv import load_dotenv
 
 
 def LLM_call(prompt, state):
@@ -140,7 +137,7 @@ def fixer(state: GraphState, section_name):
     else:
         with open(state['files']['Error'], 'w', encoding='utf-8') as f:
             f.write(result)
-        raise ValueError(f"Fixer failed as well")
+        raise ValueError("Fixer failed as well")
 
 
 
@@ -165,11 +162,11 @@ def clean_section(text, section):
     text = text.replace(fr"\section*{{{section}}}", "")
     text = text.replace(fr"\begin{{{section}}}", "")
     text = text.replace(fr"\end{{{section}}}", "")
-    text = text.replace(fr"\maketitle", "")
-    text = text.replace(fr"<PARAGRAPH>", "")
-    text = text.replace(fr"</PARAGRAPH>", "")
-    text = text.replace(fr"```latex", "")
-    text = text.replace(fr"```", "")
+    text = text.replace(r"\maketitle", "")
+    text = text.replace(r"<PARAGRAPH>", "")
+    text = text.replace(r"</PARAGRAPH>", "")
+    text = text.replace(r"```latex", "")
+    text = text.replace(r"```", "")
     text = text.replace(r"\usepackage{amsmath}", "")
 
     return text

### 2025-05-06 astropilot/latex.py
Improve formatting based on ruff linting (fixed 77/98 ruff errors)

@@ -1,9 +1,10 @@
 import subprocess
-import sys,os,re
+import os
+import re
 from pathlib import Path
 
 from .parameters import GraphState
-from .prompts import *
+from .prompts import fix_latex_bug_prompt
 from .tools import LLM_call, extract_latex_block
 
 
@@ -76,12 +77,12 @@ def compile_latex(state: GraphState, paper_name: str, verbose=True):
 
     # Try to compile it the first time
     try:
-        result = run_xelatex()
+        run_xelatex()
         if verbose:
-            print(f"    LaTeX compiled successfully: Pass 1")
+            print("    LaTeX compiled successfully: Pass 1")
     except subprocess.CalledProcessError as e:
         log_output("Pass 1", e, is_error=True)
-        print(f"LaTeX failed on pass 1")
+        print("LaTeX failed on pass 1")
 
     # if there is bibliography, compile it
     if os.path.exists("bibliography.bib"):
@@ -90,7 +91,7 @@ def compile_latex(state: GraphState, paper_name: str, verbose=True):
     # Compile it two more times to put references and citations
     for i in range(2):        
         try:
-            result = run_xelatex()
+            run_xelatex()
             if verbose:
                 print(f"    LaTeX compiled successfully: Pass {i+2}")
         except subprocess.CalledProcessError as e:
@@ -279,7 +280,7 @@ def process_bib_file(input_file, output_file):
     for line in lines:
         if line.strip().startswith('title') or line.strip().startswith('journal'):
             key, value = line.split('=', 1)
-            quote_char = '"' if '"' in value else '{'
+            # quote_char = '"' if '"' in value else '{'
             content = re.search(r'[{\"](.+)[}\"]', value).group(1)
             escaped_content = escape_special_chars(content)
 

### 2025-05-06 astropilot/method.py

@@ -1,8 +1,6 @@
-# from cmbagent import CMBAgent
-import cmbagent
-import copy
 import os
 import re
+import cmbagent
 
 class Method:
     """
@@ -155,7 +153,7 @@ The methodology should focus on describing the research and analysis that will b
                              )
         
         chat_history = results['chat_history']
-        final_context = results['final_context']
+        # final_context = results['final_context']
         
         try:
             for obj in chat_history[::-1]:

### 2025-05-06 astropilot/prompts.py

@@ -1,5 +1,4 @@
-from langchain_core.messages import AnyMessage, HumanMessage, SystemMessage, AIMessage
-import re
+from langchain_core.messages import HumanMessage, SystemMessage
 
 
 def idea_prompt(topic):
